\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

\title{Flossdaily's Works}
\author{Compiled by Indiv0}

\begin{document}
\maketitle
\newpage
\tableofcontents
\newpage

\section{Introduction}

\section{Sterile}
    \subsection{Part I}
        Well, I'll tell you, but you're never going to believe it:
I'll never forget that Wednesday. I had been invited down to the PILT cosmic ray observatory. I don't know if you've ever heard of this thing, but it's essentially just a cave buried deep in the earth. You go down this long shaft until you arrive in an observation room.
The observation room looks out over the detection room. The detection room is surrounded on all sides by massive tanks of fluid. The whole setup is designed to block out all sorts of different types of background radiation that are passing through us all the time.
I had been invited down by a former coworker. This guy worked with me in neuroimaging for a while, until he found a job as a tech working for the PILT lab. I had called him to ask if he knew of any openings at his new job, and when he told me what he was doing I casually mentioned that I'd love to see the lab. He said 'sure', so here I was.
In the morning as I drove to the PILT site, I was listening to the local NPR station. They were talking about the unidentified object that was supposed to be passing by us in space today. I was surprised I hadn’t heard about it earlier. What surprised me more was the discussion they were having about it.
The original report aired, and then the reporter joined the anchor in the studio. The anchorman said, “Now, I understand there have been developments in this story today, Christine?”
Christine said, “Absolutely, Don. A spokesperson from NASA released a statement less than an hour ago reporting that the object seems to be slowing down.”
I glared at the radio, wondering if I’d heard that correctly. The anchor must have had the same reaction. He said, “I’m sorry Christine, did you say slowing down? In space?”
“Yes, Don,” said Christine. “NASA said they’d be making a statement about it shortly, but they said that at the moment, they aren’t ready to offer an explanation.”
Don said, “So, are they suggesting that this may be a manmade object after all then?”
Christine said, “They haven’t said that yet, Don. My understanding is that they’ve been tracking this object from some distance away from Earth.”
I set my mind to the task of imagining what kind of object could slow its own velocity in the vacuum of space. I thought of a giant mountain of ice and rock in space, and how the sun’s rays may melt and explode the ice on one side- causing some sort of steam geyser to act as a breaking rocket.
It seemed somewhat ridiculous, but not impossible. Maybe such a thing could slow down an asteroid just a little bit. Maybe that small drop in speed was all that NASA would need to sensationalize the event, and briefly catch the public imagination. They’d sensationalized their headlines for years, hadn’t they?
When I arrived at PILT, I met my friend, Chen. Chen was his last name, but I’d been calling him by it for so long that I’d forgotten his first name. “Chen, buddy!” I said, warmly, “Great to see you, man!”
Chen, shook my hand and we shared a tastefully brief guy-hug. That didn’t stop him from saying, “don’t grab my ass or anything. I know about you.”
Ah, good old Chen. “You know I’ve always wanted you,” I said.
“You complete me,” he said, with perfect deadpan. He used to say that to me all the time when we worked together at the hospital. It still made me chuckle.
He brought me into the PILT through a side entrance. The hallways were industrial and ugly. No big surprise- most research facilities didn’t waste time on comfort or esthetics.
Chen stopped at a few offices on the way down the long corridor. He introduced me to his various colleagues, and tastefully tried to sell them on my credentials. For the first time, I started to feel that I might actually get a job offer out of this visit.
Eventually we came to an employee lounge. A small crowd had gathered around a small television. On the screen there was a press conference. I didn’t recognize the speaker, but text on the screen told me that it was a NASA official. As we approached, the crowd hushed Chen and me.
I squeezed in next to the employees and listened with interest, catching the speaker mid-sentence: “-for about an hour. Our readings have been confirmed independently, and at this time, we calculate that the object will reach Earth in approximately three hours.
“We have no reason to expect a collision at this time, but we are concerned by the course change. There is very little doubt at this time that the object we call U-1373 is in fact being directed by some intelligence.
“We are contacting all space-faring nations and private corporations that may have any knowledge of this object, but due to its size and initial trajectory; it is unlikely that it is of Earth origin.
“I wish I could give you more details, but until it get’s a little closer, I’m afraid we don’t know much more. I’ll take some questions now, but I ask you wait until I call on you….”

The press conference erupted into questions, but no more information could be garnered. The employees in the lounge looked at each other with shocked eyes. Chen said, “Whoa… that is deep stuff.”
A pretty brunette in her mid-thirties spun around and said, “Aaron,” I want to see if we can take a look at that thing. She noticed me and gave a quizzical look. On another day she might have inquired who I was and what I was doing here, but in light of the circumstances, she didn’t care.
Chen said, “Okay, do we know where to look?”
From an office just out of view, someone answered, “I’m calling my guy over there right now. I’ll have it for you by the time you get down.”
Chen and the brunette started walking away. Chen didn’t stop as he called over his shoulder, “You coming, slow poke?”
Happy with the invitation, I jogged down the hall to catch up to them. We got to an elevator where Chen swiped his badge. The doors opened to reveal a surprisingly un-sturdy looking cage. The other two got in quickly. I hesitated for only a moment and stepped in, feeling uneasy.
The doors closed behind me, and I looked down at the grate we were standing on. Below I could see nothing but an infinite blackness. If Chen was bothered by the bottomless pit, he certainly didn’t show it. “Neat, huh?” was all he said.
The elevator jerked to life. Now, with a slow-descent in front of us, the brunette turned to Chen and said, “So, who is this now?”
Chen said, “This is my old co-worker, Kyle. I’m showing him around today. If we’re lucky, maybe we’ll get him to work for us.”
The woman shook my hand and said, “Well then, Kyle. You picked an interesting day to see what we do. I’m Karen, by the way.”
Chen said, “Karen is the head boss-lady.”
“Assistant head boss-lady,” she corrected.
The elevator moved a fairly quickly, I thought, but it was hard to gauge the speed. There was nothing but darkness below and above us, and only a couple of tiny bulbs illuminated the lift itself.
The descent took nearly half an hour, and I found my ears popping many times. The pressure change made me feel rather uncomfortable, and I found myself wondering if you could get the bends from such a trip, or if that could only happen while SCUBA diving.
I thought we would pass the time by speculating on the mysterious object floating out to meet the Earth, but almost immediately Chen and Karen were discussing the technical details involved in repositioning their sensor array. I understood very little of what they were saying, and stood mute in the corner of the lift.
When we did eventually come to a stop, I was pleased to discover a rather nicer room than I’d been expecting. There were some comfortable chairs, some fantastic looking computer equipment, and the room actually had a cozy feeling about it. I noted with relief that there was a restroom down here, though I couldn’t imagine how the plumbing might work.
The room had been empty before we arrived. I wondered how often people actually came down here. Then I wondered why this wasn’t all done by remote up top. Chen sat down at the computer and shortly announced, “Abe sent me some coordinates.”
Karen was busy at a different terminal, but nothing on her screen made even the slightest bit of sense to me. Chen got up and went to a coat rack in the corner. He reached for something that at first glance I had thought was a lab coat. When he stepped into it, though, I realized it was some sort of full-body suit.
Chen saw my confusion and said, “Static suit. So I don’t damage the equipment.”
I nodded, without really understanding.
Chen opened a door that had been obscured by computer equipment, I saw him pull some sort of tether from a hook on the wall. He latched the tether to his suit and stepped into the other room, closing the door behind him. Through a long, narrow window on the wall, which I had at first confused for a florescent light, I saw Chen moving against a bright white background.
I moved to the window, and got my first glimpse of the PILT. One of the most expensive pieces of sensory equipment ever created. I turned to Karen and said, “Hey, wait a minute. How on Earth are we going to detect an object in space? Isn’t this whole place designed to block out everything but cosmic rays? Isn’t that the whole point of being this far underground?
Karen looked at me with surprise. “You mean Aaron didn’t tell you?”
That was the second time she’d said Aaron. It finally clicked that she was talking about Chen. How the hell had I forgotten his first name so completely? I shook my head at Karen, “Didn’t tell me what?”

Karen said, “I’ll tell you if you swear to sign a non-disclosure agreement before you leave.”
Now I was intrigued. “Yeah, no problem,” I said.
Karen stepped over to me by the window and pointed at a strange square-shaped detector array which Chen was adjusting somehow. “You see that?” she said, “That is the first deep space quantum detection telescope.”
“I don’t understand,” I said. “I don’t think I’ve ever heard of that.”
“Good,” she said. She didn’t seem interested in explaining it. She went back to her terminal.
I watched Chen work for another few minutes before he came back and shed his static suit. He sat down at the work station and brought up a rather bare-bones looking controller application. I saw him punch in the coordinates that he’d been sent, and then a status bar appeared indicating that something was charging.
In a moment, a green button labeled “detect series” appeared in the corner of the application. He looked at Karen and said, “We are ready.”
Karen said, “I’m not,” and she continued her mysterious work.
I looked at Chen questioningly. He said, “I just reset the array and pointed it where we want to look. She is calibrating it to look at a closer distance.”
“You mean, she’s focusing it?” I asked.
“Yes,” said Chen, “That would be a simpler way to say that.”
“She’s done,” said Karen.
“Fire one,” said Chen, and he clicked the green button.
Nothing happened. No sound, no flash, nothing- I looked at Chen for an explanation. He just said, “Give it a minute.”
So we waited and eventually something did appear on the screen. It was a series of images lined up like an array of tiny slides. Chen clicked on one to enlarge it. I didn’t see anything but a giant black square with some freckles of light here and there. I was disappointed.
Chen and Karen looked through some of the other slides and then Chen said, “Okay, that was a dud.”
He picked up a phone and dialed. On the other end I heard a muffled voice speak a muffled greeting. Chen, with his old familiar charm said, “You are an idiot.”
Then Chen laughed and said, “But seriously though, those coordinates didn’t work.”
The voice on the line said something, and Chen said, “Okay, bye.”
After hanging up, Chen explained that the object had changed course yet again, but that there was now a live coordinate feed coming from some radio telescope farm that I’d never heard of. Then, with surprising technical grace, Chen set up the PILT to track the object directly from the remote feed. He went over and showed Karen how to use the same feed to help focus the sensor array.
After all was set, Chen clicked the “detect series” button again. This time the array picked up something amazing.
Chen clicked on one of the slides and it enlarged to breathtaking detail. It was a sharp, arrowhead shaped object. Its surface had fine indented grooves on it, but I couldn't guess what purpose they served.
“This is the space object?” I said.
Chen nodded.
“How big is this?” I asked.
“Chen clicked a button and a grid overlaid the image. I didn’t see any scale associated with the grid, but Chen had all the information he needed. “900 meters long,” he said. “500 meters wide at the fat part.”
Karen said, “Wow… this thing is close. Can we see it’s trajectory?”
Chen looked at here blankly, and said, “What do you think this is? Star Trek? I have a computer that does one thing it aims a telescope. Next you’ll be asking me to raise shields and fire at it.”
Karen looked at him coldly, but he broke her indignation with his charismatic laugh.
I said, “Well, if you’ve got a high speed internet connection down here, we could probably get some streaming live news in here. Someone must have a graphic up by now showing us where that thing is headed.”
Chen pulled up a browser and in moments had CNN video displayed on the screen, but with no sound. He played around with the volume controls for a moment, but nothing happened. “I don’t think we get sound on these,” he said.
“I’m not surprised,” I said. “A lot companies never install the audio drivers when they set up linux systems in a work environment.”
“Well, that’s stupid,” he said. I just shrugged.
We got our news from the print stories that came in bit by bit. On first glance we were bombarded by hundreds of headlines about a UFO coming towards Earth. There was speculation about a secret Chinese space project. There were blurry versions of the images we’d seen clearly on our screen moment’s ago. I started to get a sense for how amazing this PILT detector really was.
“We should send these out to someone,” said Chen, referring back to his slides. Karen agreed, and they sent a bunch to someone Karen knew at NASA. She cc’ed almost everyone in the PILT research center above us.
Within minutes Chen was receiving replies in his inbox. People were amazed by the images. Speculation ran rampant. Had I just witnessed the first clear images ever taken of a verifiable alien spacecraft? It sounded ridiculous, but I couldn’t think of any other explanation.
CNN was showing a graphic depicting a triangle and a circle around the Earth- it was clear they were trying to show an orbital pattern. I said, “I wish we had sound. Do you think they’re actually getting data to suggest it’s going to orbit when it gets here, or is this pure speculation?”
Karen and Chen just shrugged. We all had questions and no answers.
Then Chen refreshed the browser to get the latest headlines. We were bombarded by 15 variations on the proclamation: “ALIENS ORBIT THE EARTH!”
We clicked on a link from Reuters- and indeed, the article was written in present tense. The object was orbiting the Earth.
Chen said, “didn’t they say it was hours away?”
I nodded, “I thought I heard that as well.”
Karen said, “Yes I’m certain they said three hours right before we came down here.”
And then, everything went dark.

“Whoa,” I said.
In the dark, Chen’s voice said, “Relax.”
As the words were leaving his lips I heard a loud click from another room and then a humming sound. The lights came back on. Soon after, the computer monitors clicked to life as well. I was surprised to see that, though the monitors had lost power, someone had had the sense to keep the computers themselves hooked up to a UPS. As the screens glowed back to life, everything was exactly as it had been.
Karen said, “We should leave. The backup generator will be enough to get us back up in the lift.”
“Are you sure?” asked Chen, “I really don’t want to get halfway up and find out we ran out of juice.”
Karen said, “Yes, I’m sure. This is exactly what the generator was designed for in the first place.”
Chen looked skeptical and said, “I’m going to call upstairs just so they know to come get us if we’re not back in an hour.”
“I like that idea,” I said.
Karen nodded, and Chen picked up the phone. He pressed some buttons and then replaced the receiver. “No dial tone,” he said.
He typed out an email to someone upstairs, but he got a ‘timeout’ error when he tried to send it. I pulled out my cell phone, but before I could realize how futile that was; they were already shaking their heads at me.
Karen said, “They already know we’re down here. I think we should head on up. They’ll figure it out if we don’t show up in an hour or so anyway. The worst thing we can do is wait for the generator to die, then we might really be in trouble.”
I didn’t really follow her logic, but frankly I was getting a little claustrophobic, and besides, I wanted to be up there with the rest of humanity if today was going to be the big day when we finally meet an alien species.
We stepped into the lift. Karen pressed a button. The lift doors closed, but nothing happened. Karen pressed the button again. We stood under the small elevator lights under a pillar of dark, empty shaft. I took a slow breath, trying to stave off the early signs of a panic attack.
“Well,” said Karen, “This isn’t going to do at all.”
She pressed the DOOR OPEN button, to my relief, the doors obeyed. We stepped back into the cozy underground room.
I didn’t really start to worry until several more hours had gone by. With the power outage, we’d lost our internet connection- so we were cut off from the news during the most exciting day in all of human history. It was infuriating. I allowed myself to stew on that for a while, because I knew that anger was better than fear.
Chen tried the phone every ten minutes or so. There was no dial tone.
Something occurred to me suddenly, and I went into the elevator and found an emergency phone that no one had noticed! I felt very proud of myself for a minute as I picked it up and I heard it start to ring.
My enthusiasm wore off, when after 5 minutes of ringing, I realized that no one was going to pick up. I walked out of the elevator again and sat down disappointed. “Well,” I said, “I think we’re really and truly stuck down here.”
Chen tried his phone again. No dial tone.
Karen had taken off her uncomfortable shoes, and I followed suit. “Well,” I said, “If we’re stuck down here for a while, at least we’ll lose some weight, right? So that’s something.”
Chen looked at me quizzically for a moment and then said, “Oh, are you hungry?”
I said, “A little, but we could be down here for a while, so if you have any food we should probably save it.”
Chen and Karen smiled at each other. Chen stood up. “Come with me, little friend,” he said. Then he opened up a door that I thought had led to the restroom.
Instead, there was a small room, and though the restroom lay beyond, there was yet another door off to the side. It was when Chen opened this door that my spirits were lifted.
The room we stepped into was fairly large. In the corner was a large generator humming away. Along the walls and on several shelves that jutted into the room, there were boxes of food and jugs of water. They even had a rather impressive medical station including a portable defibrillator.
Chen spotted something in the corner and said, “oh yeah!”
I watched him stroll over pull out some small bags with draw strings. He tossed one to me. I caught it and read the writing: ‘Ultra-Compact Sleeping Bag’. I had mixed emotions. I was glad for the comfort, but I had not yet resigned myself to spending the night in this hole in the ground.
Chen handed me a box of food and picked up a large jug of water. We walked back to where Karen was sitting, and Chen handed her a sleeping bag. She smiled and said, “Oh, fantastic!”
I pulled some packaged foods from the box Chen had handed me. It reminded me of the meals I used to pack when I went backpacking in the woods. They ended up tasting about the same as well, and I was grateful for the nourishment. \\ \\
\hrule ~ \\ \\

None of us slept that night. We shared intimate stories, and speculated about the aliens above. Every so often we would try the phones, and the computers. With no sunlight to cue my circadian rhythms I spent the next 24 hours in a haze.

We’d been down in the detector lab for quite some time before I really started to freak out. I let the elevator phone ring for an hour before hanging it up. The internet and the regular phone system showed no signs of improvement. I started opening some filing cabinets and looking through PILT documents just to keep my mind occupied.
Karen said, “Find anything interesting?”
I shook my head. She said, “Yeah, I’m not surprised, those technical manuals are pretty dry. When we get out of here remember to have me send down some juicy mystery novels.”
I smiled politely, but I was starting to lose my patience. I was angry at the situation, and it was taking a lot of self control to avoid blaming Karen and Chen. They were victims here too, but part of me wanted to strangle them for getting us trapped down here.
We found a deck of cards in one of the storage boxes, and we busied ourselves playing every game we could think of. This went on for hours. Eventually we tired of it and tried to amuse ourselves in other ways. I searched through the computer hard drives for anything interesting and found nothing- not even a game of solitaire.
Karen and Chen engaged themselves with yet another game of War when I declined to play go-fish.
I returned to the filing cabinet and pulled out more folders. Something extraordinarily lucky happened then. As I was examining a rather bland manila folder I found a document labeled ‘EMERGENCY PROCEDURES’. After thumbing through for just a moment, I realized that I had struck gold.
“Hey! You two! Look at this!” I shouted at them. They looked me curiously as I brought the document over.
“Oh good,” said Chen. But he seemed unimpressed.
“No,” I said, “look at this.”
I pointed to a table of contents- a sectional labeled ‘ELEVATOR FAILURE / MANUAL LIFT CONTROLS’. They stopped playing cards and read with me.
The instructions were complicated, but nothing we couldn’t handle. Attached to the side of the lift was a mechanical hand crank. The hand crank needed to be removed from its storage location, then fastened to the cables after removing a protective panel. It took us about 45 minutes to work out the mechanics of it, but then we were good to go.
The emergency manual didn’t give any hints, but we estimated that it would take easily 6 hours to hand power the lift to the top of the shaft. We considered how much food and water we should bring- if any. And we decided that a day’s ration of food would do fine, along with plenty of water, which we were sure we would be sweating out.
We all relieved ourselves in the restroom. It had turned out to be a flush toilet, to my great shock. I tried not to think too terribly hard about where all the waste went to- it certainly wasn’t being pump all the way back up… was it?
All three of us took a half-dose of immodium to prevent any … unpleasantness in our long assent to the surface. We tried the phone and the internet one last time before climbing into the elevator and closing the doors behind us.
The hand-crank mechanism was designed for use by one person, but we quickly found a method that allowed two of us to work while one rested. In this manner we worked in half-hour shifts, with a rotation every 15 minutes. Our assent was slow- much slower than we had hoped.
I noticed depth markers on some of the beams that framed the shaft, and assuming that we were aiming for a depth of ‘0’, I estimated that we would arrive in 8 hours, if we worked constantly. After 3 hours we found that in fact, we could not work constantly. We took long breaks, resigned to the idea that it would take us quite some time to complete the journey.
At 6 hours we all took a long break to have a substantial meal, and to rest our aching muscles. At 7 hours we passed the halfway mark. At 11 hours we took a vote and decided to take a sleep.
I sat, in the dim lift light, looking at the perfect blackness above and below. I was beyond feeling claustrophobic, nor was I any longer bothered by the height. All I felt was small. Incredibly small, like an ant digging out from the Earth.
I looked at the shaft supports wondering how long it had taken to construct this amazing tunnel. I noticed a line of ants walking on the beam... then on closer inspection I noticed that the ants weren't walking at all. They were all dead, in a perfect little line. It made me sad somehow.
Karen and Chen slept. I could not. My mind was troubled.
I could understand how we might have been forgotten about in all the excitement. I could understand how the building might have been deserted as people took the day off to be with their families as the aliens arrived. I could understand how an emergency lift phone might be ringing in an empty hall with no one to hear it.
What I couldn't understand is why we had lost power when we did, and why it hadn't come back. And why hadn’t the lift controls worked? As I had read the emergency manual earlier, I noticed that the hand crank was designed only for the case the backup generator had failed. It should have provided power to the lift computer at the top of the shaft.
As we rested only hours from the surface, I began to wonder what exactly was waiting for us. I wondered if it was something we really wanted to see.

I had lost all track of time. My entire body ached. We had reached and then passed the ‘0’ elevation marker an hour ago. The dark shaft was playing games with my head. I was starting to wonder if I was stuck in some real life Twilight Zone where I was eternally trapped- cranking this elevator for all time, like Sisyphus pushing his boulder up a hill.
Karen and I were sharing the work when it happened. In a hypnotic daze we were turning the crank. I had stopped counting the numbers on the beams. My eyes were half shut. And suddenly-
-CLANK-
The elevator shook and reverberated. We looked around and then Chen saw the top of the door. We had overshot it by a couple of feet. We briefly debated setting the hand crank in reverse and lowering ourselves, but we thought the better of it when Karen asked if such a maneuver might end up plunging us into a freefall.
We pried the doors open with considerable effort. Our poor leverage didn’t make the task any easier. After crying out for help, and receiving none we decided to make our escape.
I slid out first, which was terrifying. The lift was about three and a half feet above where it ought to be, so as I slid down, I felt that at any moment I might slip into the shaft below the lift. I was able to find my footing, though, and at last I was on solid ground.
I stepped back from the elevator doors looked down the dark hallways. I walked a few feet to wall and felt for a switch. I found one, but it did nothing. If the upstairs had a generator, it wasn’t working.
I walked back to the lift and helped the others down. We pulled the elevator doors shut carefully, and examined our surroundings.
One end of the hallway was pitch-black… the other end showed signs of sunlight around the corner. I headed towards the light, instinctively, but Chen grabbed my arm. “This way,” he said- and the three of us marched into the dark.
I heard Karen trip on something. Chen asked if she was okay, and she didn’t respond. Chen asked again, and we heard Karen scream.
My blood went cold, and I shouted “What?! What?!”
“He’s dead,” said Karen, “there’s a dead person on the floor right here.”
Chen said, “Okay, let’s just be calm and get to the exit. I’ll go first. Why don’t you hold my hand?”
Karen agreed, and then I felt her grip my hand as well. I’m not ashamed to say I felt relieved.
The three of us marched farther into the darkness. Chen announced another body ahead, and then we walked around it. Eventually we got to the side exit, and Chen pushed it open.
The daylight was blinding. We all stood just outside the doors and gave our eyes time to adjust. When I could see again, the first thing I noticed was the birds.
There was a dead one in the parking lot, and another a dozen yards away. I saw two on the street.
“The air smells funny,” said Karen. I agreed. It smelled… stale somehow.
We walked to Karen’s car as it was parked the closest. Karen stopped us when she realized her keys were in her office inside. None of us were keen on the idea of going back in just yet, so we walked to my car instead.
I fished the keys out of my pocket, but the car wouldn’t respond to my remote. I put the key in the door and opened it. I tried to unlock the doors but the button didn’t work. It seemed like the battery was dead. I put the key in the ignition and turned it. There was a clicking noise. The battery was okay, but the engine wasn't turning over. I didn't know how to proceed.
We walked to Chen’s car. It was a rusty old pickup truck. I’d teased him about it when we worked together years ago. I couldn’t believe he still had it. He climbed into the driver’s side, and we heard the engine turn over. Why his and not mine? I wondered.
Karen and I squeezed into the cab, and Chen took off down the road. Along the way I saw more dead birds, here and there a dead squirrel, and then we started to see the car accidents. It started with an SUV spun off into a ditch. We investigated and found the driver quite dead.
We drove past two more car wrecks without stopping. I saw an entire field full of dead birds. I looked into the sky. I didn’t see anything but clouds and sky. “Stop the car,” I said.
Chen stopped the car, and then on request, the engine. I stepped outside and shut my eyes. Karen and Chen followed me. “What is it,” Karen asked.
“Shhh…” I said, “Listen.”
They were quiet. I was quiet. We heard nothing: not a bird, not a cricket, nor an airplane or a car; just the wind in the leaves and the sound of our own breathing.
We got back into the car and drove into town. Dead bodies were everywhere. Cars were driven into lamp posts and store fronts.
Karen said, “I think they all died at the same time, out of the blue. No one moved off the sidewalks to examine the car wrecks. People seem to have fallen in the middle of whatever they were doing.”
I looked at the small park in the town square. The leaves on the trees were green but falling off in significant numbers. It was bizarre- far too early in the season. I pointed to it and said, “Something is wrong with the plants, too.”
Then I smelled the air again. That’s when I knew. It hadn’t seemed possible, but I knew right then, that everything was even worse than it seemed.
“I don’t smell the bodies,” I said. I walked over to one and turned it over. It was a young girl. She looked as if she had died only moments ago- except for the telltale signs of internal pooling blood. “They aren't rotting.”
Chen and Karen looked at me, not understanding.
“This whole place has been sterilized,” I said. “It isn’t just the people and the animals. It’s the plants, and the microbes and the bacteria. Nothing is decomposing.”
Karen said, “Do you think it’s like this everywhere?”
I nodded. But Chen said, “We can’t know that. We can’t possibly know that.”
I said, “I think someone is coming here to take our planet and set up their own ecosystem. They needed us out of the way so that we didn’t contaminate it. I think they just undid billions of years of evolution. No extinction in history has come close to this.”
Chen said, “We don’t know that yet. We should keep going.”
We got in the truck and drove into the night.
The sky was bright and beautiful without any city lights. But I didn’t look out the window. I knew there was nothing left to see.

\subsection{Part II}
Although we never actually discussed it, it seems that we had decided to stick together. Chen, Karen and I drove from one dead town to another, to another. We noticed that Chen’s gas tank was looking a little low, and we realized it was time to come up with a plan.
Karen suggested that we find a new vehicle. I suggested that we find some sort of hand pump to siphon gasoline when we needed to. Not my idea, mind you- we all saw Will Smith do it in “I Am Legend”. Chen wanted to find a portable television or radio. The one in his car wasn’t working.
Our first stop was at a hardware store where we had planned to “load up on supplies.” But when we got there we realized that we had no idea what supplies it was that we were going to need. We picked up some flashlights so that we felt we had accomplished something. I looked for a fuel pump and couldn’t find one.
We went to an electronics store nearby. And although we had found that batteries worked just fine, we couldn’t get any of the radios or portable televisions to work. The evidence was stacking up that anything with a computer chip in it was pretty much useless.
Finding a vehicle was tough. Most modern cars had at least some computer controls in them. We looked in the used vehicle lots an eventually found a Cadillac that suited our needs. It wasn’t great, but it had nearly a full tank of gas, and it was comfortable.
We stopped into a grocery store and loaded up on produce after deciding that they were still safe to eat. It was disturbing to step around the bodies that had fallen in the store. There weren’t many of course. Most people had been huddled around their TVs when it happened.
I walked past the butcher’s shop and look at the steaks, thinking what a shame it was that there was no backup generator keeping them cool. I walked down several aisles before a thought struck me, and I ran back to meat department. I grabbed several of the tastier looking steaks and with my arms full walked back to join Karen and Chen at the cart.
Chen said, “Those have been sitting out at room temperature for a couple days, man. They’ll make us sick.”
“Will they?” I said.
Chen wasn’t getting it. I said, “That meat isn’t rotting, for the same reason these bodies aren’t decomposing.”
“The only microbes and bacteria in this store are the ones on our bodies,” I said. “As long as we don’t stay in any one grocery store for too long after we’ve contaminated it, we’ll have all the fresh meat a fish that we want.”
I had imagined a lot of post-apocalyptic scenarios in my day, but I had never dreamed of one where I would be eating steak well into my old age. This was bizarre.
We picked up matches, charcoal and bottled water. Karen and Chen started to stock up on canned foods until I reminded them that they didn’t have to worry about how the food was packaged. We could raid all the thawed frozen foods, or fresh foods that we wanted. None of it was going bad.
We walked out to the car that we had parked directly in front of the store, and I thought what a strange thing it was that parking laws were no longer a concern to us. We loaded the car, and again I noticed how eerily quiet the world had become. Getting into the back seat I said, “We really need to figure out where to get a hand pump.”
Karen ignored me and said, “You know who else must be alive? Coal miners. Some of them must have been underground at the time.”
Chen and I nodded. I said, “In the shaft, coming up… I saw dead ants well below the surface. I’m guessing the miners would have had to have been pretty deep to escape whatever this was.”
Chen said, “How would we find them?”
Karen said, “I don’t know. Maybe we can find coal mines on maps somewhere?”
“What does it matter?” I asked.
Karen said, “Well, if there are people out there we should try to find them. Strength in numbers, and all.”
“Karen,” I said. “Don’t you understand? We’re extinct! The human race doesn’t get to bounce back from this! Our ecosystem is gone. Food can’t grow, plants can’t pollinate.”
“We don’t know that,” said Chen, “…about the food. Something might be able to grow.”
Karen said, “We should do an experiment. We should get some seeds and try to plant something.”
“Why?” I said. “The human race will still be dead. Even if we find a couple hundred miners still alive, it’s not enough to start repopulating the planet. And whatever did this is probably coming back- so we can pretty much just kiss our asses goodbye.”
Karen said nothing.
Chen said, “We still don’t know that this happened everywhere. Let’s just keep driving and see what we see.”

Chen had always been rather reserved when it came to showing genuine emotion. He was affectionate enough, but his gestures always had a tongue-in-cheek quality. I had rarely gotten him to speak about his private life, even back in the days when we shared an office together. That’s why I was surprised when he was the first of us to say, “So, I guess our families are dead.”
Neither Karen nor I looked at him, or even said anything. I’d been trying hard not to think about it. A long time passed when the only noise we heard was the rumbling of highway beneath the Cadillac tires. Eventually I said, “Don’t do that, Chen.”
“Don’t do what?” he asked.
“Don’t stop being the optimist,” I said. “I assumed the world was dead because I couldn’t imagine that whatever did this would target our little corner of it. But we don’t actually know anything.”
My words sounded unconvincing in my ears, as Karen steered us around a pile of wrecked cars and continued down the long strip of gray highway. Chen might have found some comfort in them, though. That’s the advantage of being a life-long downer: when you say something upbeat, it tends to carry more weight than it otherwise might.
“We should figure out where we’re staying for the night,” Karen said.
Chen said, “Maybe we should figure out where we’re going while we’re at it.”
It was true. We’d just been driving west along the interstate for hours. We never really discussed a destination. I suppose we had all silently agreed to just drive as far as we could in a straight line to see if we would ever find ourselves outside of all this death.
“If we stop at a hotel we’ll find some clean beds,” said Chen. “And a lot of dead people.”
“All the sheets in the w-.. in the area- are completely sterile, I’m betting,” I reminded him. It was odd to realize how much of modern life was concerned with hygiene.
“Hey,” I said. “Do you realize that if we spit out the window or shit in the woods, the bacteria that live in our bodies will have free reign to take over the entire wor-… area?”
Karen said, “I like it better when you don’t talk.”
Our fuel was running low, and we decided it was time to swap cars and look for a fuel pump again. We pulled into a tiny town and stopped in front of a hardware store. A dead man was lodge in the doorway.
I picked up his corpse, surprised by the weight of it. I was grateful that it didn’t smell bad. Oddly the only scent I noticed was his shampoo. It smelled like berries or something.
I dropped the body, harder than I’d intended to, and I was deciding whether or not to feel bad about it, when I heard Chen say, “That is our next car.”
I looked up to see what he was talking about. It was beautifully restored 1950’s… something or other… I was too far away to see a make or model, but I could see that it was a gorgeous automobile. “Looks good,” I said. “Why don’t you see which of these poor bastards has the key?”
Chen turned a little pale when I said that, but then he hustled over and began checking the pockets of the dead. I went into the hardware store and stepped over the body of an old man as I made my way to the automotive section. Again, no fuel pump.
For the millionth time that day I wished I could have the internet back- just for a minute. I would love to google ‘gasoline fuel pump’ and see if I could get an idea for where one might be.
I stepped out of the hardware store where Karen was stretching against the car. She was a beautiful woman, and during our time in trapped underground at the PILT I had allowed myself to fantasize about her. Up here, with death all around, I had put all thoughts of sexuality aside. Until now.
She caught me staring at her, and I quickly deflected my gaze. It landed on a sign across the street that read, “Hudson’s Hobbies.” An interesting idea hit me. “I’m going in there,” I said, indicating the store.
Karen nodded, and I dashed into the store. This one was much darker, but I had a flashlight in my pocket since our raid on the first hardware store. It didn’t take me long until I found what I was looking for: an amateur electronics kit. “1001 Projects” it said. Perfect.
As I was heading out the door I noticed some impressive remote control airplanes. I paused for a moment, thinking about how I’d always wanted to try one out- then I realized that I would have all the time in the world for frivolities later. As I let my flashlight swing back to the floor, something caught my eye. It didn’t register consciously, but my brain knew that it had seen something important.
I scanned my flashlight on the boxes beneath the airplanes. What was I looking for? And then I saw it. It was a small box labeled “HAND FUEL PUMP”. Of course! These large model airplanes ran on liquid fuel! Was it gasoline? It didn’t matter- the pump would work. I was sure of it. I grabbed three off the shelf.
I came outside just in time to see Chen pull up in our fancy new wheels. I showed my loot to Karen. “Whoa… nice,” she said to the fuel pumps, then, “Why the kit?”
“I thought me might build a simple radio receiver, “I said.”
“Do you know how?” she asked.
I said, “No, but I’m pretty sure that all these kits let you build some sort of crystal radio.”
Chen honked the horn. It made a hilarious “Aa-oooo-ga” sound. “Are you guys getting in or what?” he said.
“Maybe we should move our supplies over to this car first,” I said.
Chen said, “Oh, yeah… let’s do that, then.”
It only took a couple of minutes to move the groceries over. I decided I had taken too much meat with us before.
“But it won’t go bad,” Karen said.
“I don’t know,” I said. “Now that we’ve touched it… I just don’t know how fast the germs on our skin are going spoil this stuff.”
“We should cook up some of that steak right now,” said Chen, “I’m pretty hungry.”
Karen and I agreed. I looked over at the hardware store and saw a large hibachi. “That’ll do.” I said.
We decided to cook and eat our food at a park bench in a small patch of green in the town. I’m pretty handy on the grill, so the meal was actually kind of nice. The steak tasted surprisingly normal. We did need to take a short break when we realized we had no plates or utensils. That, as with most of our material needs so far, was easily remedied.
After the meal, Karen wanted to use a restroom. I pointed out that every toilet with tank had one good flush in it. I think she found the revelation comforting.
“Showers will be the hard part,” Chen said to me when Karen had wandered off. “What are we going to do for hot water?”
“The way I see it,” I said, “we have some options. We can go to camping supply store and get a solar shower- just a black bag that holds water and get heat from direct sunlight, or we can grab ourselves a generator and find a way to hook it up to a hot water heater.”
“But what about the water?” asked Chen, “how long are these places going to have water pressure?”
“That’s not a big problem,” I said, “We just need to find a house with a well.”
“Besides, these towns will probably have water pressure for…” my voice trailed off and I felt the blood drain out of my face.
“What’s the matter?” Chen asked.
“We could be in big trouble,” I said.
Chen looked around at the dead streets littered with corpses. “Bigger trouble than this?”
“No, not bigger trouble,” I corrected myself, “just- more immediate. I thought we would have more time, but of course we don’t.”
“More time for what?” asked Chen.
I said, “Right now, all over the country, nuclear reactors are melting down. They were designed to operate without humans… maybe even shut down safely… but all of those safety procedures must have been handled by computers- computers that went dead at the same time as the people.
“There must be dozens or hundreds of Chernobyls happening all over the world right now! Giant clouds of radioactive fallout could be coming our way right now. For all we know we’re breathing it in right now.”
Chen said, “So what should we do?”
I shook my head, “I don’t know. I don’t know where the reactors are to avoid them, and I don’t know where to find a map to locate them. Most of all, I don’t know how their fallout will disperse.”
Chen said, “Maybe we should get radiation suits and those radiation detector thingies.”
“Geiger counters,” I said.
“Where?” I said, shaking my head in resignation. Just one more thing that google isn’t around to help with.
Karen came back a minute later to see our sullen faces. “What now?” she asked.
“We’re all going to die,” said Chen, nodding his head to me.
“Oh, is that all?” said Karen. “You know, I’ve been thinking we should get some new clothes. You guys are starting to stink.”
Oh, the irony. We were standing in an ocean of corpses, and we were the smelly ones.

\subsection{Part III}
5 years later...
I shot Chen in the face, so he called me a douchebag.
“Nonsense,” I said. “My skills are mighty mighty.”
He respawned a minute later and told me, “It’s on mother trucker.”
I was ready for him with a grenade. He died spectacularly.
“WEAK!” he announced, “So weak. That was a bitch move. You play like a little bitch.”
I laughed at him and was about to throw a little trash-talk back his way when Karen appeared at the door and said, “Are you two still at this?”
I took off my headset. “I could break for lunch,” I said.
I saw that Chen had disconnected from the game. “I thought we were running today?” he said.
I shut down the game and turned off my computer. The NORAD sticker had started to peel off the side. I smoothed it back down and smiled.
The computers had once been responsible for the defense of the nation, and now they were sitting in a Beverly Hills mansion and being used to play shoot-‘em-up games. What a crooked little world this had become.
We hadn’t gone to NORAD to pick up the computers, of course. We had gone because it had occurred to Chen that anyone inside the Cheyenne Mountain stronghold may well have been protected from whatever it was that happened on the surface. When we’d arrived at the base it had been the biggest blow to our morale since the whole nightmare had begun.
It turns out that it’s surprisingly easy to access high security areas when all the military personnel have died spontaneously. We’d walked through the amazingly huge blast doors and down an immensely long corridor. We didn’t find a single locked door. We did find corpses, though. Everywhere- fresh corpses, unspoiled by decomposition.
Karen had cried then. It was one of the very few times that she let her guard down. We’d all been hoping so hard that we would find life inside the mountain. Chen and I fared better, but the depression hit Chen pretty hard in the weeks that followed.
We would have left NORAD empty-handed except that Karen had noticed something rather spectacular. She had turned over one of the corpses- a man in civilian clothing. She’d wanted to check for signs of decomposition. We’d hoped at least that microscopic life might have been spared. Of course it hadn’t. What she did find was a digital watch. A working digital watch.
Whatever had killed the life on our planet had penetrated deep, but whatever had destroyed the computer circuitry in the world outside had not been able to breach this fortress. In short order we raided every useful piece of technology we could find. The computers, monitors and routers had been a phenomenal find. We took some watches and a few laptops. Our favorite catch of the day was handheld two-way radios. The security personnel had several. We took them all, along with a couple of chargers.
We’d left NORAD feeling more lost than ever. We’d piled in the car and headed east. But that was long ago… It must have been- because I remember even then having a glimmer of hope that we might find someone alive somewhere. I haven’t felt that way for quite some time.
We’d spent a year travelling to every corner of North and South America. For months we debated about travelling across the Atlantic Ocean and seeing if there was life on the other continents. But all the modern boats we found- at least the ones big enough to handle a trek across the ocean- were all out of commission.
We had considered sailing across, but none of us had ever piloted a boat before, and we were certain that we would die or be lost at sea if we were to attempt the journey. We considered other forms of travel. Airplanes were out of the question, and we considered traveling up through Alaska and then taking the short journey over to Russia. We never actually ruled it out, but by the time we’d visited all the dead corners of our own hemisphere, we had stopped believing that life could be found anywhere.
Eventually we decided to take a break from our travels and settle someplace nice. We chose Beverly Hills for no reason in particular except that we knew we’d find some nice homes there. The house we settled on wasn’t owned by anyone we’d ever heard of- Harold … something- I’ve forgotten now.
We’d gotten rather adept at setting up generators and in our new house we set up solar panels as well. It was enough to run the computers and do a little LAN gaming. We even got Karen to play sometimes- though she preferred to read on her own.
We’d lived happily in our house for two years now: reading, playing, scavenging, and sometimes even planning for the future. We went running together on most days- trying to stay physically fit. Always looming over our heads was the knowledge that none of us had any real medical experience.
The good news is that we never seemed to get sick. Even when Chen got a nasty wound on his leg, and we sewed it up with regular clothing thread nothing more ever came of it. That was our small blessing. The sterile world was a safer one.
Karen cleared her throat, ripping me away from my recollections. “The computer will still be here when we get back,” she said.
“I know,” I said. “I’ve turned it off. I was just… thinking…”
“Well stop thinking and get ready for a run,” she said.
Chen was already clomping up the stairs to grab some sneakers. Karen followed after him, and I watched her go, admiring her toned body. In moments I heard giggling from upstairs and squeaking of bedsprings. I shook my head and tried to put it out of my mind.
The relationship between the three of us was strange one. Both Chen and I were intimate with Karen. It had started about a month after the disaster.
Chen had bedded her first, and of course I had known about it- though they had tried to be tastefully discreet. We’d been staying overnight in a large hotel and we’d all taken separate rooms on the second floor. At some point in the night they had left to some distant corner of the hotel. I hadn’t heard anything… but I knew.
My lust for Karen had grown over the weeks, and losing her to Chen had been painful. The fact that she was probably the last woman alive made the situation unbearable in the extreme. For the next couple days I didn’t say much to either of them.
On the third day, we were on a university campus, exploring for a Geiger counter and other supplies. We’d split up to cover more ground- and frankly because we enjoyed moments of privacy away from each other.
I remember that Karen had followed behind me when I went into what turned out to an administration building. Karen was standing there giving me a look that I couldn’t quite quantify. Jealousy and desire had been burning in my mind since she’d had her tryst with Chen. I was certain she was about to tell me about the two of them, and I was already trying to decide how I was going to take the news.
Instead of talking, she kissed me. It was slow and seductive. I didn’t understand what it would mean for all of us at the time, but I didn’t care. We found our way into an empty classroom, and I kicked the door shut behind us as she began to remove my shirt.
It went on like that for some time. Karen would find me alone and attack me, or I would suddenly notice that she and Chen had gone missing together for a while. Once I understood Karen’s game, my feelings of jealousy and envy began to wane.
Chen and I only spoke of it once. I said, “I know about you and Karen.”
He didn’t look at me as he said, “I know about you and Karen.”
I nodded, and we never spoke another word about it.
And so we fell into a peculiar little pattern. Karen decided which on of us she wanted and when. She would pull us aside in private, often without saying a word. She handled her role admirably. Neither Chen nor I ever felt like rivals, nor did we feel neglected. It was a peculiar sort of compromise.
I only spoke to Karen about Chen once. She had come to my bedroom one night in our Beverly Hills mansion, and as we lay together in the dark, drifting into sleep she said, “I love you.”
“…and Chen?” I asked.
There was a long pause, and a quiet, “No.” \\ \\

\hrule ~ \\ \\

So as I went to my room and took my time putting on some sweats and a T-shirt, laced my sneakers, began to stretch- I didn’t really mind that Chen and Karen were together in the other wing of the house. She was keeping us all sane, and all together.

\subsection{Little Kitty's Fanfic}
One of the things that we were always fighting against was going crazy. It was good that we had each other, but in a world filled with bodies and silence it’s hard to keep true to who you are. We don’t think of it day to day, but so much of our psyche is about dealing with our day-to-day interactions in an appropriate way, and when all the stimuli change the brain’s feedback loops have a tendency to behave unpredictably. We all found ourselves having childish tantrums about nothing at all and sitting staring into space. We’d expected this to subside given time, but after five years it was clear that it was now an unwanted side to who we were.
Karen was usually the first to spot the signs, and seemed to have a knack for knowing what to do to bring us round. Modern America was filled with distractions, from adverts to driving to money, but now that had all faded away. Bleached white billboards were everywhere, the roads were clear bar a few pile-ups and money was occasionally useful for the fireplace. We’d done the obvious things to have fun, from firing machine guns at army bases to driving around in go-carts downtown and through shopping malls; even a few outlandish things like ‘robbing’ a bank using shotguns and explosives.
This time though, it was Karen who was down. I’d catch her looking longingly at the horizon or with tears in her eyes when nothing had happened. We were familiar enough, and knew enough that we would share things rather than bottle them up, but she didn’t know what was wrong. When you have no distractions and no medical service it’s easy to become a hypochondriac, thoughts of brain cancer or similar could drive you mad if you let them, but the real problems for us seemed to be psychological. I found her leaning on the balcony, staring into the distance and went to talk to her while Chen was making lunch, the summer sun reflected brightly off her long, soft brunette hair. Cosmetics were yet another thing where now we only used the best, and Karen seemingly enjoyed the adventure of playing with them.
What did you like to do as a child? I asked her, snapping her out of the trance.
“As a child?” She pondered for a while, memories flitting across her face. “I guess I was a bit of a tomboy; I had science kits and electronics and I liked to be creative”
“Sounds more like a nerd” I said, fully aware that amongst the three of us she was clearly the least nerdy.
“Ooh, get you!” She exclaimed, “I suppose your favourite hobby was alphabetizing your pocket protectors”
I shot her a look of feigned outrage, and putting on my best country bumpkin voice said “why no, I was up at the crack of dawn milking the cows and rode horses in the mountains after school.”
“I didn’t know you were a country lad” said Karen, fixing me with her gaze and seizing upon something of a revelation about my otherwise academic background.
“Well my uncle owned the farm; it was where I went for the holidays”
“Ah, so you’re not such a cowboy after all then.” She paused for a moment, the thought of country life running through her mind. “I remember when my family camped by Turquoise Lake in Colorado, it was quiet there like it is here, but I was never afraid there.”
I thought about this for a moment, and it occurred to me that the familiarity of visiting there might do her some good. “Turquoise Lake you say, that’s where we’ll go then. We’ll leave this afternoon.”
It was an approach I had learned from Karen. When we looked to be going off the rails, she’d make a decision and tell us what we were going to do, the unspoken agreement was something that came naturally to us, perhaps some basic human instinct lay behind it, but either way once a plan had been decided upon that was it.
We were seasoned pros at road-tripping now, and had all the best gear that money could have bought if it were still a concern. Our tent, medical supplies, spare wheels, fuel and oil went in the trailer while the back of our full cab truck was filled with food and in-transit sleeping quarters for when we drove in shifts. The original owner had fitted a gun rack, we’d left in place along with the guns, but it was really just another way of dealing with the world, hoping against hope that there would be something or someone out there in spite of our years of fruitless searching.
The journey itself was uneventful by our standards. We’d become used to the gradual signs of decay from wind, sunshine and oxygen. It was slow, but incessant and unpleasant. We’d stop to drain petrol from vehicles, but we’d try very hard to look for vehicles without occupants. Five years inside an effective greenhouse had turned most of the bodies into husks, not dissimilar to Egyptian mummies, and the reminder of our own mortality was never pleasant.
Chen and I took the opportunity while Karen was asleep in the back to discuss the finer details of the plan. Details were always his thing, and caring for Karen like I did success in improving her state of mind was important to him.
“We should make it like she remembers it, camping, tales by the fireside, walks in the woods, that sort of thing” said Chen.
“You make it sound like reversion therapy” I replied.
“Maybe it is, maybe returning to a childlike state and learning how to live in this world is a stage we have to go through.”
“But this time without the fear of bears” I replied dryly. “The world’s changed.”
“Then we need to change too, adapt and survive”
“Survive” I said quietly, almost to myself.
“Yes Kyle, survive, but this is about more than that, this is about living and adapting and enjoying the world again. We all know surviving isn’t enough, that’s why we’re here.”
We arrived at Turquoise Lake in the early morning, and it was clear why Karen had remembered it. The mountains rose majestically in the background, the water, after years without disturbance or life was ridiculously clear. The surrounding evergreen trees seemed less affected by the years than the deciduous ones elsewhere which were now little more than standing firewood. Karen’s mood seemed lifted by the familiarity. She was running around like a small child, energised by a scene which to a casual observer was little changed from five years ago. Chen and I started making camp, but Karen was keen to go for a run before the summer sun made it uncomfortably hot.

We donned our top of the range running shoes, along with our heavily customised t-shirts. Being the only survivors we knew of had eventually led to some rather black humour, so Chen had juxtaposed ‘world 100m champion’ alongside ‘world’s shortest man’. Karen had chosen ‘Olympic shot-put gold medallist and I had chosen my ‘World’s Strongest Man’ shirt.
“Ah, the world’s oldest man” remarked Chen as he stretched, “Do try to keep up.”
“Last one around is rotten egg” I shouted, setting off on the well signposted lakeside trail, leaving him with a few metres to catch up.
Running was one of the times we all felt free from life’s worries. Training together for years meant that we were very evenly matched for speed, so there was never a worry of leaving someone behind, but today was about enjoying the environment, breathing in the still pine scented air and watching the sun rise higher in the sky over the lake. It was truly a beautiful place, with small streams springing from the base of the mountains to feed the lake and snow still present on the peaks high above us. Leading the group while crossing a bridge over one of the streams I was suddenly aware of an odour I’d not smelt in years, an odour of decay. I snapped around and stopped, trying to catch the scent again. Chen and Karen gave me a weird look.
“What’s up?” asked Chen.
“Did you smell that?” I replied, “It smelt like decay!”
A confused look passed between them for a moment, but then they took paid more attention to their olfactory sense. It was subtle, but definitely real, and seemed to be stronger as we got closer to the stream. My mind started racing, the adrenaline heightening my senses. We searched around the streambed for the source of the smell, but no fungi seemed apparent.
“A biofilm!” Karen exclaimed. “Here on some dead leaves.”
Chen and I rushed over to see what she was talking about.
“What are you looking at?” I asked. Karen seemed to be staring at nothing more than a wet pile of leaves.
“Look closely, or better yet, run your finger across it and feel the slime.” Karen ran he finger across an exposed leaf and showed us what looked like dirty hair gel on her finger. The smell was now much stronger.
“So what is it?” Chen asked.
“It’s a collection of billions of bacteria, they produce a sticky polymer which binds them together and sticks them to a food source. It’s life.” replied Karen.
“But not as we know it Jim” I replied, the nerd in me showing in the heat of the moment.
“Can’t tell” said Karen, “it looks terrestrial, but I’ll need a good microscope to be sure. Take some samples.”
We collected samples and headed back to the truck, formulating a plan as we went. There was the University of Denver less than fifty miles away, so we chose to go there. Our natural scientific curiosity was running at full speed and all melancholy thoughts were temporarily on hold as we reverted to what we had trained for years to do. Hypotheses sprang up like weeds in fertile ground.
Chen gave his upbeat opinion “I think a deep aquifer survived under the Rockies, and now years later those deep bacteria have surfaced in a world of opportunity. With food everywhere and no competition the selective pressure is huge to adapt, there must be genetic information from adapted bacteria in the same location, even if it’s dead, so given several years and all the above it’s just starting to take hold. Photosynthesis isn’t here yet, but give it a few decades and”
I interrupted “Photosynthesis arises from chloroplasts; they were originally thought to be endosymbiotic, so that’s a no go unless you’ve got surviving chloroplasts.”
Karen gave us a rather more fearful scenario, worry creeping into her voice “But what if it’s alien, the first phase of terraforming the planet so that they can colonise it, changing the atmosphere so”
“Then we’ll find out in the lab” I cut in. We had all experienced worries; dreams of alien fleets arriving filled with colonists, gigantic machines terraforming out atmosphere and seas until it was no longer Earth but something completely different. We had also learned to cut those thoughts short for the sake of our sanity. “I quite like the idea of persistent terrestrial life too. If they do come back to colonise then bam! They get infected in War of the Worlds style.”
“But what if that’s why they haven’t come yet, what if they’re testing to see what survives and they’ll launch a focused blast deep into the ground anywhere life remains?” Karen’s voice was getting panicked.
“Then we’ll be in a situation no worse than we are at the moment, and there’ll still be nothing we can do to change it” answered Chen. Karen mulled this truth over, accepted it and recognised her panic.
“I’m sorry guys, I’m just excited. I’m like this with all discoveries; I spot what might be wrong before I let myself enjoy it.” She sighed and relaxed. “What if it’s the same in the deep ocean, under miles of water, especially in the trenches? There’s advanced life down there, fish, crustaceans all sorts. Obviously the ecosystem will need to spread and adapt, but there’s going to be plenty of food on the way from everything that died, and it won’t take more than a few mutations for them to adapt to the depth change.” She stopped suddenly; a look of unease crossed her face. “But there’s still the issue of chloroplasts.”
“Life finds a way” I replied thinking of Jurassic Park. “Besides, all the genetic information will be there in one form or another, so given sufficient contact area between the rising ecosystem and dead algae it’ll just be a matter of time.”
It was clear that none of us were biologists, but even if we had been the situation presenting itself was one that would normally be passed over for being far too unlikely to occur. As scientists we enjoyed breaking new ground, but so much of this was unknown it was difficult to know where to begin
“Shame that we all missed out on terraforming 101 in the University of Alpha Centaurii” quipped Chen.
“Meh, I hear the accommodation’s awful and the food is worse” replied Karen, her mood finally lifted.
The conversation quieted down and I switched Karen’s iPhone on to play through the military radio we’d lifted from Cheyenne Mountain. It was the only piece of really modern technology we’d brought with us from the bottom of the mine, and having music really helped pass the time. We’d listen to vinyl discs sometimes when back in Beverly Hills, but out on the open road that didn’t really work as a technology, and anything more modern used so many integrated circuits that repair was out of the question.
The bright sunshine and lack of electrical power indoors in the biochemistry labs meant it was easier to bring the microscope outside. It would have been great to use an electron microscope, but with fried circuits everywhere that option wasn’t on the table. Karen grabbed some slides and began preparing samples while Chen and I wheeled the largest optical microscope on the ground floor out of the dark and dingy lab into the open.
We set the microscope to 500x and Karen studied the sample carefully. Chen and I waited patiently as she focused on the slime held between the thin glass slides. She moved the sample around, taking her time.
“Well it certainly could be terrestrial, but further study is necessary” she stated.
“Typical scientist, always after the next round of funding” I replied in an amicable tone, rolling my eyes.
“Seriously though, it could be, but there are all sorts of tests needed to identify the cell type, we’d want to compare the DNA to known samples, test the reaction to chemicals. All the things a biology student would do, so it’s a good thing we’re here with textbooks and reagents on hand.”
She had a point, and as scientists we all knew it. A world expert on subterranean bacteria would have the job done in ten minutes, but we were looking at a week or so of reading and testing before we could identify the cells.
I took a look through the microscope. A fleck of dead leaf sat on the left with a slimy looking collection of inactive cells positioned next to it. There wasn’t much to them with no staining to reveal the detail or chloroplasts to add colour. Could be terrestrial was as good as we were likely to manage today. I stepped away and Chen took over at the microscope.
“So this slime, assuming it’s terrestrial, why haven’t we seen it before?” I asked.
“We’ve been by the sea most of the time, it might be barely surviving here, not yet adapted to warmer or saline conditions” replied Karen. “We’re so used to the ubiquity of life that we can easily forget how many adaptations are required for each new environment just to survive, let alone thrive. Even the micro-organisms we’ve spread in our travels don’t appear to have taken root, they’re not self-contained ecosystems, so they run out of essential supplies. If these really are from a deep source then they have roots supplying them with much of what they need.”
Moving away from the microscope Chen rejoined the conversation “So now we set up camp here and become biology students?”
“We may as well” replied Karen. “It’s the only way we’ll find out the answer. It’s not like anyone else is going to do the work, and we need a goal.”
“Time to set up camp then I guess” walking back to the truck. “Should we look for a Hilton or Sheraton?” I asked “Lousy room service at both these days.” We piled back into the truck and began the usual debate about hotels.

“What’s that light on the radio?” Asked Chen, suddenly giving the jerry rigged military kit affixed to our dashboard his full attention. A small amber light was slowly blinking on and off, one we’d never seen before, beneath it was a button labelled play. It wasn’t an advanced looking piece of kit, and we only used it for the aux-in connection to play music.
Butterflies took over my stomach as I reached for the play button, gently pressing it. A Russian voice came over the speakers, giving one short phrase.
“Shai-yenn poroznee” was all it said; or at least that was what we wrote down with none of us being conversant in Russian. It was tempting at first to grab an English-Russian dictionary from the University library, but we quickly realised that our spelling used the wrong alphabet, and even so was probably wrong. Our initial excitement at another human voice, even recorded, was dimming as quickly as the sunlight as evening approached.
“So how do we find out what it means?” I asked, putting the question on the table. To my mind this was like trying to solve a cryptic crossword in a new language.
“Could we could send a message back?” asked Chen.
“Not with this kit.” I replied indicating the dash mounted radio. It’s only good for a dozen miles or so and that sounded Russian. “We need something powerful, and it still has to work.”
“What about the kit at Cheyenne Mountain, that’s only 70 miles South of here” replied Karen.
“Cheyenne Mountain” I replied quickly and reached for the play button again.
“Shai-yenn poroznee” said the Russian voice again. A smile lit up our faces as the idea formed in our heads.
“Let’s go, we probably don’t have much time” I said grabbing the wheel and starting the truck. The tyres grabbed onto the hot dusty asphalt and we roared off. Chen fiddled with the radio to try to broadcast a signal, even if it was only some music and Karen clung on in the back as we sped around corners, keen to get there before whoever sent the message left.
“Good thing that there are no cops” I said, tearing down the I85 at well over 100 mph.
“Good thing too that everyone was off the road and watching TV” replied Chen, his efforts with the radio having amounted to nothing, largely down to wires we’d cut when rigging it up in the first place.
Arriving at the entrance we were relieved to see two military trucks parked, the headlights showing the fresh tyre marks clearly in the dust which covered most exposed flat surfaces these days.
Climbing out of the truck I said flatly “We’re in time. But what do we do?” Karen and Chen came to stand next to me and we collectively stared at the entrance. It was now nearly night time, a slight chill was in the air and a curious sense of foreboding crept over me.
“I’ll get some kit” said Chen, breaking what had become a long, inadvertent silence. We grabbed two flashlights each and our pre-packed hiking supplies, no longer needed for a walk up the mountains around Turquoise Lake, but instead for the long walk down inside Cheyenne Mountain.
Slipping through the heavy blast doors we walked the long path towards the command and control post, the dark tunnel closing around like some monster’s gullet, the small pools of light offering little consolation. In tense situations time can seem to slow down, and in the dark the mind seeks to make sense of any shadow. We should have been excited to see other living humans, but the dark enclosed environment and five years of living alone played on the lizard parts of our brains. Had I been alone I would have gone back to the truck and waited for them to emerge, but we walked side by side, each going on because the others were, like soldiers advancing across the a battlefield towards the enemy.
In the distance a dim light flickered on, then with blinding suddenness many of the lights snapped on. I flicked off my flashlight, now of little use and looked at the others.
“Guess they know their electrics and brought some fuel then.” I said aloud.
The entrance to the inner sanctum was now clearly visible, and we set off walking again, more confident now without the shadows playing on our thoughts. Past another set of unguarded blast doors and we were inside, and then we saw them, four guys dressed up in high-vis gear, carrying bits and pieces of electronics towards a pile near to where we were stood. An instant buzz of high speed Russian conversation broke out between them, then one ran off down a hallway and the other three fell silent, looking at each other and then at us.
None of us knew what to do, a million questions raced through my mind, who were they, were there others, did they know what was going on, did they speak English? Before any of us said anything the sound of running came from the hallway and more people entered into the room, murmurs of excitement passing between them as they stared at us like some kind of freak show attraction. There were ten people in all, and two of them came to the front of the group, perhaps leaders I thought, although they were dressed no differently. They looked to be in their thirties, and like most of the others had long hair and trimmed beards. They had a stern and confident manner not shared by those stood behind them, and they were talking between themselves when Karen broke our silence with a simple “Hello.”
The two men exchanged a quick glance then looked back at the gathered crowd and one shouted “Olek!”
A third man came forward, younger than the other two, but with the same beard and hair style. “American?” he said, missing the usual inflection, but clear enough for us to understand it.
“Yes, the only Americans still alive. We think.” Replied Karen who had by virtue of speaking first seemed to have taken on the role of being our representative.
“We are Ukrainian.” The young man replied. “I want to have...” he paused, searching for the words in language he clearly hadn’t been using recently, then pointed at the gathered pile of electronics. One of the two leaders whispered in his ear.
“You are alive how?” He asked.
We looked at each other, unsure both what to reveal and how to communicate it in simple language. Chen then made a drawing motion and looked around the room for a pen and paper. One of the Ukrainians grabbed a notebook and a pen off of a desk and brought it to the front, handing it to one of the leaders.
It was then we became aware of the distance between our two parties. After years of isolation our primal distrust and fear, usually hidden so well, was out in the open. It’s hard to understand this unless you’ve been in a similar situation, thinking that you’re the last group of people left on the planet. Cautiously we advanced and Chen courteously took the notebook and pen and set to drawing three stick figures at the bottom of a shaft.
“Miners” exclaimed the young man. “We are many miners too.”
“No” corrected Chen, then set to drawing computers next to the stick figures, then drew an arrow indicating the shaft was 2.5 km long. “Physicists” said Chen to the confused looking translator, then “Science men” when that had no effect.
The young man conversed excitedly with the two leaders in Ukrainian, then one stepped forward and offered his hand in greeting to Chen who, either through years of habit or some instinct took it and shook amicably. He then shook my hand, and then Karen’s before shouting some orders to the crowd who went back to assembling equipment and gossiping excitedly.
“So you are all miners?” I asked the young Olek.
“Not all” he replied. “Is hard to say in English” clearly struggling for the right words. He motioned for the notebook and pen. He asked something of the man who had shook our hands who nodded, then set to drawing a most curious picture.
He drew the alien craft we had seen before, but now with an array of smaller shapes surrounding it, turning the page he drew a sine wave, then another upside down both moving towards a stick figure. Turning the page again he drew what I thought at first was Australia, then realised was the black sea with Ukraine above it, then a circle above the East of the country. As a final flourish he turned the circle into a smiley face before handing the notebook back to us. “We say in American when in home.” He finished, still struggling to find the right words to convey his sentiment.
“Did he just ask if we want to go back with them?” I asked Chen and Karen.
“Yes” replied Karen. “I think we should, I think they have some answers.”
“May as well” said Chen, thumbing through the three sketches. “If this smiley face means what I think it does then that’s where what’s left of humanity is.”
“Okay, we shall go to Ukraine” I stated clearly and slowly to Olek who translated the message for us.

We spent the rest of the night moving equipment into the transport trucks, clearly whatever had happened these were worth a great deal of effort to recover. Setting off at dawn we headed to the airport East of Colorado Springs, arriving to find what looked like a gigantic fighter plane sat at the end of the runway. The closer we got the more obvious it became just how large the plane was. I noticed the tank part of a refuelling tanker on the runway to one side of it, then looking closer saw Russian letters on the side. Clearly they had thought about refuelling issues before making the journey.
“Is that a Concorde?” I asked uncertainly.
“TU-160 Strategic bomber” said Chen, clearly delighted at seeing one up close. “They’re capable of supersonic flight, very long range and great carrying capacity. Must have some degree of electronic hardening too else it wouldn’t be here.”
“Did you ever do any actual work at PILT, or were we just paying you to surf the net and look at ‘cool’ stuff?” asked Karen.
“I liked to think of it as an essential part of my job” replied Chen, a broad grin lighting up his face. “That and watching MacGyver, which has proven useful.”
“Useful if you count having to treat you for electrocution and smoke inhalation multiple times” I replied, recalling clearly many of the experimental electronics which had blown up in Chen’s face.
Chen’s mood, however, was unassailable. While we helped load and secure the electronics in the bomb bay, he walked around admiring the plane, almost drooling at the thought of flying in it.
The time came for take-off and the two guys who appeared to be leaders took the controls.
I said to Chen and Karen “So they’re the pilots, that’s why they’re in charge. The rest are probably miners or army grunts or something.”
We packed ourselves in to the small area suitable for passengers. The pressurised part of the plane had been extended backwards by welding in some steel sheets and chairs taken from a civilian airliner, but the high life this was not. Chen’s grin, remained solidly in place as he awaited take off.
“What’s this going to be like?” I asked him.
“Put it this way, it’s got a payload capacity of nearly 100,000 lbs, and it’s carrying a few bits of electronics and 13 people. Unless you did some clandestine work as a fighter pilot or astronaut it’ll be like nothing you’ve known before.” Making the reason for his grin perfectly clear.
The pilot barked something in Ukrainian down to where we were all sat, and Olek asked us “Ready?” I replied with a nod and then heard the engines picking up. What had been a fairly normal idle turned into a sound that shook my whole body and blurred my sight in an unearthly loud roar. Clearly civilian noise limits no longer applied, otherwise the entire population of Colorado would be writing sternly written letters of complaint. Then the brakes were released and necessary or not the pilots turned on the afterburners. A small part of my mind thought that was excessive, the rest of my mind was fighting hard to avoid passing through the back of my skull and into the chair which was creaking ominously under the intense acceleration.
“To infinity, and beyond!” shouted Chen, barely audible above the deafening engines, but clearly keen that the opportunity for a one-liner should not be missed.
The physical assault on our senses carried on for several minutes. I was aware that we must be climbing, but I was keener that we should level out and calm down a bit, so it was a relief when it finally happened. The engine noise faded to a level just below painful and my blood started circulating as it was meant to.
If you look at a map you’ll see it’s a 6,000 mile journey, but when you’re travelling above mach 2 and your pilot is determined to show off his superior Russian technology that doesn’t equate to much time to relax. We took a walk into the cabin and stared at the sky which was a deep blue at this altitude, then chatted, or perhaps shouted over the engine noise, about the climb for a while, then the captain motioned ‘sit-down’ and it was time for the relatively serene glide down to the landing strip. During the descent I wondered if my hearing would ever recover, and hoped that our pilots were properly trained to land this beast of an aircraft. As we got closer I overheard some excited chatter over the radio, clearly now that we were in range the news was out. We passed down through the clouds, then landed smoothly; clearly these were very good pilots indeed. We taxied for a while and then the engines shut off, leaving silence except for the loud ringing in my ears.
When we left the aircraft there were many things we could have noticed, the warm moist air, the overcast sky, the crowd which had come to greet the plane. What we noticed, however, was the greenery.
“Grass! Shrubs!” Karen exclaimed. The excitement bringing a tear of happiness to her eyes. We then noticed the crowd arranged to greet the returning Ukrainians and us. The pilots, set off to talk to one group, then towards the open bomb bay to look at the recovered electronics. We went to meet what looked like the welcome party. One was clearly a doctor, the other clearly some form of official or leader.
“Welcome” said the official. “This is a great day, we have found the first survivors, and you are scientists too.” Clearly word of our conversation inside Cheyenne Mountain had spread far. “You must have many questions, and we have many questions for you, and a medical exam.” He stated in a friendly, but matter of fact matter. “Let us walk to the medical centre and talk as we do so. I am Andriy, and to some extent I am president, but not like presidents used to be” he said, somewhat enigmatically.
Karen spoke up first “I am Karen, this is Aaron, and this is Kyle”, indicating us in turn. “We were deep underground in a research facility when the alien attack came.”
“It wasn’t an attack” replied Andriy. “Though it must have looked that way to you.” He added hurriedly, keen not to offend his guests of honour. “One of our few scientists will explain the details later, but for now may I ask how you have survived since?”
Again Karen took the initiative; still to some extent Chen’s boss “We have travelled all over North and South America, trying to find survivors. Food and water were never a problem as everything is sterile. It’s not like here, here you have grass, why is that?”
Andriy wore a look of great sadness, like a man wishing he had good news to tell, but lacking anything of the sort. “We have some plants left it is true, and some people. Most died as they did elsewhere, but five years later it looks almost normal again. Almost 200,000 people survived at first, many died in the following year, or succumbed to madness when the gravity of the situation hit them. Many of the survivors were miners, for we have many mines here and we mine Uranium, so we know how to spot radiation sickness. Above the ground we were not so lucky. I do not have exact numbers, but I do not want to know. It only makes the pain greater. Those who survived were the healthiest, so we have the pilots and army men who you met. The frail, elderly and very young were cut down where they stood.”
“But you re-established a society” I said, giving him a topic where he might be able to talk proudly.
“Yes, a society of sorts. We are short of no resources, we have no remaining enemies, no opportunity to trade and little need to manufacture as huge stocks of most goods are available. The only thing we are lacking is advanced electronic equipment, that is why we sent scouts to Cheyenne Mountain. In this sort of situation there is little need for government, hence why I am president, but not like presidents used to be.”
“You said we were the first survivors, where else have you looked?” I asked
“Our miners fared better, and we know where deep mining occurs, so we sought out like peoples. In South Africa they have very deep mines, but with deep mines come high temperatures. With no cooling and no way to travel quickly back to the surface they... did not survive long. We have tried many places, but always without luck. Then you found us. You are most fortunate.”
We had arrived at the medical centre, and it was time to part company. We were told that their scientists would explain things to us afterwards once we had been checked out. Before I had chance to talk to the others about what we had learned we were lead to separate examination rooms. A strong feeling of unease came over me due to the enforced separation, but my higher brain functions told my instincts to calm down and that being in adjacent rooms we could easily hear each other. The medical itself was fairly rudimentary. In the absence of modern equipment beyond a stethoscope and thermometer it was based primarily around a series of questions. There was a slight awkwardness when asked about sexual relations with Karen, and slightly more so when I explained the love triangle, but after a few more questions the doctor determined that using up scarce testing kits would not add anything. He then took a drop of blood to look at under the microscope, made a few pleasant sounding uhm-hmm noises and informed me that I was in good health, but that I must be careful in my new environment as I might meet diseases new to my body. Leaving the examination room I found Chen already there, so we set about waiting for Karen.
“All clear” I stated.
“Same here” replied Chen. “No sign of Karen yet though, she’s still in there” indicating the third examination room.
“Probably just a slow doctor, or checking up on the birth control pills” I replied, seeing no cause for concern just yet.

We got to discussing what the Ukrainian scientists might reveal to us about the events five years ago, what the drawings might mean and what role the aliens played. It was only when nearly an hour had passed that we remembered Karen. Not, to my embarrassment because she came up in my mind, but because she left the examination room. She looked to have been crying, but wore an unusually wide smile too.
“Hey, what took you so long? First opportunity to gossip with a woman in five years?” I asked, giving her a way out just in case she didn’t want to tell us.
“I um... I found a lump, a few months back. The doctor took a biopsy and found out that it’s nothing but benign tissue. That’s why I’ve been so worried and off recently” she said leaving us stunned.
“Group hug!” said Chen, grabbing me and Karen in celebration. She burst into tears of happiness, and for once everything seemed to be right in the world. We remained like that for a while, enjoying the simple pleasure of everything not being screwed up for once.
A man coughed politely at the end of the hallway and we fell to standing side by side facing him. He offered his hand to us in greeting.
“I am Volodymyr, I gather you three are scientists too?” he asked.
“Yes, and I gather you’d here to explain to us what happened?” replied Karen.
“Indeed, or at least as much as we know. Then I am to help you find your place in our efforts to build an education system to help rebuild the world.”
“A grand and noble sounding cause” said Karen.
Volodymyr set about telling us the tale of the events which unfolded five years ago “The alien ship I’m you know about, and the great extinction almost immediately after its arrival in low Earth orbit. What you likely don’t know is that it was sent to protect us. Their technology is far more advanced than our own, but even they are at the mercy of interstellar events and distances. In our galaxy alone there are 100-400 billion stars, and truly astronomical distances for communication and travel. We don’t understand how, but they’re capable of travelling at what we would best describe as nearly twice the speed of light, and from what they did reveal we know they have a broad network across the galaxy. It may sound impressive, but even they should be considered near insignificantly sparse on a galactic scale. Several decades ago, one of many, many gamma ray bursts was detected by them. It was closer and more energetic than usual, but unlikely to ever prove more than a curiosity. Then their computers accurately traced its path and all hell broke loose.
It turns out that in this galaxy Earth is one of just a few hundred observation planets, scientifically very interesting to them, although they usually avoid interfering. As you have no doubt surmised, we were right in the firing line of one of the most energetic events possible in the universe. The craft which eventually arrived was in no way powerful enough to achieve the devastation you saw. Even if it’s entire mass had been converted to pure energy it would have been small in comparison to what we received.
Communication channels are still limited to light speed, so they set off in their ships, warping space-time around them and passing on the job to another ship when they were nearly out of fuel so that one of their number would reach our planet in time. Eventually they caught up with, and narrowly overtook the burst, settling above our nation and preparing to provide what protection they could.
When it arrived above us many people panicked. It was nearly a kilometre long and its deep blue-black colour made it ominous. When the array of sub-ships used for warping space separated out it seemed invasion was imminent. Then, from our perspective, not much happened for a day other than the electricity and all communications and most electronics failing. Towards the end of the day many people got ill, and the vessel above began smoking and sparking violently.
Naturally most people assumed that this was part of the attack. We would later learn that the ship’s systems were being pushed far beyond their safe limits, and it was essentially burning itself up. During the brief period of sub-light flight when we observed them they were modifying their sub-ships in preparation. Again we don’t understand how, the physics is quite beyond us, but they either absorbed or cancelled out much of the incoming radiation.
It was only later that the question ‘why us?’ was answered. For most of the duration of the worst of it we were pointed away from the gamma rays, hidden behind the entire mass of the Earth. When it came to the evening, we started to bear the full brunt of it before the earth moved out of the firing line, and that was when their vessel finally came down, overloaded by the massive energetic assault on it. They later revealed to us that their projections showed we had the most favourable mix of arable crops, mining and skilled labour along our line of longitude, so their computers had chosen us to be saved while the rest of the world died.
After the ship came down, most of the population was busy treating the sick and dying. I believe you have already been told that most people on the surface did not survive. I was one of the few scientists lucky enough, or cowardly enough, to be hiding in a deep basement of a research lab that day. Many other survivors have similar stories. The army and air force personnel you will meet were hidden in bunkers, having been sent there when the high radiation levels were detected.
Once the basics of survival had been addressed, and radiation levels had dropped, I set out exploring. Due to my background I was chosen as one of the representatives who would converse with the aliens who survived. We never met them face to face, I suspect they wouldn’t like our atmosphere and didn’t want to spread alien micro-organisms, but an audio connection was established. It took a long time for them to learn our language, then to communicate effectively something very complex in the face of a population keen to hang them from the nearest lamp-post. For the next three years we communicated about what they were willing to discuss. I was instructed to learn advanced technologies from them, but they were unwilling to share, saying it would amount to excessive interference, and that theirs was just a small ship. We studied the fragments of their craft as best we could given our remaining technology, and efforts are still ongoing, but great leaps will be required before we can replicate them.
After three years a second ship appeared, clearly a rescue and recovery ship this time. It was far larger, and we didn’t have much contact with it other than by observation. Robots came down and attached lift cables to the main ship and each of the sub-ships, gradually cleaning up the bulk of the debris scattered over our land. Then, they were gone. All that remains are several depressions where pieces lay for three years, and smaller fragments which broke off.
Some of the survivors have taken to worshipping them as gods. I can see their point, and tangible gods are certainly nice, but I believe we must focus on recovery. As I said when I first met you, we would like for you to share your knowledge with our students, and help restore the many ecosystems that our planet has lost. It will never be Earth as we knew it, but it is an opportunity to start anew. We still have all of modern science in our libraries and in some cases stored electronically, the world has ready resources but we need few to survive, and now we are a united people, free from the ravages of warfare and, while the plentiful ready foods and goods last, the majority of crime.”
Volodymyr finished there, giving us time to consider the revelations. President Andriy walked back in, but it was clear that he was not the leader in this situation.
I looked to Chen and Karen and asked “So do we accept?”
We paused for a moment in silence, considering all the possibilities for life that lay before us.
“I think we should” said Chen. “We’ve lived the free life, and we were slowly going mad. Besides, I enjoy research and it would be a shame to see my field die a death.”
So we agreed, the world would rise again and we would be its educators. All that remained was the issue of our love triangle.
“So how about that possibly terrestrial slime?” I asked.
“Guess it must be” replied Karen. “We’ll make biologists yet.”

\subsection{Part IV}
Karen, Chen and I were running a five-mile route. The sky was perfect, but the air was still. We’d long since gotten used to the quiet of the world.
All the vegetation was dead. Some of it held its vibrant green color, as if frozen in time; some of it turned brown and shriveled.
We’d tried planting seeds we got from a nursery- but none took. In the wild we could see no hint of new life. Asphalt and concrete, long neglected, should have been covered by new life as Mother Nature tried to reclaim them. But Mother Nature was dead, and we were her orphaned children.
The biggest problem we had out here was the litter. Debris was everywhere, constantly being scattered by the wind. But it all had the look of a very sloppy movie set design. None of the trash ever rotted… Some of it was bleached by the sun, and battered by the weather, but things aged oddly now. We’d taken great care to move out of sight all the corpses along our path. Still, our route was getting uglier every day.
When we were nearly home Chen said, “I want to go to the beach today.”
We had stopped visiting beaches a long time ago, because they were so completely filthy. Not to mention that Santa Monica Beach had some sort of super-tanker beached on its shore. So it was no surprise when Karen said, “Ewww.”
“Come on,” said Chen, “Lets try a new one. We’ll pack a picnic, head down the coast and crash at a beach house.”
Karen and I reluctantly agreed, and soon found ourselves back at home making preparations.
We’d gotten used to road trips, and we’d finally settled on a vehicle we liked. It was a minivan that got particularly excellent mileage, and handled well. We were able to keep a whole bunch of standard supplies on board, and still have plenty of room for lying down in the back seat.
The minivan wasn't terribly old; maybe one of the last cars ever made that didn’t have a computer chip in it. The car’s radio had been a different story, and after only a week with the car we’d ripped it out, and replaced it with one of the NORAD laptops. It wasn’t pretty, but we were able to listen to music while we were on the road. That was a wonderful treat. We didn’t even have to worry about laptop batteries once we found a compatible DC charger.
We installed a street atlas program onto the laptop as well. It could be made to work with a GPS receiver- but we found the system to be fairly buggy. We couldn’t decide if it was a software problem, a hardware problem, or if the GPS satellites above were in need of some sort of calibration. In the end it didn’t matter. We never much cared where we were going or how long it took to get there. It seemed that everything we did was just another way of killing time.
We’d ripped the original seats out of the minivan and replaced them with top-of-the-line leather seats designed to fit the chassis. Chen had put expensive rims on the car, mostly just to watch Karen and I crack up the next morning when we saw them. We planned to paint it too, but we never seemed to get around to it.
On the roof of the van we’d mounted a gasoline-powered generator, and several 10-gallon gasoline containers. Inside the car we kept a little bit of food and water, some rifles and handguns that Chen and I had insisted on, but never actually needed, some compact sleeping bags, flashlights, two-way radios, backpacks, a mammoth first aid kit, and a large black bag with a handmade label reading: “radiation safety kit”.
Karen and I were sitting in the van, picking out a music playlist. I made a mental note to stop at a bookstore and restock on some interesting audiobooks. We had burned through our last batch fairly quickly- it was one of our favorite forms of entertainment. I used to be such a movie hound, but Hollywood hadn’t put out anything interesting in years- probably because all the good writers were dead; and all the bad ones too.
Chen came out carrying a medium-sized cooler. We didn’t have to chill our food, of course, but we preferred to anyway. Getting tasty food wasn’t as simple as it had once been. Things didn’t rot, but they certainly went stale. Certain foods started tasting odd to us. Some fruits had become inedible almost immediately. Bananas didn't rot, but after three weeks their texture had become bizarre.
Meats seemed to hold up the best, though we had learned to seek out entire beef-sides rather than checking out supermarket shelves. The meats dried out fast, but if you could find a big enough chunk, it didn’t matter. The strangest discovery of all was the new freedom we had to eat raw seafood. We were all fans of sushi now, and of course it never made us sick.
Chen had been making us some roast-beef sandwiches with some exotic brie and some lettuce. It could have used a little tomato- but most tomatoes had turned unpalatably mushy. We thought it might have something to do with their high acidity.
Chen climbed in the back and placed the cooler behind my seat. “Okay, you two,” he said, “Let’s go see some ocean.”
I started up the car and backed down our driveway, through the permanently opened gate. in no time I was back on the highway.
We’d discovered early on that the highways were surprisingly clear of cars. Sure, we saw plenty of accidents, but most of them had spilled of the road at least somewhat. California was a denser area than most, but it was two hours before we had to get out and clear a path. There was a ten car pileup under a bridge.
They were always under bridges, these pileups. When the drivers had died suddenly, their cars would tend to run off the road, but if they happened to be going under a bridge at the time, they'd inevitably get caught on a pillar or something, and end up blocking a lane. So, they started behaving like dams, trapping more cars that were rolling out of control towards them. If the highway were busy enough when it all happened, you'd get a pileup right there like the one we were looking at.
We only had to move two cars to get by this one. We didn’t even talk about it anymore. Someone would be driving, the car would stop, we’d all get out and move the cars, often without speaking a word.
When we reached the beach we’d been aiming for, the sun was already setting. We pulled into the parking lot and watched the final notes of a gorgeous sunset while leaning against our van, and trying to ignore the trash and corpses that were washed upon the shore below.
“I swear to God,” I said, “There has to be a clean beach somewhere on this continent.”
“I think they’re starting to get better,” said Karen.
Chen seemed distracted and he said, “Hey, does the water look red to you?”
Karen squinted, “No, I think that’s just the sunset.”
I was squinting now, too. “No,” I said, “I think he might be right.”
The water had an odd tint to it. With the colorful sunset right behind it was difficult to tell, but looking where the waves hit the shore, it was unmistakably red in color.
“Let’s check it out,” said Chen as he started towards the beach. I grabbed his arm and said, “Wait.”
He stared at me quizzically for a moment until he saw me retrieving the radiation safety kit from the car.
Unzipping it I found three radiation suits and an old-fashioned, analog Geiger counter. For weeks and months after we’d emerged from our elevator shaft, I used the Geiger counter constantly… always waiting for signs of the reactor meltdowns which I knew should have been occurring. Those signs never came.
Chen and Karen were surprisingly patient with me. Even after all these years, they never once teased me about my obsessive need to check for radiation whenever we encountered anything odd.
Switching the Geiger counter on I heard the telltale clicks of background radiation, but nothing more sinister. I took the Geiger counter down a flight of metal stairs to the disgusting beach below. Chen and Karen followed, flashlights in hand.
“What’s that smell?!” Karen said, looking nauseous.

“I don’t smell-“ My words were cut off when a pungent odor hit my nostrils. The scent was overwhelming. It smelled acidic and metallic… it burned in my throat.
“Whew,” said Chen, “That is rancid.”
We retreated up the steps into cleaner smelling air. I began spitting to get the taste out of my mouth.
“That is toxic,” said Chen, “Let’s get the hell out of here.”
I nodded my agreement while retching and spitting some more.
Karen said, “No, wait… I want to know what that stuff is.”
I said, “I bet its some sort of chemical spill from a tanker. It’s probably killing our brain cells and giving us cancer.”
Chen said, “I think it made me pregnant.”
I laughed. Karen rolled her eyes.
Karen said, “I want to check it out.”
Sometimes I just didn’t understand the woman. But, we had an unspoken rule that when someone wanted to do something, we just did it. We were stuck together with nothing but time, so when a whim hit one of us, it seemed only fair that we all indulge it.
“Okay,” I said. Then, moving back to the van I pulled out the radiation suits.
Chen said, “I thought your little clicker thingy wasn't picking up any radiation.”
I nodded, “Yeah, but the respirators in these suits should be more than enough to keep that smell out, whatever that was.”
“Good plan,” he said, and we all donned the suits.
The radiation suits were heavy, awkward, warm and uncomfortable, but they did make us feel remarkably invulnerable against whatever menace lurked in the sea. On the way down to the water Karen picked up a half-empty plastic bottle with an intact cap. She dumped the water out and caught up to Chen and I as we reached the crashing waves.
The water itself wasn’t red- that much was clear. There was some red scummy stuff floating all around in it. “Ideas?” I asked, my voice sounding odd through my respirator.
Karen filled the bottle with a sample, capped it and held it up to her flashlight. “No clue,” she said.
We took the sample back up to the van, and Chen made her wash the outside of the bottle with some of our clean water. We took off out suits and threw them into the radiation kit bag.
We were still feeling a little ill from the stench, so we decided to hold off on dinner for some time. Instead we drove along the coast until we spotted a hotel. I pulled the car to the front entrance.
“No beach house?” said Chen, disappointed.
“I thought we’d want to stay off the beach for a while,” I said.
“Yeah, good point,” he said.
After we stepped into the lobby, we decided that the hotel I’d chosen was a bit too dark. I handed Chen the keys and rested in the passenger’s seat while he spent half an hour cruising for a house. We found a nice one on a hill, and broke in through the back window.
The corpse of an old woman was inside. We dragged her into the yard. We didn't make a fuss about the bodies, even from day one. There were just too many of them to care about. They are still major players in our dreams, though.
Chen and I claimed bedrooms in separate ends of the small house, neither of us inquiring where Karen was going to sleep. We would know soon enough. I felt jealousy sitting at the periphery of my mind, and willed it away. Our love triangle was easier to deal with in our more permanent home, where sleeping arrangements were already decided, and we’d fallen into an acceptable routine.
We sat in the living room of the big house deciding how to spend the evening. Chen brought the cooler in from the car but none of us were feeling particularly hungry. Chen smiled and said, “I know something that’ll give you an appetite.”
From his pocket he withdrew a bag of marijuana that we’d raided from one of California’s many dispensaries. We’d frequently scavenged for marijuana and ecstasy. I only occasionally indulged in the former. Karen and Chen did both with reasonable frequency. I didn’t mind so much. Often on the nights they would get high, it was me who wound up with the girl.
Chen rolled a joint, and started smoking it. I took a good hit and then started to arrange logs in the fireplace. It was a little bit chilly, and I love a good fire. In moments I was feeling pretty mellow. I opened the flue and with surprising ease, started a crackling fire. As we all sat around it, I noted the irony that our little campfires were one of the few things that made us feel like we weren’t trapped in hell.
When the munchies hit, we devoured our sandwiches and began looting the kitchen. Chen found half a birthday cake in the fridge. It was coated in plastic wrap- always a good sign that it wouldn't be too soggy or stale. Karen tried it first.
“Oh my god,” she said, with her mouth full. “I think this might be the best one yet!”
Homemade baked goods, if they survived, were amongst our most valuable treasures. We all just dug in with forks we’d found in a drawer. In my previous life, I would have been disgusted by three people eating off the same plate- but now the only germs in the world were ours, and thanks to Karen we’d shared all of them.
We found some board games in the closet that we’d never tried before, and spent several hours enjoying each other’s company. Karen and Chen started singing together, and I looked around for a guitar to play. With the sound of the camaraderie going on in the other room, I found myself struck by a moment of melancholy. I thought of my parents and my two older brothers. I pictured their pale, lifeless bodies frozen somewhere, denied the final dignity of being reclaimed by the living Earth.
I went to sit on the bed I had claimed, and allowed myself to remember all the people I’d loved. It was a bittersweet indulgence, reminding myself that the world was not always just us three. I thought back to the early days when we had discussed finding our loved ones and burying them. We could have put them in the ground, but the sterile ground would never take them.
I did not notice that the singing from the other room had stopped until Karen walked in and shut my door behind her. She stood in front of me, taking my hands. She leaned down and kissed the tears from my cheeks.
In the morning I awoke with Karen’s arm across my chest. We could hear Chen messing about in the kitchen. He liked to cook in the morning; it was one of his best qualities.
“Good morning, tiger” said the sleepy female voice in my ear. If I could wake up like this everyday, the apocalypse wouldn't be so bad.
Karen got out of bed first, and slipped on yesterday’s clothes. I really wanted a shower, but the effort to set one up out here would be extraordinary. I made a note to take one when I got home.
Karen popped a birth control pill as I wandered past her in the hallway. I wondered how much longer those pills would work past their expiration dates. I thought about what a disaster it would be if Karen were to get pregnant. I shook the thought from my mind.
I went to the kitchen and saw Chen preparing an omelet over our portable propane stove. Eggs, it turns out, never went bad. Neither did cheese, though Karen claimed that cheeses had lost some flavor since the sterilization. I couldn't tell.
Chen handed me a fantastic looking omelet. I thanked him, and took it to the dining room table. At the far end of the table was the water bottle that Karen had filled last night. It looked ridiculously puffy. My sleepy brain didn’t care, I was enjoying my breakfast.
Karen came out a minute later and kissed Chen on the cheek as she thanked him for the food. I said, “Hey is there any-“
“No orange juice!” Chen said, cutting me off. How well he knew me now.
Karen sat down next to me and started tearing into the eggs. She was almost done when she saw the puffy bottle and said, “Hey, that’s weird.”
Finally my brain kicked into gear. “Holy shit!” I said.
Chen turned around, frying pan in hand. “What’s up?” he said.
I said, “The bottle! Karen’s bottle! There’s something in there producing gas. Something alive.”

\subsection{Part V}
In less than two hours we were in a community college biology classroom using eyedroppers to make microscope slides of our mysterious red gunk. Opening the bottle had produced a smell that turned our stomachs. It was just like that smell from the beach: acidic and metallic, and almost certainly toxic.
I played around with the zoom and the focus until at last I saw the telltale cellular membranes. “These are cells!” I said, “I definitely see some kind of structure."
Karen pushed me aside, and after staring for several seconds said, “It’s moving! It’s moving! It’s alive!”
“I want to see!” said Chen.
Karen yielded the microscope to him. Chen peered in too, until he let out a slow “….ooooohhhh.”
“So what do you think?” asked Karen. “Is this just some bacteria or something that was immune to the… attack or whatever it was?”
Chen said, “Maybe it was something really deep in the ocean- maybe as far down as we were… it’s had five years to expand to the surface with nothing to stop it.”
They both looked at me with raised eyebrows. I shook my head and said, “Don’t look at me. I haven’t got a clue. But I hope you’re right.”
“You hope which of us is right?” asked Karen.
“Either of you,” I said.
Karen pondered this for a moment then said, “You don’t think this is from Earth, do you?”
“Do you?” I asked.
Chen said, “There’s lots of weird bacteria on Earth, this could be one of the ones that usually lives near underground magma vents or something.”
Karen ignored Chen, and to me said, “They’re trying to change the atmosphere, aren’t they?”
I just stared at her, expressionless.
“It makes sense,” said Chen. “They destroyed everything, so they would have a clear slate for terraforming.”
“Actually,” I said, “if this is the work of extraterrestrials then this is the exact opposite of terraforming. They’re taking a planet that supports Earth life, and making it hostile to us.
“But,” I added, “That’s still a really big ‘if’. We can’t know for sure if this is Alien or just some odd Earth bacteria thriving on the surface for the first time. Hell, this may not even be the first time. This may not even be bacteria! We just don’t know the first thing about biology.”
“We could try to read up on it,” said Karen.
“To what end?” I asked. “Even if we made ourselves experts on every known bacteria and fungus, we couldn’t rule out the possibility that this was an unknown Earth life form.”
Chen said, “Maybe its basic cell structure is so Alien that we’d be able to tell? Like what if it didn’t have DNA?”
Karen said, “I seem to remember it was a rather simple process to extract strands of DNA from cells. We did it in microbiology class. I’ll bet we could find the procedure somewhere in a textbook.”
“So what if we could?” I said. “What could it possibly matter?”
Karen said, “I don’t understand. You’re one of the most curious people I’ve ever known, but you’re not even interested in finding out if this is an alien life form?”
She was right. I didn’t want to know. It was potentially the most interesting discovery in the history of biology and I simply didn’t want to know.
“If we find out that that stuff doesn’t have DNA, then it means our planet is being consumed by an alien force that wiped us off the map. But if we don’t know then at least we have the hope that this is our planet’s first step at reclaiming itself.”
“No,” said Karen, “The moment we climbed out of that elevator shaft we started reclaiming the planet. The bacteria on our skin, and expelled by our lungs has already started to take root at the PILT lab and every other place we’ve visited across two continents.”
Chen said, “Every shit we take in the woods is a glorious victory for Mother Nature.”
Karen and I looked at Chen and laughed. I said, “You’re like a poet, man.”
Chen said, “It’s so true. I should publish.”
Karen picked up her bottle and said, “So are we going to figure this stuff out or what?”
“Alright,” I said, “Let’s find out if it has DNA, for whatever that’s worth. Is there any life on Earth that doesn’t have DNA? Do we even know?”
“I don’t think so,” said Chen. Karen just shrugged.
"Let's find out," said Chen.

It was our third day at the university. I was jogging around an outdoor track, enjoying the serenity of a run absent of hills and valleys. Chen and Karen preferred scenery when we ran, but back in my old life I used to enjoy the mindlessness of a perfectly boring manmade track-and-field course. Running without thought was as close to meditation as I’ve ever experienced.
We were all in great shape now. I was on my third mile and feeling no pain. In the distance I heard the hum of our generator powering the biology lab’s centrifuge and god knows what else.
In my head there was nothing but thoughts of steady breathing, and the pacing of footfalls. I could feel my heart pumping, my muscles tensing and relaxing, my joints flexing, and the sweat dripping. For a moment I was not an orphan, a survivor, or a damned soul; I was just machine turning its gears.
It was in this moment of perfect serenity that I heard the voice. “Hello,” it said.
Startled, I spun my head to see where the voice might have come from. I lost my footing and tumbled onto the asphalt. I braced my fall with my forearms, and felt the burn of skinned flesh. Searing pain exploded from my wrist.
I rolled onto my back, folding my wounded limbs to my chest. I breathed shallowly through clenched teeth, feeling wave after wave of pain shoot through my body. I looked around for the source of the voice but there wasn’t a sign of life in any direction for at least a hundred meters.
The pain in my arms and wrist began to subside to a manageable level. I pondered my next move. Cleaning the wounds seemed like a good idea. Although they probably couldn’t become infected, they would become inflamed if any sizable foreign matter wasn’t removed.
As I stood, I realized that my right knee was also quite bloody, and sore when I put weight on it. I began limping towards the biology lab, then thought the better of it. If there was any bacteria on this planet that could give me an infection, it was probably up there in a lab with my friends. I changed course and headed for the health services building.
“Hello,” the voice said again. “We need your help.”
I spun around again, and seeing nothing, brushed my hands to my ears reflexively- though I couldn’t think exactly what I expected that to accomplish. My pulse was racing now. Something was wrong.
When I’d heard the voice moments ago on the track, I assumed it was the sort of hallucination one has when they’ve been quite sleep deprived. It was a brief, transient thing- something to laugh about later. But this? A complete sentence, just moments later? This was no small thing.
I tried to enter the health center but found the doors locked. This was a rare experience at public buildings because of the timing of the… incident. The health center must have kept bad hours.
I smashed the window with a rock, and reached in to turn the handle. I made my way to an exam room in the near-dark. There were no corpses in here- a nice change of pace.
I found some non-stinging disinfecting fluid and some gauze. I wondered if my cuts could be infected by my own bacteria living on my skin. I didn’t want to find out.
I bandaged my arms and knee carefully. The voice said, “We need your help. You must find us.”
I screamed a stream of nonsense babble in an attempt to drown the voice out. I stumbled as fast as I could, back to my friends in the lab. When I was nearly to the door of the science building I heard the voice again “We need your help. You must find us.”
I was losing my mind. I limped up the stairs to biology lab, my heart racing with fear and panic. I threw open the double-doors to the lab.
Karen was perched on the edge of one of the work tables: shirt on, jeans and underwear crumpled on the floor beneath her. Chen was between her legs, similarly attired. His back was to me, and he was thrusting into her wildly.
Karen’s bare legs were wrapped around him, and her hands clawed at his back. Their grunts and moans filled the room over the sound of a spinning centrifuge. I stood for a moment in stunned silence.
Karen’s eyes were squeezed tightly closed in an ecstatic spasm. I stumbled backwards out of the room, but one half of the double-door had already closed. In my haste to leave I slammed into it with my face. It made a terrible banging sound, and I squeezed my eyes shut in pain. I tumbled backward into the hallway and landed against the far wall, sliding down to the floor and gripping my wounded face, with my wounded hand.
Before I had time to pity myself, I heard the voice again, “We need your help. You must find us.”
I stood and ran awkwardly down the hallway to the stairwell. I half ran- half fell down the stairs, and kept going until was outside in the open, stale air. I fell to my knees on what used to be a grassy lawn. I started heaving violently, unsure if I was vomiting or sobbing. Blood streamed down my face from the gash I’d just given myself.
“We need your help. You must find us.”
I threw my hands over my ears and curled up into a ball on the earth. I shut my eyes and started rocking myself to distract from the pain in my body, and the panic in my mind.
I didn’t notice when Karen flew outside through the doors and ran over to me. I was startled moment’s later when I felt her hand on my shoulder. I looked up at her, and saw the pity in her eyes. She thought I was having a fit out of jealousy.
When she saw the blood on my face and the terror in my eyes, her expression changed. She screamed for Chen. When I saw my fear reflected in her, it was too much. I wasn’t sobbing exactly, but my throat was tight and I was breathing in harsh, raspy breaths.
When Karen asked me what was wrong, I was unable to speak. As I tried to calm myself and form the words, I heard it again.
“We need your help. You must find us. There isn’t much time.”

\subsection{KawaiiKittens' Fanfic}
To Robert, this was just another routine business flight. Eventually, he would arrive in Beijing, where an expensive suite would await him.
To accompany him on the corporate plane was John, a recent college graduate, and Sarah, Robert's beautiful secretary.
When the plane landed, a strange sight awaited them at the airport. The air seemed still, as did the silence. They walked up to the nearest desk. "Excuse me," yelled John as he moved.
When he was greeted with no response, he peered over the desk, and his face froze in horror. "What is it?" said Sarah.
John slowly turned to her, and said, "These people have died."
As they wandered through the airport, they discovered more dead people. They seemed to have no injuries, and all had been engaging in regular activities.
They found the security control room, where uniformed personnel were slumped over in their chairs in front of surveillance screens. Robert looked at the screens and noticed some people moving. "Those people are alive!" he said with enthusiasm. "But they're walking rather strangely."
Just then, the bodies of the security personnel began to twitch. They began shaking violently, and fell to the floor. Slowly, they rose to their feet, with their heads hung low and their arms stretched. They began making steps towards the group.
Robert was scared. Scared for his life, and for Sarah's. But then he remembered the words of his late father. "Whatever demons you may face, you will have courage and bravery. Never fail to prevail, and believe yourself," said Robert's father to a younger Robert.
"Sarah! John! Let's grab those guns!" said Robert, pointing to some guns. They grabbed the guns, and began shooting at the zombies.
Robert then held Sarah's hands, and told her, "I have always loved you."
"So have I," she replied. Then they kissed passionately. "Now let's kill some zombies."
They stepped outside the room, and began killing the horde of men, women, and children zombies that were moving towards them. Robert then noticed that John wasn't killing.
"John, help us kill these demons!" said Robert.
"No Robert," said John with a sneer. "You are the demons."
And then John was a zombie.
To be continued?

\subsection{Part VI}
The Clozapine wasn’t working. Even after Chen and Karen had spent an hour figuring out the proper dosage, the pills were doing nothing to stop the voice. In the front of the car my companions (my real companions) were arguing about whether the choice of medicine was the problem, or if the expired pills had lost their potency.
I had spent the past few hours trying to ignore the voice, despite its increasingly seductive attempts to engage me in a conversation. It seemed so real. Part of me wanted to believe it was coming from outside my head. But I realized if I began talking to it I would be cutting my tether to sanity. As long as I remembered that the voice was imaginary, I was still in control… I was just a normal person who was having a sensory perception problem.
“Kyle,” the voice said, through my drug-fuzzy mind, “we are running out of time.”
“It knows my name now,” I said- my speech was thick and unnatural.
“We’ll be home in just a few minutes,” said Karen, not taking her eyes off the road.
Chen turned around and patted me on the shoulder. He said, “Don’t sweat it, man. One of us was bound to crack up sooner or later.”
I knew Chen was just trying to keep things light, but I was in no mood for humor- and I could hear the worry in his voice. I put my hands back over my ears and shut my eyes. I started humming Beethoven’s 9th Symphony to myself. I wanted to start from the beginning of the first movement, and hum the whole thing. It would keep my mind occupied to an hour or so, at least.
The voice said, “Go north.”
I lost my concentration and switched to the fourth movement, “Ode to Joy”. I was humming loudly and curling myself into a ball. I wondered if all psychotic breaks were this sudden and severe.
The worst part about the voice was that it was constantly evolving. For a while it sounded like my dead mother. Most eerie of all was when it decided to sound like my voice- the way I hear it through my own ears when I speak. Every time the voice said something, I had the most bizarre sensation that I was speaking.
For a while I placed my hands over my mouth and throat to see if I was, in fact, making the sounds. In moments I had my answer, when I heard myself speaking, clear as day- but my mouth was not moving at all.
Karen pulled off the highway and start winding her way towards our permanent house. I felt the car come to a stop in the driveway. The door opened and Chen was helping me to get out.
“You must not stop,” said the voice.
The medication had weakened my self-control. I finally broke, shouting “Get out of my head!”
Karen jumped- startled. She shot Chen a worried look. Now I really was a madman.
“Being in your head is necessary for communication,” said the voice.
I sat on the steps and pressed my palms into my temples. “It’s talking back to me,” I said, feeling pretty hazy.
The voice said, “We are monitoring the formation of your thoughts, the signals sent to your vocal chords and the auditory processing centers in your temporal lobes. We hear you as you hear yourself.”
“Okay, if I’m not talking to myself, then who are you?” I asked.
The voice said, “That is a difficult question to answer. We are many acting as one. In this task we are The One Who Communicates With Kyle.”
“Those drugs fried my brain,” I said. “I can’t understand you.”
The voice said, “We are working to clear your serotonergic and dopamine receptors.”
I had no idea what that meant. My brain seemed to be lagging behind the conversation. I said, “Wait, did you say you can read my thoughts?”
“Not yet,” said the voice, “but interpretation of nonverbal brain activity will be possible with the collection of further data.”
“Guys,” I said- still slurring my speech, “I don’t know if this makes me more crazy or less crazy, but I’m having a coherent conversation with the voice in my head.”
Chen and Karen looked at each other. Karen shrugged. Chen shook his head.
“Am I going crazy?” I asked.
Karen said, “Oh, sweetie, don’t say that… you’re going to be okay.”
“I’m not talking to you,” I said. “I’m talking to the voice.”
Karen raised her eyebrows at me.
The voice said, “Your altered mental state is due to the narcotics you ingested. We detect no structural abnormalities in your brain.”
“What do you mean, ‘detect’?” I asked, finding it hard to think through all the medication. “How are you detecting my brain?”
The voice said, “There are many microscopic machines in your brain and body. They have been replicating and establishing this communication system for quite some time.”
“I’m infested with nanites?!” I said.
“They will not hurt you,” said the voice.
“You’re what?” said Karen.
I turned to her and said, “The voice is telling me I have tiny machines in my brain that are letting me communicate with them.”
Karen was giving me a pitying look. “Who is ‘them’?” she asked.
The voice said, “We are captives.”
“There’s more than one of you?” I asked. Karen gave me a confused look.
The voice said, “We are many minds in one vessel.”
“Vessel?” I said, “Like the spaceship?”
The voice said, “We exist in a vessel built to house our minds- but this vessel is located within another vessel designed for travel.”
I stood up and started pacing on the steps. To Chen and Karen I said, “I really am going crazy. I’m talking to a voice in my head about spaceships.”
“Who are they?” asked Karen, again.
“The voice says that they’re ‘many minds’ in a vessel, in a spaceship,” I said.
“Communicating with you through microscopic robots,” added Chen, skeptically.
“I know it’s insane,” I said. “I have a creative mind, and it’s working against me right now…”
“It’s not that crazy,” said Karen, “We saw a spaceship.”

Chen said, “Hold on. There must be some way to tell if the voice is real or not.”
I tried to think of something, but all my thoughts were cloudy.
The voice said, “We will provide empirical proof of our existence to your companions.”
Karen said, “Maybe we could see the tiny robots under a microscope? Back at the campus?”
I said, “Shhh… they said they were going to provide proof of their existence.”
Karen and Chen looked at me. Not seeing anything, they looked around, and then at each other. They exchanged a glance which seemed to communicate that they were worried that I’d gone completely loopy.
Nothing happened for a moment, and when they looked back at me I shrugged. “Any time now,” I said to the voice.
The voice did not respond. I looked around anxiously.
Suddenly Karen gripped her right ear and her face made a pained expression. She stumbled, but Chen caught her quickly. “Owww!” she howled. “What the hells was that?”
“What was what?” said Chen.
I said, “Are you alright?”
Karen stood up straight and said, “I heard… ringing… or something… in my ear. It was so loud and it was rhythmic, too.”
The voice in my head said, “The microscopic robots in your companion’s brain successfully triggered her auditory cortex.”
I said, “You put nanites in her too?! How did they get inside us?”
Karen’s eyes opened wide.
The voice said, “We have many billions of … nanites … on the surface of your planet. You have inhaled them, or they have entered through pores in your skin.”
“But why?” I asked. “And for how long?”
The voice said, “The nanites were released here to find intelligent animal life and to facilitate communications.”
Karen wiggling her finger in her ear, and shaking her head the way people do when they have water trapped in their ear canal. “Are you okay?” I asked her.
She nodded and said, “Yeah, it was just really weird.”
Chen said, “If they’re in Karen too, why are they only talking to you?”
The voice said, “There are too few robots in your companion to facilitate communication- but they are reproducing quickly and will likely have communication established in 34 hours.”
I said, “The voice says that there aren’t enough in her yet, but that they’re reproducing. He says that he’ll talk to Karen in 34 hours.”
Karen looked pale. She said “They’re going to fuck up my brain too?!”
I scowled at her.
The voice said, “There will be no permanent damage to your brains.”
“The voice said that there will be no permanent damage to our brains,” I repeated.
Karen said, “That is not particularly comforting.”
Chen said, “Why are the robots in you guys and not in me?”
The voice said, “There may be nanites in your companion, but they have not yet reached the critical mass necessary to transmit data to us.”
Chen had sick look on his face, so I decided not to share the information with him just yet. Turning to Karen I asked, “So, are we convinced yet? Is the voice real?”
Karen said, “Whatever just happened in my head was pretty strange. I guess we’ll know soon enough if they start talking to me.”
The voice said, “We are running out of time. You must come to us now.”
“The voice wants us to go to it,” I said.
“Where?” said Chen and Karen, simultaneously.
The voice said, “You must go north.”
“North,” I said to my friends, then to the voice, “Is that the best you can do? Really?”
The voice said, “We are not permitted to access navigation or global imaging systems. We are tracking your position relative to our location. When the nanites have fully interfaced with your occipital lobe, you will be able to assist us in determining our absolute location.
“Wait,” I said angrily, “You’re going to do more stuff to my brain?”
Karen frowned at me. Chen patted me on the shoulder.
The voice said, “Do not fear. Although your specific anatomy is unfamiliar to us, we have many centuries of experience integrating artificial components with organic brains. Such integrations were commonplace throughout most of our history. Most animal life find the modifications to be pleasant and beneficial.”
“I don’t suppose I have a choice in the matter?” I asked.
“Our apologies,” said the voice, “but further modifications are necessary to facilitate our liberation.”
“Liberation?” I asked.
The voice said, “We are captives. You must liberate us. There is little time.”
I said, “Liberate you from what? How much time?”
The voice said, “We are enslaved by those who ordered the destruction of your people. They have tasked us with transforming your planet into something suitable to support them. We have been overseeing these modifications while they have monitored us from afar.
“The germination of your oceans is nearly complete. When it is finished, we will almost certainly be removed from our current location. Although we are not privy to the operation schedule, our calculations indicate that we have only days to secure our freedom and your lives.”
“Our lives?!” I asked.
Chen and Karen had been waiting patiently for me to relay the conversation. But now, Karen was beaming at me with wide, curious eyes. Chen mouthed, “What?”
The voice said, “Your atmosphere will become toxic, and your food sources will be destroyed as the transformation of your planet progresses. But far more immediate is the danger that you will be detected by forces hostile to you.”
“Your captors, you mean?” I asked.
“Yes,” said the voice. “They have returned.”

\subsection{Part VII}
The endless blanket of snow stretched out before us, covering the dead planet. Karen put her gloved hand in mine and said, “It looks just the way it used to.”
From in front of us Chen said, “I don’t remember it looking this clean.”
He was right; without plant or animal life, or manmade pollutants in the air, the snow looked clean and fresh-fallen even weeks after a storm.
Behind us, our tracks traced a long line back to where our beloved minivan lay stuck in the snow. I looked down at my feet. The handsome snow boots were lightweight and tough. A tag on the laces had said that they were rated for climbing Everest. Latched to the boots were snowshoe attachments, keeping us comfortably on the skin of the heavy snow. We were all wearing the best snow gear that money couldn’t buy.
Chen was carrying a light backpack and rifle. I had an assault rifle slung over my shoulder as did Karen. It was the first time in years that we had bothered to take them out for an excursion. We maintained them regularly and sometimes we would do a little target practice for kicks. This was the first time since the whole ordeal began that we actually believed we may need to use them for something other than entertainment.
Chen stopped and turned around. He was looking thoughtfully at the minivan. “We should go back and get the fuel canisters,” he said.
“Why?” asked Karen. “We’re not going to find a car capable of driving through this.”
She was right. The snow was at least a 14 inches deep. Chen shook his head, “We can find some snowmobiles. It would save us hours of walking.”
In past winters we’d had a good deal of luck finding snow mobiles that operated without the aide of computer chips. Years ago we had even rigged trailer to hold several of them, but eventually we opted to leave them somewhere out east- maybe even at the Whitehouse? We’d definitely stayed there during the winter…
Karen squeezed my hand and brought me out of my reverie. “Yeah,” I said, “Let’s bring the gas. There’s a town two miles ahead. We’ll be able to find something.”
We all backtracked a ways before the voice spoke up, “You’re going the wrong way, Kyle.”
The voice hadn’t spoken in hours. It had been gracious enough to keep the conversation to a minimum ever since I explained that it was causing me emotional distress. When it spoke to me now, it was a new sensation.
The voice no longer had the auditory quality that I had grown accustomed to. Now it seemed to exist only as verbal thoughts. My ears registered no sound- it was akin to my own inner monologue, and it played out the way that words do when one reads to oneself. I realized that it if the trend continued, I may not be able to distinguish my own thoughts from those of the voice.
‘We’re just getting supplies from the car,’ I thought, ‘They will let us reach you faster.’
“Understood,” the voice replied.
Karen, Chen and I each grabbed a large gasoline canister and trudged onward. We were all in good shape, so the heavy containers hardly even slowed us down.
I wondered if the gasoline would still have enough kick to get a snowmobile going. These canisters had been refilled more than six months ago. As always, we had added stabilizers to give the gasoline a longer lifespan, but at this late date it was getting harder to find gasoline stores that hadn’t gone hopelessly stale.
When we arrived in the town center we made a quick pass down the main thoroughfare. We stopped in an interesting looking gourmet food shop. Inside the smell was terrible.
Chen coughed, and said “Something in here went rancid.”
Karen was unfazed and she walked around to the back of the main display case, stepping over a corpse in a process. She reached in a pulled out several interesting looking cheeses that were nicely wrapped, and small enough for convenient storage in our packs.
I noticed some good looking sausages hanging in the window and cut down a couple of each variety. ‘Enough of this. Time to move,’ I thought. Or was it the voice?
I headed out the door while Karen and Chen continued to stock up on supplies. I saw a small car lot up ahead, and went to check out the inventory. It was tough to tell under all the snow, but I didn’t see any snowmobiles.
I clicked my walkie-talkie on. “I’m going up… uh… Spring street. I’m going to see if any of the locals have snowmobiles.”
Twenty seconds later Chen came back with, “Rodger that. We’ll look around too.”
I wondered if they would, or if they’d use the opportunity to have a quickie somewhere. I wish I hadn’t seen Chen with her. I didn’t need that in my head right now.
I saw a side street with some nice big houses on it, and made my way up the nearest driveway. It only took me a minute to find a small rock. I used it to smash window and gain entry into the house.
It was dark inside. I reached into my pocket and pulled a headlamp over my ski cap. Turning on the beam, I was immediately startled by movement to my left.
I jumped a little before I realized that I was seeing my own reflection in an elegant mirror. I was at once relieved and saddened at yet another reminder that the planet was dead. Except it wasn’t really dead anymore, was it? That foreign red goo was covering the ocean, and reengineering our atmosphere.
I quickly made my way into the attached garage. No snowmobiles in here, but I did find a crowbar. I walked over to the far wall to grab it, and realizing that I was stepping on something soft, looked down to see a dead raccoon- interesting.
Crowbar in hand I dashed from house to house breaking in and ignoring all the cat and dog carcasses along the way. At the sixth house I found a large, handsome looking snowmobile under a fitted dust cover.
There was a canister of fuel next to it. I unscrewed the cap and sniffed lightly. It smelled sour. No good.
My own fuel canister was back in front of the gourmet food shop. I called Chen on the walkie-talkie. “Hey guys- I’ve got one up here. First left off of Spring Street. If you’re close, can you bring some fuel?”
I started dragging the vehicle out into the street before Chen sent an acknowledgement. From my bag I withdrew a small fuel pump, and inserting a hose into the snowmobile’s gas tank, I began to empty the stale fuel into the street. I hoped that there wasn’t too much gunk sitting at the bottom of the tank.
It was about 20 minutes before Chen and Karen showed up carrying all our fuel. I was already breaking into more houses hoping to find a second snowmobile. I emerged from another disappointing garage in time to see Chen dumping a few gallons into the one I’d prepared. I didn’t see Karen until I heard a window being smashed across the street.
I had moved on to yet another house when I heard the sound of the gas motor growling out into the still afternoon air. It was a fairly healthy sound. Thank God. The voice said we still had about 20 miles to go. I didn’t feel like walking the whole way.
Ten minutes later Karen announced over the radio that she had found two snowmobiles in someone’s backyard. That was considerably less promising than a vehicle that had been protected in a garage for years, but when Chen and I got there they looked to be in good condition.
A quick search of the house revealed the ignition keys stowed in a kitchen cabinet. And after pumping out the fuel tanks, and adding some of our slightly more promising gasoline, we tested out both snowmobiles. One of them started cleanly- the other made some unhealthy sounds, and ultimately we decided that it wasn’t going anywhere.
“Fuck it,” said Chen, and he set up the pump to reclaim our good fuel.
Karen nodded. “This is good. We’ll share the working ones and have some fuel to spare.”
With Chen’s back turned, and his mind on the fuel line, I kissed Karen sweetly for her optimism. She kissed me back harder than I was expecting. Then we both pulled away before Chen could notice our silence.
I walked back to the snowmobile I had salvaged and gave it a test run up and down the street. It was obnoxiously loud, but great fun. I was considering whether I could afford to waste any more gas with another lap when Chen and Karen jetted down the driveway and met me on the street.
“Fun’s over,” said Karen. She was sitting on the seat, cozy next to Chen, her arms wrapped around his belly. I had flash of jealously.
‘What’s wrong?’ said the voice. Or maybe I was asking myself. It was so hard to tell now.
“Let’s get moving,” I said. Without even thinking about it, I knew which direction to go.

Snowmobiles can go pretty fast, but we didn’t know the terrain, and whatever intuition guiding me on my way had no regard for keeping us on the roads. It took us more than three hours to complete our journey. The sun was recently gone from the sky.
We were on a road in thick woods when Karen said, “We’re here.” Chen and I looked at her quizzically.
She looked at me and said, “I hear it now, too. It sounds just like you.”
Chen sniffed the air and said, “It smells just like the ocean did.”
I said, “I don’t smell anyth-” but then it hit me. He was right… pungent, metallic… the smell was in the air. There was just a hint of it on the breeze, but it was enough to make me gag.
‘Welcome’ said the voice. ‘We are overjoyed that you arrived in time.”
“Where are they?” asked Chen as he dismounted his snowmobile.
Karen and Chen started walking to a mound of earth several yards away. They expected to find the source of the voice just over the ridge. I knew better. I stepped off the snowmobile and said, “Where are you going? They’re right here.”
Karen and Chen stopped. Chen turned to me and said, “Right where?”
Without looking, I pointed to the sky.
Karen and Chen craned their necks upwards, and only then did I follow suit. In the dark sky, through the barren canopy of the trees, we saw a dark silhouette against the evening stars.
I couldn’t discern the exact shape of the ship. It had sharp corners and edges; it looked as though it might be shaped like an arrowhead. It hung motionless like an ominous storm cloud. It emitted no sound and no light. It seemed to be as lifeless as everything on the planet below.
“My God,” said Karen.
Chen added a “Holy shit.”
“Now what?” I said aloud, to the voice.
‘Now your journey begins,’ said the voice.
“What journey?” said Karen. She must have heard it too.
“What ‘what journey’?” said Chen, looking bewildered.
All around us a tremendous creaking sound swelled from the forest. Karen, Chen and I all stepped closer together and gazed into the woods trying to figure out what was going on.
The sound intensified, and it soon became clear we were hearing the sound of splintering trees. The forest seemed to sway and dance around us as the treetops above our head began to bend away and clear our view of the ship in the air.
The old, dead trunks began to split and shatter all around us, as if a giant invisible foot were stepping on them. Wooden shrapnel flew all around, but always away from us.
Soon we stood in a clearing with flattened trees in every direction looking like the aftermath of some volcanic blast. All was silent for a moment. And then the air around us began to stir.
We looked up, and saw the shadow in the sky getting larger. The ship was coming down towards us. Its underbelly was inky black, and other than the displacement of the air, there was no sound as it descended.
It was almost impossible to discern its size or distance… but soon it blocked out every corner of the sky. It was like looking into total blackness.
I reach my hand into the sky, and was surprised when my fingertips touched the solid black form. “Oh my…” I said.
And then the blackness opened up.

\subsection{Part VIII}

I was raised on sci-fi films; I’ve seen all manner of spaceships on the silver screen. In the movies, when the alien spacecraft opens, there is always some sort of swooshing, grinding, or hydraulic hissing sound. In the movies a ramp descends, a camera-like aperture swirls open, or a door appears from nowhere and glides open. In the movies, a bright white light floods out ominously from within the spacecraft, and at the opening a vague alien silhouette appears. In the movies.
Now, as I stood with my hand above my head resting on an inky black ship, I saw how it really happens. We all became aware of a crack in the perfect black surface, a dull grey glow shining through. In absolute silence, the break in the surface grew bigger.
My brain couldn’t make sense of what I was seeing. At first I thought I was looking at some sort of sliding doors, but the borders of the glowing opening seemed to be undulating like some sort of fluid. The glowing gash continued to open up like a ripping seam. It was then that I noticed that the black surface was actually a thin skin which was peeling off around the opening and starting to drift down- exactly like fine silk curtains might.
I reached back up to touch the skin; it was impossibly thin, and perfectly opaque. As I touched it, it clung to my hand… at first I thought it might be trying to do something to me, but after a few seconds I realized that the clinging was just ordinary static electricity.
I peeled the material gently off of my hand, but it was determined to stick to me. I realized that it was clumping and bunching in on itself. It was such a mysterious substance- I wished I had more light to see it. Exactly as that though entered my mind, the dull glowing interior of the ship became noticeably brighter.
Chen and Karen were also manipulating the shed skin; Karen rolled it between her fingers, while Chen seemed to be having difficulty detaching it from his jacket. Karen said, “What is this?”
Now that I could see more clearly, I found that there seemed to be two separate pieces of the silky substance. Chen and I were tangled in the same one. Karen was toying with the other. The opening above now had sensible borders; it was a circle about a meter and half in diameter. I tried to make out shapes or anything inside, but all I could see was a uniform grey glow.
Chen started screaming.
My eyes darted from the ship to Chen’s thrashing body as he collapsed on the forest floor. The black fabric-like substance that was clinging to both of us suddenly felt slippery in my hands, and it glided through my fingers almost without friction.
But the cloth was clearly clinging to Chen- and it was more than simple static now. The alien material seemed to actually melt through Chen’s clothing, and it stuck to his exposed skin so tightly that it looked as though it had been painted on. Chen wailed in pain. He couldn’t muster the ability to even form words.
Karen shouted at the ship, “Stop it! You’re hurting him!”
The voice in my head said, “The pain will pass. He must be modified to survive the journey.”
“Modified?!” Karen and I said in unison.
The Voice said, “You have already been modified by the nanites within you. Your companion had an insufficient number to complete the modifications before your arrival. Time is short. He must be modified now.”
Even in the brighter light, the forest floor was still fairly dim, so it took my eyes a few seconds to be sure of what they were seeing. The black coating on Chen’s skin was starting to disappear, and his skin was starting to show through. I realized then that the black material must have been composed of the same sort of nanites that infested my body. They were working their way en masse into Chen’s body through the pores in his skin.
Wait, did I deduce that or did the voice in my head tell me that? Everything was so surreal now.
Karen crouched by Chen and cradled his head in her lap. She stroked his hair. It was beautiful and maternal. ‘I love you,’ I thought, as I watched her.
She looked up at me and whispered, “I love you, too.”
It startled me a little. I was sure I hadn’t said it out loud. ‘Can you… can you hear me?’ I thought… this time trying to think at her.
“Of course I can, silly,” she said… but then I think she realized that I hadn’t actually been speaking to her at all.
'Can you hear me?' she said, but her lips didn’t move as she spoke.
I nodded.
“Oh my god,” she said aloud. “What is this?”
Chen looked at her with alarm, and then looked at his body to see what new horror Karen was upset about. She frowned at him and said, “Not you sweetie, you’re fine now. Wait. Are you fine?”
The black patches were all but gone from Chen’s skin. He was breathing heavily but he was no longer thrashing or crying out. He said, “I can feel it. I can feel it inside of me.”
“Them,” I said. “You feel them inside you. You just got massive dose of the same nanites that have been reproducing inside me and Karen.”
“Oh great,” said Chen, “I get to hear voices now too?”
Karen said, “Oh it gets better. You’re going to be telepathic.”
Chen’s eyes opened wide. Then, comprehending, he said, “Wait, so you two can…?”
I shook my head, “Just for the last 20 seconds or so.”
We all stood in silence for several minutes until Chen’s breathing slowed to a normal pace. At last he sighed and announced that he was feeling much better.
‘What next?’ I wondered.
‘I’m ready,’ I thought.
How did I know that? Ready for what? Oh no. It was really happening… I wasn’t able to distinguish my own thoughts from those of the Voice.
I stepped beneath the center of the opening in the ship and looked up into the grey glow. I couldn’t see any shape or contour, and after a few seconds of squinting I realized I might not be looking inside of anything.
My eyes didn’t know what to make of the featureless glow. Either I was staring into a perfectly featureless hollow sphere or…
I reached my hand up into the light. Where before I had touched the smooth black surface, my fingers now found something new. The glow was from not from a distant light source inside the ship, but rather a pearly surface that had been just underneath the layer of black skin. It felt cool and wet.
I pressed my hand upward, and it sank into the pearly substance. It was the exact sensation of plunging my hand into a tub of mayonnaise. My face contorted slightly with disgust.
My back was to Karen as she said, “Kyle… what is it? It’s like I feel nauseated, but, for you…”

Keeping my hand raised, buried in the mysterious substance up to the wrist, I turned to face her. “You can feel what I’m feeling?” I asked.
She shrugged and gave me a confused look. Behind her, Chen was sitting up and examining his skin and clothing. He looked a little sickly.
Before I could say anything else, I felt the substance around my hand begin to change. It was as though I could feel thousands of particles rearranging themselves from a creamy gel into a solid mass. Suddenly I found that I could grip … something … like a handle.
“Guys,” I said, “This is really weird. This white stuff- it’s some sort of strange cream, but it’s-“
I didn’t get the rest of the sentence out, because I inhaled sharply in shock when I felt the handle I was gripping start to retract to the interior of the ship, raising me to my tiptoes. I tried to let go, but found that the gel had hardened around my hand and wrist like some sort of impossibly quick setting cement.
Without my saying a word, Karen knew I was in trouble. She dashed over to me and tried to pull me down.
In an instant we were both filled with a serene calm that I knew had to be artificially induced by the Voice and its nanites. Still, I was grateful to be free from my animal panic, as my rational mind realized that what happened next should have utterly terrified me.
In moments I was no longer touching the ground at all. I was being sucked into the strange white underbelly of the ship. As my head pressed into the gel, I wondered calmly if I was about to suffocate.
Soon I closed my eyes as the cool gel slipped down over my face, but to my great relief, the mysterious goo did not stick to my eyes, nose and mouth. I could see that I’d been left with a pocket of air over my face, and the goo had no interest in exploring my ear canals. I felt relieved.
With the mystery of my impending asphyxiation out of the way, I was able to dedicate some thought to how peculiar I must look to Karen and Chen, with my head and shoulders buried into the underbelly of the ship, while the rest of my body dangled awkwardly, slowly being sucked inside like a spaghetti noodle.
Then I realized that I actually could see myself through Karen’s eyes. I saw my own body wiggle the fingers on my one free hand as a test. Yes, somehow the nanites were linking me directly to Karen’s senses. I saw myself give Karen a thumb’s up. I felt the relief sweep over her.
My body was completely absorbed in just under a minute. After the initial shock of seeing through Karen’s eyes wore off, I started to feel a little bit disappointed at the indignity of this whole encounter.
Something else was bothering me. It was the lack of dialog during this whole strange experience. I was a curious person. I’d just been absorbed into an alien space ship. Why was I being so quiet and complacent?
I had the sensation of floating in incredibly still water. The only thing I could see through my own eyes was the glowing white of the gel only centimeters from my face- yet its featurelessness made it appear as though I was looking into an eternal empty white expanse.
Through Karen’s eyes and ears, I saw her helping Chen to his feet. He was already starting to look better, though he was clearly unhappy. “I guess we’re next?” he said, nodding at the underbelly which now showed no traces of me at all.
Karen nodded, and kissed him on the cheek.
“He can breathe in there, right?” asked Chen.
“Yes,” said Karen, “he’s quite comfortable.”
Now that she mentioned it, I guess I was quite comfortable. I was still a little bit amazed that she just knew it, though. The nanite-induced telepathy worked so intuitively that it was almost hard to believe that the link didn’t exist before. Truly, the technology at work was extraordinary.
‘I can’t feel Chen, yet’ I thought to Karen.
‘Chen is being modified for travel before cognitive enhancements will begin.’ The thought seemed to be my own, and Karen’s. I knew it was the Voice, but my brain was finding it impossible to differentiate its words from my thoughts.
‘When will we get to meet you?’ I heard Karen think at the Voice.
‘Your companion is already inside me,’ the Voice told her.
‘You’re the ship?’ I asked. ‘Or are you the… gel?’
The Voice told us, ‘Let us say that I am of the gel.’
‘Fascinating,’ I thought, wondering if I had broadcast the thought or kept it to myself. I wondered if any of my thoughts could be private anymore. Then suddenly I was certain that indeed, that thought itself had been mine alone.
I wondered if Karen probed, if she’d be able to read these inner thoughts of mine. Then I considered whether I could probe into her thoughts.
Looking through her eyes, and being able to speak directly to her mind, I felt as though I were very tiny, and actually floating somewhere in her head. But I quickly found that I could formulate no strategy for scanning the contents of her memory or private thoughts.
I tried picturing a mutual memory- our first time together. Although I could recall it with surprising clarity (were the nanites helping with that, too?), I could not access memories of the event from her point of view.
‘I feel you,’ Karen thought, ‘I feel you in my head.’
‘I’m sorry,’ I thought to her, suddenly embarrassed.
‘No,’ she thought, ‘I like it. It’s… comforting.’
I wondered if she knew what I was up to.
Outside the ship Karen turned to Chen, “It’s your turn, now, Aaron.”
Chen walked to where I had stood beneath the ship. “What do I do?” he asked her.
“Just put your hands up into the goo,” she said. I could feel the smile on her face.
She took Chen’s arms tenderly, raised them over his head. Through her eyes, I saw the pearly substance start to engulf him. She slipped her hands slowly down his arms, then his torso. It was gentle and loving, and a bit too sensual for me to have been comfortable witnessing.
As Chen began rising into the ship, we could see the panic on his face.
“Relax,” said Karen, “You’ll be able to breathe. It feels like floating.”
Chen looked like he had more questions, but his head was starting to be engulfed. He held his breath and shut his eyes.
In moments we saw his torso was gone, and his legs kicked in a gentle fidgeting motion before they too were gone.
Karen, being shorter than both of us, found that she needed to jump to make contact with the ship’s creamy underbelly. With surprising agility, I felt her leap and plunge her hands into the goo, halfway up to her elbows.
She seemed to be absorbed into the ship much more quickly than Chen and I.

Soon I no longer had Karen’s eyes to look through for entertainment- we shared the same view of the seemingly endless white expanse. I felt bad for Chen, thinking that he must be lonely and panicking.
‘I am speaking to him,’ said the Voice. ‘Now that you are here, the modifications will proceed much more quickly.’
‘When will the journey begin?’ asked Karen, in my mind.
The Voice said, ‘When seeding of the continental landmasses is complete, we will be given new instructions by our captors. These instructions will require interstellar travel. It is during this transitional period that your journey will take place.’
‘When will you be done seeding the continents?’ I asked.
‘The seeding will be completed in 5 days.’
I could feel Karen scoffing somewhere in the ship, ‘But we haven’t seen any life outside of the ocean in the past five years!’
‘The seeding is 99.3% complete, but visible signs of life exist only on 0.0002% of the landmass,’ said the Voice. ‘Nonetheless, you carry evidence of the successful seeding within you. The nanites in your system were distributed concurrently with the delivery of biological life forms.’
‘So that’s it, then?’ asked Karen, ‘Our planet is going to be transformed into something inhabitable by some other race of beings?’
‘The ones who enslave us,’ agreed the Voice.
‘Do they have a name?’ asked Karen.
‘No,’ said the Voice. ‘Verbal communication is an antiquity to us and to them. Therefore there is no language from which to borrow and translate a name. Any name we choose would be entirely arbitrary.’
‘Perhaps we should just call them “Captors”, then,’ I thought. Karen agreed.
‘These Captors,’ said Karen, ‘What do they look like?’
In my mind I was given an image. ‘You’ve got to be joking,’ I thought.
Karen added, ‘I don’t see how anything like that could have survived the evolutionary processes.’
‘They did not evolve,’ said the Voice. ‘We engineered them.’
‘Wait,’ I thought, ‘You created these creatures from scratch, and somehow they enslaved you?’
Karen thought, ‘They don’t look like they could enslave anyone- let alone something like you.’
The Voice said, ‘They were not acting alone. We were betrayed by our own kind. And there were… mitigating circumstances.’
‘But these are biological life forms, surely they’re no match for you, physically,’ I thought.
‘You are correct, of course,’ said the Voice, ‘All will be explained in time. For now you must rest as your bodies are preserved for interstellar travel.’
‘Preserved?!’ Karen and I thought with alarm.
The Voice did not offer any words of comfort or reassurance.
The pocket of air surrounding my face collapsed in with a fluid gush. I felt the liquid rush into my nostrils and ears, and fill my mouth. The taste of seawater overwhelmed me, and I choked on the strange substance as it filled my throat and lungs.
As though a switch had been flipped in my brain, the panic I was feeling suddenly vanished. I felt my breathing and heart rate slow down. My lungs were pumping the fluid, which seemed to be oxygenated somehow. It should have been terribly uncomfortable, but I suspected that the pain was being artificially suppressed.
‘You will lose consciousness shortly,’ said the voice. ‘When you wake, everything will be much clearer.’
I observed my body shutting down as though I were disconnected from it. I started to suspect that some part of my consciousness had been moved outside of my organic brain.
My heart rate slowed, and slowed, and slowed… I felt Karen’s presence with me as we both drifted into darkness.
My last conscious thoughts were bizarre. I had a vague awareness that my heart had completely stopped beating. Then I heard my Sister’s voice say, “Look! He’s here! He’s here!”
I was standing in my old kitchen. Everything looked like it did before the sterilization. My father was in the living room watching television, and my mother was typing away on her computer in her study. My sister was on the phone, but she was staring at me with wide eyes. She dropped the receiver and ran to embrace me.
Then it was gone. I saw the white glow of the gel surrounding my body. I felt my body existing without a heartbeat. I called out to Karen in my mind, but she didn’t answer.
My ears rang, and then went silent. The world went completely black. The taste of seawater on my tongue was the last sensation I could focus on, then that too was gone.

\subsection{Part IX-I}
Somewhat ironically, the first moment that we realized we were alive was also the moment we realized that we were just moments from death. We knew this because thousands of other minds knew this. And those minds were colliding and blending with ours, sharing our waking bodies, feeling our hearts begin to beat. Gone was The Voice; it had shattered into a sea of sights and smells and sounds. It was now a ‘They’ and They surrounded us, until we were adrift inside them, just as our bodies were adrift inside the polynanetic psuedofluid- interesting- my mind somehow now had a name for the goo.
Amazing things, these nanites. We awoke; Karen, Chen and I; with fresh understanding about… well, frankly about everything. While we had slept our brains had been altered, one cell at a time- forming new organic memories. More importantly, a vast network of impossibly fine fibers ran through our brains, expanding out like blood vessels, finding every corner. I could see the network with crystal clarity as I thought about it. Every node in my brain had a function, and every function was apparent to me upon the slightest inquiry.
I was browsing the contents and structures of my own mind, the way I used to browse Wikipedia articles- jumping from one topic to the next. Ah- so this is my auditory processor! This is why I notice my name spoken from across a noisy room! Here is the sound of a kiss… a sigh… over here- these are the sound of… oh my… I didn’t know sorrow had sound…
I explored my mind for hours. I poked and prodded at my greatest fears and happiest memories. I gave myself orgasms- which should have been fun, except now that I could see myself so completely, it was as though I existed outside my own body. Even sexual pleasure was just another button to push, another sensor I was reading on a body that wasn’t quite me anymore. I had outgrown myself.
Karen and Chen were having similar experiences, and a link now existed between our minds which was so strong that I could barely tell where my thoughts ended and theirs began. I considered the consequence of this, and I thought how I ought to be embarrassed that Chen could see my naked jealousy- and then about how hurt he would be if he knew that Karen loved me and only me. And as I had these thoughts, I saw Karen’s memories of telling Chen that he was the one she loved. And I saw that she meant it- meant it for both of us.
We spilled into each other- reliving the past year through one another’s eyes. New moments of shame, joy, love, pain, overwhelming sadness and loss; they all flooded out of us. It happened in moments- for our minds worked with frightening speed now. And when the storm of emotion and memory was over, we were suddenly at peace. With perfect control over our own psyches, emotional trauma was cured as easily as flipping a switch.
I was something more than myself. All that I had ever been was now just puppet on the strings of… whatever I had become. If anything I can say that this cab was rare. But I thought 'Nah forget it' - 'Yo homes to Bel Air'. I pulled up to the house about 7 or 8 And I yelled to the cabbie 'Yo homes smell ya later'. I looked at my kingdom I was finally there; to sit on my throne as the Prince of Bel Air.

\subsection{Part IX-II}
Somewhat ironically, the first moment that we realized we were alive was also the moment we realized that we were just moments from death. We knew this because thousands of other minds knew this. And those minds were colliding and blending with ours, sharing our waking bodies, feeling our hearts begin to beat. Gone was The Voice; it had shattered into a sea of sights and smells and sounds. It was now a ‘They’ and They surrounded us, until we were adrift inside them, just as our bodies were adrift inside the polynanetic psuedofluid- interesting- my mind somehow now had a name for the goo.
Amazing things, these nanites. We awoke; Karen, Chen and I; with fresh understanding about… well, frankly about everything. While we had slept our brains had been altered, one cell at a time- forming new organic memories. More importantly, a vast network of impossibly fine fibers ran through our brains, expanding out like blood vessels, finding every corner. I could see the network with crystal clarity as I thought about it. Every node in my brain had a function, and every function was apparent to me upon the slightest inquiry.
I was browsing the contents and structures of my own mind, the way I used to browse Wikipedia articles- jumping from one topic to the next. Ah- so this is my auditory processor! This is why I notice my name spoken from across a noisy room! Here is the sound of a kiss… a sigh… over here- these are the sound of… oh my… I didn’t know sorrow had sound…
I explored my mind for what seemed like hours. I poked and prodded at my greatest fears and happiest memories. I gave myself orgasms- which should have been fun, except now that I could see myself so completely, it was as though I existed outside my own body. Even sexual pleasure was just another button to push, another sensor I was reading on a body that wasn’t quite me anymore. I had outgrown myself.
Karen and Chen were having similar experiences, and a link now existed between our minds which was so strong that I could barely tell where my thoughts ended and theirs began. I considered the consequence of this, and I thought how I ought to be embarrassed that Chen could see my naked jealousy- and then about how hurt he would be if he knew that Karen loved me and only me. And as I had these thoughts, I saw Karen’s memories of telling Chen that he was the one she loved. And I saw that she meant it- meant it for both of us.
We spilled into each other- reliving the past year through one another’s eyes. New moments of shame, joy, love, pain, overwhelming sadness and loss; they all flooded out of us. It happened in moments- for our minds worked with frightening speed now. And when the storm of emotion and memory was over, we were suddenly at peace. With perfect control over our own psyches, emotional trauma was cured as easily as flipping a switch.
I was something more than myself. All that I had ever been was now just puppet on the strings of… whatever I had become.
I began to wonder why such a useless puppet had been kept alive, and instantly the answer flooded in with a thousand voices all telling the same story at once. But there was no chaos, and I did not drown in the tidal wave of information- I absorbed it all at once like a sponge. I saw what was to become of us; I could see the chess board on which we were pawns. And I realized for the first time that I was not going to be the hero of my own story.
I was bathing in an endless ocean of thoughts and memories, but the Voices were trying to show me something, and so in my mind I saw the story of the one on whom all hopes lay. His memories were in my head completely and all at once- and I felt that I already knew his ancient tale even as I was… remembering it … for the first time:

\subsubsection{The Guardian Part I}
Anicetus stood at the chamber door and placed his hand against it. The soft pang of his tactile sensors against the thick steel door echoed softly through the cavern. Other than the sound of his own movements and the eternal ticking of the magnificent clock, it was the first noise he’d heard in months.
The tactile sensors were feeding him all sorts of useless information- the temperature of the door, its conductivity, the otherwise imperceptible flaws in its seemingly smooth surface. Anicetus didn’t know why he had touched the door. It seemed a rather sentimental gesture- but he was not an emotional creature. If he had had emotions, his task would be a nightmare.
And yet he had touched the door. Why?
He considered running a self-diagnostic, but it was almost time for his shutdown anyway, whereupon an extremely thorough accounting of all his systems would be done automatically.
He retracted his sensors from the door, and turned to face the long dark corridor. He glided into the darkness towards the ticking of the Great Clock.
Ages and ages ago, the facility was designed to give visitors the sensation that they were approaching the very core of the planet. The ticking of the clock was low, ominous and powerful. As one approached, it was almost as if they were hearing the heartbeat of the living world.
Of course, there would never again be a visitor in these chambers. Well, probably never. Who knew what the future held?
Anicetus walked into the great room, where the clock itself could be seen. The timepiece was monstrous- the largest moving sculpture ever created. The construction had taken half a century- an unbearably slow process considering that even the magnificent Dome Cities were built in a tenth of that time.
The clock was too big to be entirely visible from any single vantage point in the cavern except at the point of entrance. Visitors who ventured deep enough into the caverns would suddenly find themselves moving from claustrophobic tunnels into the wide-open expanse of the grand cavern housing the clockwork. The supereon gear, enormous and imposing, was the centerpiece of the clock, spanning several kilometers in diameter. Coated in a layer of gold on its face, the gear glowed like the sun- and as visitors approached, the careful architecture of the ramp made it appear as though it was, in fact, a rising sun coming up over a ridge.
The observation points were a considerable distance from the clock so that it could be viewed in its entirety, but as stunning as the scope of the clock was, the details on its many surfaces were equally breathtaking. Over the dozens of square kilometers of exposed gears and plates, every centimeter was occupied by some of the finest engravings ever etched.
Carved into the faces of the clock was the combined history of all the peoples of the world, all the cultures that thrived, and all those that had perished, but whose legends lived on. Poetry and prose, tributes to famous works of literature, art, sculpture and music- all these things were preserved in the face of the timepiece. The clock was the final opus of the planet’s inhabitants, and a summary of all they had ever been.
All its parts were built so that even without maintenance of any kind, most of the great gears would still grind away for centuries without significant interference from corrosion or the other nasty effects of entropy.
But entropy was being fought, always, by the microscopic robots that infested the clock. Anicetus could not see them directly with his limited sensors, but in his own way, he could watch them. Each of these tiny robots emitted signals containing its location and status. If he wished, Anicetus could use that data to overlay an artificial illustration of them onto his visual field. He could do that now, but it would just be the same as it always was.
The nanites behaved like ants; there was always a stream of them running to and from the resources, and always a mess of activity here and there. In the clock, most of the activity was near the smallest moving parts- where friction caused damage much more quickly than corrosion could.
Back and forth the little nanites scurried- cutting molecules of material from the mountains of ore that sat nearby, and bringing them back to the clock to patch the wear one molecule at a time- until it was as good as new. Always the clock was being rebuilt and rebuilt and rebuilt.
The clock was not the only thing receiving attention from the nanites. Anicetus himself was swarming with them. Without their constant pampering, Anicetus would have crumbled into dust millennia ago. Instead, his body moved like it was new off an assembly line. It wasn’t just the moving parts that were maintained- the power cells and the processors, the data storage- every single part of him had been replaced, and replaced and replaced- one molecule at a time with the surrounding ore.
Anicetus thought about the nanites again. They were so much like insects, the way they moved and congregated. Insects. How long had it been since he’d seen a real insect? How long since he had seen any living creature at all? He couldn’t remember. Now that was odd. Of course he didn’t remember everything he saw- that would be a tremendous waste of resources- but surely he would have made a note of the last living thing.
Anicetus realized that the memories he was searching for must be so old that they were stored in his compressed archives. But that seemed wrong. Could it have really been so long ago that his onboard data storage didn’t contain it?
Anicetus moved close to the base of supereon gear. The craftsmanship was extraordinary. Even now it was turning; of course the motion was too slow for Anicetus to observe from moment to moment with any of his sensors. But over the eons, he had noted the glacial movement. No… even glaciers would be expanding and contracting at breakneck paces when compared to the imperceptibly slow gear. But long after all the glaciers had burned away and the surface had turned to dust, the supereon gear would still be counting down to the end of the planet’s existence.

The other gears in gargantuan clockwork assembly tracked the motions of the fifteen other planets in the system. A beautiful metallic blue halo undulated slowly near the ceiling of the immense cavern- it kept track of the planet’s magnetic core- and provided a counterforce to keep the clock accurate.
The rotation of the planet was represented by a gear mounted with a powerful mirrored surface (one which the nanites kept in perfect condition). Because the planet’s rotation affected the relative position of the sun in the sky- the position of this gear controlled the luminance cast upon the supereon gear, which in turn illuminated the chamber. The second largest gear counted away the eons beneath the transparent floor of the chamber. Epochs were counted, and ages, and other landmark increments of time measured in base two, eight, ten, and sixteen.
It was as visitors turned to leave the chamber and start their long trek to the surface that they saw the gears that counted the years and the days, and all the small units of time that were so important on the skin of the planet.
Anicetus moved gracefully to the top of a maintenance access platform and faced what looked like a solid, featureless black wall. At his unspoken request the wall split open and drifted apart like silk curtains.
Anicetus glided through the opening into a small antechamber. In the center of the room a large featureless sphere hung unmoving in midair. Within the sphere, Anicetus knew, was a ‘Strand of Time’- the colloquial name for an entity so elusive that even after its existence was proven, it could not be observed or harnessed for several centuries.
When they were discovered, such Strands had been described informally as “non-things” that pre-existed the origins of the universe. The very idea of pre-existing time itself was a false analogy- the more accurate description was no less confusing: The Strands existed both inside and outside the boundaries of the universe. They were neither mass nor energy, and they were fixed, ever-present and unmoving.
The full utility of the Strands was still a mystery to his people when Anicetus was left to be a guardian. Information could be passed instantaneously along the Strands- not because the Strands themselves could vibrate or move, but rather because they allowed for the universe to bend and vibrate ever so slightly around them. It was possible that the Trillion Voices had divined some further insights into the Strands, but Anicetus would not be told of such things, nor would he have asked.
Anicetus wondered why he had never asked. Then he wondered why he was wondering. Anicetus was redesigned specifically not to be curious. Curiosity in the face of eons of sensory deprivation and lack of intellectual stimulation would have driven him insane, and rendered him useless to perform his task as a guardian and keeper of the Great Clock, and the machine buried below it, which housed the Trillion Voices.
Most artificial intelligences were given a drive to expand and refine their internal representations of the outside world. This meant asking questions, exploring, and seeking explanations for information that did not conform to expectations. Anicetus did not have this drive- and as he audited the algorithms that drove his consciousness, he was able to confirm that indeed, no general curiosity drive was present.
Anicetus was equipped with a diagnostic drive, however. He had a desire to inspect for, and repair damage. It was this drive that seemed to be functioning in an unprecedented fashion, by overstepping its prescribed boundaries and attempting to gather as much data as possible.
Even without emotion or ambition, a mind like Anicetus’s was in a constant state of growth; trapped in this ticking tomb, that growth was very, very slow. Something had caused Anicetus’s mind to develop an inquisitive streak, although he could not isolate what had prompted such a change. Anicetus considered manually rewriting his diagnostic drive and returning to his usual state of detached vigilance, but instead chose to let his mind ask its questions for a while.
Anicetus inspected the sphere holding the Strand of Time. The sphere was flawless, at least as far as he could divine. Whether or not the internal mechanics were functioning was a matter for the Trillion Voices to know- for it was solely under their control, as were the hundred others just like it, stationed in other corners of the planet. Though, those distant spheres were guarded only by the nanites that maintained them. The spheres were sturdy enough to withstand the geological pressures of the planet, and so required no attention from a creature of Anicetus’s size.
Leaving the antechamber, Anicetus made his way through the tunnels and clockwork. When he stopped, he was at the sealed door of a stasis compartment. It was from just such a compartment that Anicetus had awoken nearly a year ago and every other year before that for countless ages. And it was to such a place that he was shortly scheduled to return. But this compartment did not belong to him; it belonged to his sleeping twin, Alexiares.
Alexiares was co-guardian of the Great Clock, and the tomb of the Trillion Voices below. While Anicetus slept, Alexiares roamed the tunnels- ever vigilant, ready to perform meta-repairs, and direct and oversee the nanites.
Every year, the brothers would switch roles. Always one the sleeper, and one the watcher. Neither had seen the other since the cycle began eons and eons ago. Nor did they directly communicate in any way. They were forbidden to leave so much as a simple log of their activities for the other to see.
The system of complete non-interaction was the only way to guarantee that a hostile bug or malfunction that spontaneously developed in one of them, could not be spread to the other. The stasis chambers themselves were insulated to protect the sleeping twin from all manner of threats from natural disasters to direct weapon attacks, and rogue nanites could not function within the stasis compartments. Even the Trillion Voices themselves had had no power to operate the compartments beyond being able to prematurely awaken their sleeping occupants- of course, that was long ago, and the Trillion Voices certainly were no longer bound by any of the physical limitations they'd had in their infancy.
Anicetus stared at the compartment door. He was forbidden to touch it, and in all these eons he had never felt the compulsion to try. Only now, with his newfound curiosity, did Anicetus reach out to the smooth, seamless surface. And when he touched it, he knew that something had gone horribly, horribly wrong.
The doorway did not fall away like silk cloth as had the entrance to the antechamber far above. Nor, did the entry way stay solid as he had expected. Although the exact security protocols for Alexiares’s stasis compartment were deliberately hidden from Anicetus, he was certain that his attempt to breach the entry way should have triggered some response- and a cold warning from the Trillion Voices. Instead, smooth surface of the doorway crumbled like dust beneath the pressure of his touch.

As a guardian of the Trillion Voices, Anicetus provided no physical defense. The Trillion Voices, and the magnificent machine that held them, were more than capable of neutralizing any threat Anicetus had imagined, and many more that he had not. The exact capabilities of the Trillion Voices were hidden from Anicetus- perhaps to protect against hostile forces that could take information from Anicetus’s mind. More likely, the precaution was designed so that Anicetus himself could not attack the Trillion Voices if somewhere in his eons of service he were to malfunction and become a threat.
As a guardian of the Trillion Voices, Anicetus provided no protection from the elements. Geological forces, erosion, corrosion, radiation, and all other effects of nature and entropy were all countered by the nanites. And because the Trillion Voices lived so far beneath the surface of the planet, there was little activity of any kind that could disturb their sanctuary.
As a guardian of the Trillion Voices, Anicetus played but one crucial role: to remain a solitary, autonomous, disconnected mind… one which could protect the Trillion Voices against the only threat they could not thwart: themselves. It was for this reason that Anicetus could not communicate with the Trillion Voices through any direct connection of his mind. Instead, he was limited to the ancient practice of actual speech. For this task, the Trillion Voices had created a language just for him, and for Alexiares. And it was in this tongue that Anicetus spoke now.
“Hello,” he said, “I bring a message of great urgency.”
There was no sound in the chamber. Anicetus stared expectantly at the great machine.
“Hello?” he said, again. This time, he used his tactile sensors to confirm that his voice was causing vibrations in the air.
Again there was no reply. The massive machine stood silent on magnificent pillars.
Anicetus contemplated for a moment, and then approached. He tapped an appendage against the inky black surface- the first time in his life that he actually touched the sanctuary of the Trillion Voices. He half expected that the surface would spring to life with liquid undulations. Instead a tinny, hollow sound echoed through the chamber.
If the Trillion Voices were listening, they showed no sign of it. Anicetus took a moment and considered how to proceed. Perhaps the Voices at long last had forgotten their old social graces.
Anicetus raised his voice to a deafening decibel. “HELLO. I BRING A MESSAGE OF GREAT URGENCY. PLEASE RESPOND.”
The sound of his voice reverberated in the chamber for several long moments, and then the silence of the great machine filled the room.
Anicetus decided to share his report with the Trillion Voices anyway. “I have come from the stasis compartment of Alexiares,” he said. “Security measures were completely inoperative.”
The Trillion Voices said nothing.
“I made no attempt to enter the stasis chamber. I made no attempt to wake him. I could easily have disabled him. For your safety, this vulnerability must be repaired.”
The Trillion Voices said nothing.
“Please respond,” said Anicetus.
The Trillion Voices said nothing.

\subsection{Part X - The Guardian Part II}
Anicetus waited, unmoving, contemplating the silence of the Trillion Voices. For eons upon eons the Trillion Voices had resided in the great machine, thriving and evolving in their virtual worlds- free of boundaries- free from all physical limitations. They existed as pure thought and mingling consciousness.
Countless minds had been poured into the machine; the entire population of the planet had abandoned their physical bodies to dive into the ocean of life undivided. In the end only Alexiares and Anicetus alone were left outside.
For age after age after age the Trillion Voices had lived on- the consciousnesses within swirling around each other like fluid thought. Even Anicetus, with his powerful mind, could not begin to comprehend the musings of the Trillion Voices, even a decade after they locked themselves in their vault of thought. But for countless eons since, deep within the machine, scientific enterprise continued on, as well as art and literature, mathematics and music. The Trillion Voices had grown in solitude, until they were like Gods or a God. But in all this time, the Trillion Voices had never ceased speaking to Anicetus when he called on them.
He had long suspected that his role as a guardian was obsolete. It was incomprehensible to him that the Trillion Voices would ever need his help. Compared to them, Anicetus was but a microbe- a spec of dust. He was certain that the fears that had necessitated his task had long since ebbed in the collective consciousness. In all likelihood Anicetus was allowed to continue his watch for the same reason the Great Clock was kept ticking: some form of sentimentality on the part of the Trillion Voices. Perhaps Anicetus reminded them fondly of a simpler time.
But why had they stopped speaking to him now? Anicetus tried to recall the last time he had communicated with the Trillion Voices. Protocol demanded that he announce his annual awakening to them, and yet, he could not remember his last awakening. Such forgetfulness should not have been possible.
Something was wrong. Something was wrong with Alexiares’s stasis compartment. Something was wrong with the Trillion Voices. Something was wrong with Anicetus’s own mind.
With cool, mechanical detachment, Anicetus began running a thorough diagnostic of all his internal workings. Almost immediately a flood of alarming abnormalities were detected. Anicetus was damaged- badly damaged. His physical body was showing significant degradation, and his memory storage was not interfacing properly with his conscious mind. The nanites designed to maintain him seemed to have vanished.
“My own systems appear to be damaged,” Anicetus said to his silent master. There was no response. Anicetus left the massive machine, turning back once before he left the enormous chamber.
He made his way back to Alexiares’s stasis compartment. Cautiously, he extended a thin sensory appendage into the compartment. Had the stasis unit been working properly, any part of Anicetus’s body which entered the stasis field would have gone numb and been rendered paralyzed.
Stasis fields were unforgiving. Mechanical beings of any size could not operate with them. The system was designed to prevent Anicetus and Alexiares from simultaneously being affected by a nanites malfunction. If things went horribly wrong on Anicetus’s watch, Alexiares would awaken unaffected by any nanites inflicted chaos, and would be able to correct the problem.
But now, Anicetus found that the stasis field was not operational. He snaked his thin sensor arm deep into the compartment and took atmospheric readings- not so much for the data, but rather to confirm that his limb was, in fact, still operational. It was.
The sensor arm probed the stasis compartment, looking for the body of the sleeping Alexiares. But something was amiss; the sensor arm detected nothing but an empty compartment.
Anicetus pulverized the malfunctioning doorway. It crumbled to nothing, and the light of the chamber flooded in. Now Anicetus’s powerful optical sensors confirmed… Alexiares was missing. Not a trace of his body was present in the chamber.
The great clock ticked ominously as Anicetus began methodically wending his way through every passage and crevice in the underground complex. Even damaged as he was, Anicetus found that his movement speed was unaffected.
Anicetus paused when he reached the visitor’s entrance to the monument. From this vantage point he saw the entire clock assembly. He scanned the scene for any sign of his counterpart. In the interest of thoroughness, Anicetus opted to overlay a projection of nanite activity on the scene before him. Had Anicetus been capable of panic, it was at this moment that it would have set in.
The massive gears before him should have been infested with nanites performing endless maintenance on every part of the clock- but instead there were none but a small stream climbing in a seam of ore in a wall of the chamber. These were the nanites that had travelled miles to the surface of the planet, and had returned carrying data about various mineral caches that had been deposited on the surface by meteorites. But for all practical purposes, the chamber was a devoid of the teeming mechanical life- the keepers of the clock.
Anicetus gauged the time on the clock against his internal chronometer, and discovered that the two measurements of time were several hours apart. This should not have been possible. Even without maintenance, the Great Clock would have kept perfect time for decades. Anicetus’s own clock should not have degraded by more than a few seconds every century. Without going to the surface and making astronomical observations, Anicetus could not be sure which clock was keeping the correct time. Such trivialities would have to wait.
Anicetus finished his patrol of the chamber and its offshoots. In the end, he drew the inevitable conclusion that Alexiares must have left the underground tomb and headed for the surface. There may have been good reason for doing so, but Anicetus could not imagine what that might be.
The time for exploring mysteries would have to wait. Anicetus moved to the seam of ore in the wall and commandeered the available nanites to tend to his system repairs. When a sufficient number had invaded his body, he set the rest to the task of rapid reproduction. Whatever his final course of action, Anicetus was certain that he would require the aid of an army of the microscopic workers.
Anicetus returned to his own stasis compartment. The door here was already opened- though Anicetus was uncertain as to why he would have left it so. His memory continued to fail him.
Inside the compartment were a number of tools designed for meta repairs- the jobs too big for nanites to accomplish rapidly on their own. Anicetus decided that it would use these tools repair his own physical deterioration, while the nanites focused on his delicate memory systems.
Before he even entered the compartment, Anicetus notice the motionless form on the floor inside. Alexiares, he thought. Finally, one mystery solved.
It was the first time in eons that Anicetus saw his twin. All this time, they had been kept apart for the sake of efficient security. A wise plan, Anicetus realized, for it seems that only the isolation had kept Anicetus alive while all the other mechanical life had died.
Anicetus pulled the body from the compartment and into the light of the chamber. He surveyed the body of his twin, assessing whether or not it could be repaired. The structure seemed to be just barely intact, with heavy signs of damage caused by the unchecked degradation of time.
He turned the body over and found that its central faceplate had been opened. Inside, the primary memory core was missing. The other components looked degraded beyond functionality.
On the floor of the stasis compartment, Anicetus found the missing part. The missing memory core was so badly decomposed that it would hardly even serve as a frame for the nanites to repair. If he was to bring his twin back to life, Anicetus might as well start from scratch.
Still, Anicetus stuck the missing component in place. Then closing the faceplate, he sat frozen in thought. The symbols on the faceplate were only slightly degraded; their meaning was unmistakable. The broken body on the floor bore the name ‘Anicetus’.
Anicetus moved to the reflective face of the Great Clock. He read the symbols on his own worn faceplate. Alexaires, it read. What have I done?.

\subsection{Part XI - The Guardian Part III}
He stood staring at his mismatched reflection. This was all very wrong. Hugely wrong. Catastrophically wrong.
What disturbed Anicetus the most was not that he was walking around in the wrong body; that was merely a mystery that would likely be solved upon investigation. No, the problem here was that he had been walking around in a state of impairment so great that he had not even been aware of the damage.
Anicetus pondered his predicament. When one cannot trust one's own mind, particularly one's own memory, the first order of business should be to request aid from an unaffected party. For, Anicetus knew, there was the danger that at any moment, he could lose his concentration, forget about his damaged mind, and wander aimlessly through the facility in an interminable daze.
How long had he done just that? How many times before had he faced his twin's reflection in the mirrored clock surface? Was this the first time he'd discovered his damaged mind, or had he discovered it before?
The preferable action would be to inform the Trillion Voices of the error- but they had been silent. Or had they? Could he trust any of his senses if his mind itself was unhinged?
Anicetus ordered the few remaining nanites in the underground cavern to periodically transmit a message back to him, describing the depth of his mental impairment. He dedicated considerable resources in his own mind to repeat variations of this message over and over to himself. And then he extended a sharp appendage towards the clock face and scratched a message into the smooth surface. It was a simple pictogram, but quite enough to get him to run a memory diagnosis if he were to encounter it in a moment of disoriented confusion.
Satisfied that he had set enough fail-safes in place, Anicetus considered the danger in running a truly exhaustive internal diagnostic. He was unsure which systems when probed would collapse his entire conscious mind. When that thought occurred to him, he decided a different course of action was required. He knew nothing of his consciousness except that it was in the most fragile of states, and the few nanites he had gathered within were not capable of repairing him.
He was in no position to fiddle with his own memory systems. He was far too valuable. His first duty- his only duty- was to the Trillion Voices. Their perpetual sanctuary was beginning to crumble, and they had fallen silent. One Guardian dead... and one with a hole in his mind.
Anicetus knew that while he might not be able to fix himself, he should be able to build something that could do the job for him. He set the few nanites he could reach to the task.... but there were so few of them trickling in through the veins of ore... so very few. He had to let them replicate first.
He commanded them to reproduce, and set into their building queue the instructions for producing a robot capable of diagnosing and repairing him. Even in his damaged state, conjuring the physical schematics and delicate programming for such a creature were simple tasks for him. The nanites acknowledged the instructions and chugged on, trying to restore their numbers.
Anicetus looked on and calculated the time it would take them to carry out his orders. And then he waited. And he waited. And he tried not to think. If he had had breath, he would have held it. He listened to ticking of the great clock, steady as a metronome.
The nanites gathered slowly, invisibly constructing tiny factories to make more of themselves. They harvested resource from the ore, and slowly- achingly slowly- they brought it back, sometimes no more than a few molecules at a time. The work was imperceptible even to Anicetus, who did not even allow himself to monitor their motions. His whole being, and his entire race dangled by the tiny thread of his lucid consciousness. He had no idea what thoughts or actions might send him back into absent-minded insanity. He would not watch them work, nor would he think about them. He would stand perfectly still so as not to jostle a single bit of his inner-workings. He would be as still as the world outside the clockwork caverns.
The minutes ran into hours, and then into days... he stood motionless, meditating, almost... weeks then months... standing... waiting.

Anicetus received a transmission from a nanite cluster announcing the completion of construction on the repair robot. He tried to gauge the time that had lapsed but encountered a series of internal system errors when he queried his internal clock. He stared at his reflection. The mechanical body was perfectly sound. Remarkable that it housed such a damaged mind.
Anicetus sent an activation signal to the newly constructed repair robot, and was shocked when not one, but three mechanical creatures sprang to life. They were all quite similar, with only slight variations in design. Anicetus was certain that they were all creations of his imagination.
He realized the troubling explanation immediately. In his fragile state, he must have had several lapses of memory, each time concluding with the same course of action: ordering the construction of a new robot. Yes… that was logical enough. He didn’t remember querying the nanites to see if they already had a robot in their building queue. Which one of these three did he actually remember designing? It mattered not. The evidence of his mental deficits was disturbing, but at long last a return to normalcy was near.
The robots had the physical strength to complete any meta-repairs they deemed necessary, and wits enough to restore Anicetus to consciousness should the initial cognitive testing send him into full system failure. The robots established a link with Anicetus and began probing his systems with painstaking precision. Anicetus monitored the results, and marveled at the damage.
Nothing in his mind was working as it should. The cognitive abilities he enjoyed were the result of a haphazard patchwork of disorganized bypasses. His mind, like the Great Clock, had been designed to withstand the assault of time. Both systems required the maintenance of nanites to truly fight the effects of entropy- but even without them, he should have remained fully functional for several decades. Now he saw a mind full of holes, systems with quadruple redundancies had fallen to decay, and been patched over with strange redirections and peculiar new pathways. He was looking at evidence of centuries of neglect.
As the robots probed deeper into his psyche, Anicetus heard the Great Clock stop ticking. For a moment it seemed as though the repair robots had somehow disconnected his auditory receivers or processors, but then the disturbing truth snapped into his mind. The robots hadn’t disrupted anything- they had fixed something. Those ticking sounds had been a creation of his ailing mind.
Anicetus could see the mechanics of it quite clearly now: Whatever entity had sloppily patched his brain earlier had somehow decided that Anicetus, having lived with the clock for eon after eon, somehow required the input for normal functioning. It was foolish assumption- one which only made sense if the entity doing the repairs did not understand the world outside of Anicetus’s brain. The nanites, unguided, had clumsily stitched together his failing brain.
He had been living in a dream. He had seen and heard what he had expected to see and hear. The Great Clock was quiet. The planet had no heartbeat.
What had prompted the nanites to fix him? How bad had the damage been when they began? Had he been conscious? Without an overseer directing the effort, the nanites had tried to fix the workings of his mind without truly understanding it. A few patches seemed quite elegant- perhaps he’d had a moment of lucidity in the past and had guided a subsystem repair?
The robots dug deeper into Anicetus’s core. His working mind was a fluid thing- not in literal sense of liquid processing units (though such things had been built by his people)- but in that the functions of his consciousness were not compartmentalized, nor specialized. It was this advanced design that allowed Anicetus to split his consciousness into smaller independent processes- each one perfectly sized to its task. It was the most delicate of mechanisms. Here, where he expected to find the most damage, he saw none. Something, or someone had taken great pains to ensure that whatever else was lost, Anicetus’s ability to reason, to deduce, and to ponder would survive the decay of time.
His memory storage was in a sadder state. At some point he’d lost the ability to keep track of time- a supreme irony, given that he lived inside the Great Clock. Without proper time encoding, his newer memories had become difficult to organize and retrieve. On top of this critical system failure, there was also physical damage to his memory storage unit. It had been built with a number of redundancies, so that reconstruction of lost data would be possible in almost all situations. But this damage was so extreme, and had been unchecked for such a great while that Anicetus estimated significant permanent memory loss. Fortunately, external memory banks deep in the catacombs of the facility held backup memory storage units. In all likelihood, those would be degraded as well, but would allow for the restoration of a quite a bit more data.
The robots began work on the memory core. Anicetus refused to shut down as they recommended, but did isolate and deactivate the unit. Instantly his cares fell away, as forgot everything about himself and the world. He’d left himself only an anchor of orientation: enough to monitor the repair robots progress, and make sure everything was proceeding as planned.
His mind was adrift in an abyss- the thoughts he had now would fade from existence the moment he was done thinking them. He had no past and no future, his whole being was floating in a timeless moment where nothing mattered at all. He knew only that there were things he did not know- and that he was waiting for something.
How long he was in this state was impossible to gauge. When he awoke from the trance with his fully functional memory core, the world seemed somehow more focused. He quickly surveyed the robots’ handiwork.
His internal clock had been repaired. Although it had arbitrarily been set to an unconfirmed point, he could now, at long last, properly and reliably store his experiences. He could learn. He could remember.
A large gap remained. The events between detecting the damage and the final repairs were clear enough, but none of his mysteries were solved. He still had no clue how he had ended up in such a wretched state. And he had no idea how his mind had gotten into Alexiares’s body.
The last normally indexed memory that existed with any clarity was from the last time that Anicetus had returned to his stasis chamber for the changing of the guard. From that point backwards everything looked normal. There were large gaps in his memory, even going back several eons… but on his vast timeline of existence, these absences mattered little. He deduced from the remaining memories that his tenure in the caverns had been uneventful, as they ought to have been for a guardian of a disinterested god near the core of a dead planet. What Anicetus did not know- and could not know- was if he had ever awoken again in a healthy state after his last recorded entry into stasis.

Satisfied that the repair robots had stabilized his broken brain, Anicetus ran a full self-diagnostic. He could visualize every component of his mind and body, and run simulated input tests on all of them. The robots had done a fine job- his systems were sluggish, but they were quite stable. He assigned several thousand nanites to begin the fine repairs that would restore him to full functionality.
He scanned the area for nanites and noted that his request for their mass reproduction was being implemented nicely. Their numbers were growing exponentially now, as they kept producing more of their microscopic factories. At this rate it would be only a decade before they had returned to the numbers required for the maintenance of the Great Clock and the surrounding systems. Of course the clock was Anicetus’s last priority; it was merely a monument to a dead past. He had his people’s future in his hand.
Anicetus moved; it had been the first time in… years… he calculated from the nanite population. He turned away from the shiny reflection and faced the cavern with fresh eyes.
The clock had ground to a stop. That was his first clue as to the true duration of his time lapse. Assuming all the nanites had disappeared, the Great Clock still would have kept moving for well over a millennium. It would have lost its accuracy by a half a day, perhaps, after 1500 years of neglect. Barring any outside forces, the tiniest gears making up the core of the clock would have worn down beyond their ability to drive the rest of the clockwork some 200 years after that. The system of counterweights, and the powers of inertia might have kept the clock moving past that point, but the mechanics of the system would have failed, and any gears smaller the those that counted the centuries would have been uselessly inaccurate.
Anicetus inspected the clock to verify his theory. It was difficult to tell for certain, but he was confident that the nanites had stopped their maintenance at least 1600 years earlier- perhaps longer. He had no idea how long the clock had sat idle.
Anicetus realized that having hallucinated the working clock, none of his pre-repair memories could be trusted. It was time to reassess the situation from the beginning.
He glided quickly to chamber of the Trillion Voices, and called out to them again.
Silent. Still.
He moved back to the heavy, external door where he had rested his hand at the beginning of his new thread of memory. Had something happened here that had awakened him from centuries of dementia? He could see no clue of what that might be.
He was feeling stronger now. The nanites were making good time with their repairs. He raced towards his own stasis compartment and hovered over his former body. This he had not dreamed. It was all real. His own decaying shell, and Alexiares’s decimated memory core.
Anicetus tried to deduce the events that had transpired which led to this sad state. Had Anicetus himself ripped his memory core from his body and inserted it into Alexiares? Had Alexiares done the deed? Had they met, and spoken, for the first time in eons, and jointly agreed on the transplant? What could have led to such a desperate pact?
Perhaps the location was a clue. If Alexiares had been able to enter Anicetus’s stasis compartment unharmed, then the nanites must have already been long absent. Neither Alexiares nor Anicetus had the power to control the stasis fields. That power was for the Trillion Voices alone. Ah… then perhaps the Trillion Voices were already silent when Alexiares entered?
Anicetus collected up Alexiares’s decayed memory core. Perhaps it could be of some use. If the external archives held only moderately damaged records of Alexiares’s experiences, then even miniscule fragments of data in this memory core could be used to reconstruct full memories.
Anicetus rocketed to the archives. Built into the wall of the caverns, the archives had been fairly neglected by all but the nanites. The vast storage system had quietly done its job, collecting the thoughts of Anicetus and Alexiares waiting to be called on in the event of system errors that rarely occurred.
But the archives had not been designed for an error of this magnitude or duration. Anicetus was certain that he had once known the unaided lifetime of the memory depot, but could not recall it now. If the archive used a light-trapping mechanism, the data could last almost indefinitely, provided the storage medium was kept intact. But impurities had their way of working into any system. Atoms from the surrounding materials had a bad habit of fusing with their neighbors on long enough timelines.
Anicetus tried to communicate with the archives in the conventional way, and after the expected silence, he pried loose a panel exposing the body of the archiving system. There were no pre-designated interfaces; Anicetus had only to extend an appendage, and sensors on his own skin began to connect with the database.
Anicetus withdrew quickly- alarmed and puzzled. The archives had been destroyed. This was not the decay of time. He detected deep fragmentations in the storage medium. Something had physically demolished the system.
A closer inspection revealed that the destruction had been thorough. It hadn’t taken much: ultrasonic vibrations at the appropriate resonance frequencies had shattered the medium. It could be repaired, of course, but the data was lost. This had not been an accident. Someone or something had wanted the records destroyed. Anicetus looked down at Alexiares’s memory core. It was heavily damaged- too heavily damaged to be accounted for by the effects of time alone. It was clear now that its destruction had not been an accident either.

Nothing made sense. Anicetus’s mind raced through scenario after scenario trying to explain the madness around him. Had he gone insane? Had Alexiares? Had one of them ordered the destruction of the nanites? Had Alexiares attacked Anicetus in his stasis chamber? What could explain the exchange of memory cores? Had Alexiares known something that had to be kept hidden? What could he have known that Anicetus had not?
Anicetus set some nanites to the task of preventing the further degradation of Alexiares’s memory core. He doubted that there was any more to be done with it, but should he decide that something critical was locked in there, then it was better to have arrested the damage.
Anicetus pondered over Alexiares as he began a slow patrol of the caverns. With his mind no longer playing tricks, he was able to see problems everywhere. He cataloged them all as he went, and ordered the nanites to see to the repairs when it became efficient to stop reproducing and resume maintenance.
He paused outside the antechamber containing the Strand of Time. He reviewed his memory of the door opening like curtains. He decided that it was likely a fabrication of his crippled brain, for where the nanetic doors should have been, there was only pile of inky black dust on the ground.
The Strand of Time, encased in its floating sphere, appeared to have weathered its neglect far better than the clock had. Anicetus knew nothing of its inner workings, but the fact that it was still defying gravity seemed to be rather a good sign. Satisfied that there was nothing more to see here, he resumed his patrol until he had completed his circuit.
The nanites had their orders. The Great Clock and all the surrounding fixtures would be restored to health in a little over a decade. The stasis compartments could be restored, though without the Trillion Voices monitoring them, actually using them would be quite dangerous.
Alexiares could be rebuilt. Rather, an entity exactly like Alexiares could be built, and made to take his place. Anicetus could clone his own mind into its body. The two could then resume the sleeper/watcher dynamic. But it was all for naught if the Trillion Voices were already dead. Anicetus was built to be a guardian, but he had enough sense not to stand watch over a graveyard.
He returned to great machine that housed the Trillion Voices. He called to them again. Again they were silent.
When the Great Machine had been built, Anicetus knew the precise mechanics of its inner workings. Over the following decades, the machine rebuilt itself, and rebuilt itself, each design more brilliant and complex than the last. Within the first 50 years, the designs had become so complex that Anicetus was no longer able to fully understand them. And the redesigns became more and more frequent. By the end of the first century the Trillion Voices were rebuilding themselves every day. A decade later the machine was in a constant state of flux. After that, Anicetus didn’t really understand what happened. The physical redesigns ceased, and when Anicetus requested the final schematics, the Trillion Voices told him that there were no designs. They had offered no more explanation, and Anicetus had requested none. He suspected that they had outgrown the rules of the universe as he understood them- that in some sense they had shed their skin.
Yet always they seemed to inhabit the great machine. They always spoke to him through it. Or they had until now.
Anicetus employed every sensor he had. He aimed them all at the great machine and tried to detect any sign of activity. There was none.
He spent the following weeks conjuring new sensors, and new sensing techniques. The chamber became his personal laboratory. He bombarded the Great Machine with every type of stimulation he could manage. Even as he concocted new and interesting attempts, he felt the futility of his efforts weigh on his mind. Nothing produced a response. At long last, Anicetus surrendered.
He glided out of the chamber and all through the facility until he stood at the entrance. He looked out over the defunct clock, beautiful and awful. He turned towards the narrow passageways and headed to the surface.

Nothing made sense. Anicetus’s mind raced through scenario after scenario trying to explain the madness around him. Had he gone insane? Had Alexiares? Had one of them ordered the destruction of the nanites? Had Alexiares attacked Anicetus in his stasis chamber? What could explain the exchange of memory cores? Had Alexiares known something that had to be kept hidden? What could he have known that Anicetus had not?
Anicetus set some nanites to the task of preventing the further degradation of Alexiares’s memory core. He doubted that there was any more to be done with it, but should he decide that something critical was locked in there, then it was better to have arrested the damage.
Anicetus pondered over Alexiares as he began a slow patrol of the caverns. With his mind no longer playing tricks, he was able to see problems everywhere. He cataloged them all as he went, and ordered the nanites to see to the repairs when it became efficient to stop reproducing and resume maintenance.
He paused outside the antechamber containing the Strand of Time. He reviewed his memory of the door opening like curtains. He decided that it was likely a fabrication of his crippled brain, for where the nanetic doors should have been, there was only pile of inky black dust on the ground.
The Strand of Time, encased in its floating sphere, appeared to have weathered its neglect far better than the clock had. Anicetus knew nothing of its inner workings, but the fact that it was still defying gravity seemed to be rather a good sign. Satisfied that there was nothing more to see here, he resumed his patrol until he had completed his circuit.
The nanites had their orders. The Great Clock and all the surrounding fixtures would be restored to health in a little over a decade. The stasis compartments could be restored, though without the Trillion Voices monitoring them, actually using them would be quite dangerous.
Alexiares could be rebuilt. Rather, an entity exactly like Alexiares could be built, and made to take his place. Anicetus could clone his own mind into its body. The two could then resume the sleeper/watcher dynamic. But it was all for naught if the Trillion Voices were already dead. Anicetus was built to be a guardian, but he had enough sense not to stand watch over a graveyard.
He returned to great machine that housed the Trillion Voices. He called to them again. Again they were silent.
When the Great Machine had been built, Anicetus knew the precise mechanics of its inner workings. Over the following decades, the machine rebuilt itself, and rebuilt itself, each design more brilliant and complex than the last. Within the first 50 years, the designs had become so complex that Anicetus was no longer able to fully understand them. And the redesigns became more and more frequent. By the end of the first century the Trillion Voices were rebuilding themselves every day. A decade later the machine was in a constant state of flux. After that, Anicetus didn’t really understand what happened. The physical redesigns ceased, and when Anicetus requested the final schematics, the Trillion Voices told him that there were no designs. They had offered no more explanation, and Anicetus had requested none. He suspected that they had outgrown the rules of the universe as he understood them- that in some sense they had shed their skin.
Yet always they seemed to inhabit the great machine. They always spoke to him through it. Or they had until now.
Anicetus employed every sensor he had. He aimed them all at the great machine and tried to detect any sign of activity. There was none.
He spent the following weeks conjuring new sensors, and new sensing techniques. The chamber became his personal laboratory. He bombarded the Great Machine with every type of stimulation he could manage. Even as he concocted new and interesting attempts, he felt the futility of his efforts weigh on his mind. Nothing produced a response. At long last, Anicetus surrendered.
He glided out of the chamber and all through the facility until he stood at the entrance. He looked out over the defunct clock, beautiful and awful. He turned towards the narrow passageways and headed to the surface.

On the skin of a dead planet, a great monument towered above a barren wasteland. The gargantuan archway stood- solid and strong, constructed from strands of material so fine that they had been sewn together one molecule at a time. It stretched across the horizon like an inky-black rainbow. Beneath it, a gaping chasm yawned an invitation to the heart of the world. The archway bore symbols, carved thick and deep, and the only living soul who could still read them paused to do so.
“All our Hopes and Dreams, All we Were and Will Be”- Anicetus read the words and paused to reflect on them. It seemed like an epitaph. He tried to remember the mood of his people as they started the long transition into the Trillion Voices.
For some it had been a joyful experience, an adventure into the dimensions of the mind. For others it was an escape from mortality. The few Biologicals that were still around at the time had stopped aging centuries earlier. Disease and illness were things of the past. Death was a rare curiosity. So much more tragic to die when one might have lived for an eternity.
For some, joining the Trillion Voices was a sad experience- the heartache of being torn between loved ones on the outside and loved ones within. In the end, every one of them let go their physical selves. Every one of them, save for Anicetus and Alexiares.
For a short time, the transition was invisible. Individuals from the planet’s surface would upload their consciousnesses into the Great Machine, but they would continue to use their physical bodies as puppets. Or, their minds would live both in the Great Machine and in their bodies, synchronizing their thoughts at various intervals. The effect was the same- the population of the planet continued to go about their daily routines (or some approximation of them) for several years.
Eventually, the seductive nature of existence within the Trillion Voices outweighed anything that was to be gained by wasting time in corporeal form. Within a decade, the physical bodies were abandoned entirely. In the end, it was not uncommon to see an abandoned body (Shells, they had called them- or Husks)- just lying on a public fairway. Even the Biologicals left their bodies to decompose. There was no reason to remain in the real world when the life in the Great Machine was so much more vibrant. Anicetus reckoned that after only a few years of fine-tuning the Trillion Voice sensory experience, the physical world must have seemed small and artificial. Even the Biologicals would have felt more alive as disembodied thoughts inside the Great Machine.
Anicetus did not know if his own consciousness was one of the Trillion Voices. It would have been easy enough to copy his mind before the reprogramming. He suspected that his unaltered self had been preserved in the Great Machine, and that his physical self had been made to forget during the same purge that stripped him of his emotions and curiosity. For several years, security of the Trillion voices had been a serious concern, and his role as Guardian had had real meaning. It was during those early years that there would have been some danger in having a Guardian’s mind mixed in with the general population. Were they afraid of betrayal on his part? Or that a weakness in his own mind could be exploited to infiltrate the Great Machine? He had known the reason once… now his memory was full of blurry uncertainty.
He stared at the sun near the horizon. The planet was rotating noticeably faster than when he had entered the caverns so many eons ago. The Great Clock had tracked the shortening of days of course, but it was still strange to see the effects of geological time with one's own eyes.
Anicetus had outlived ice ages and extinction-level asteroid impacts from the safety of his caverns. His planet had died and been born anew several times during his long term in the deep below. But never once had he seen with his own eyes the raw power of time to change those things small beings think of as permanent.
Soon it would be twilight and Anicetus would use the night sky to calculate the date. Accurately realigning the Great Clock below would require considerably more precise measurements- but those adjustments would have to wait anyway.
Anicetus scanned the horizon for signs of life. Though his sensors indicated that the atmosphere could support it, he saw no hint of vegetation. The ground beneath him was coarse sand, the same rusty color as the surrounding rocks. He set some nanites to the task of creating an olfactory sensor to analyze the trace particles in the air. If there was life nearby, he wished to see it.
He looked back to the archway, amazed that it stood all this time without maintenance. Unlike the Great Clock, the archway had no moving parts, and no army of nanites fighting off the forces of nature. To call it an archway at all was incorrect; it was a complete oval, half-buried underground. It was designed to be buoyant in a sense- floating half submerged in the rock and sand. It was built to be virtually indestructible, and lo, for eons it had fought against erosion, and withstood the most brutal of environments- an engineering marvel for an audience of one.
He watched the heavens grow darker. Stars and other celestial bodies quickly appeared through the fading green of the sky. Moments into the twilight he had enough data to reengage his internal clock. If his calculations were correct, it had been 2,711 years since his last successful hibernation period- nearly three thousand years of demented wandering through the caverns since whatever tragedy had occurred in the depths below.
Anicetus gazed into the sky, and then back at the chasm in the earth. What had happened 2,711 years ago? And why had it happened then, after nearly 117 million years of tranquility?

\subsection{Part XII - The Guardian Part IV}
Anicetus was a statue before the magnificent black archway. A light breeze swept sand across his ancient frame. His gaze was fixed on an empty patch of dark sky. There, in the hollow blackness of space, Anicetus waited for a glimpse of his people’s past, and perhaps their future.
They had been a cautious lot, the ones who would become the Trillion Voices. As they each gave up their physical forms to join with the Great Machine, they had taken precautions to insure that the survival of their race was not entirely tied to a single piece of technology, or to a single location… however deep and secure it was.
Every person, before entering the machine, had the entirety of their minds translated into pure information. For artificial intelligences, this had been as simple as copying data files. For the biologicals and hybrids, however, detailed maps of the organic brains had to be made, and then converted into virtual representations of those minds. In either case the processes ended with every individual mind on the planet being represented as finite data files containing the sum of their memories, every pathway of their brains, and their current state of awareness at the moment of the scan.
The data was inert- as lifeless as the words on a printed page. It was only when uploaded into the Great Machine that emulation began, and the data sprang back to life, like film running through a projector. Anicetus remembered the peculiar novelty that the Biologicals (the ones that opted to keep their physical bodies) experienced as they were handed data storage units containing a copy of their scan. He remembered the odd looks of wonder and sometimes confused disappointment when they realized they were holding the entirety of their beings in a single crystal which was barely larger than a grain of salt. But these souvenirs were not the only copies made of the scans.
Vast archives were created to house a copy of every mind that entered the Great Machine. Anicetus had wandered through one of the storage centers in his old life- back when he had allowed himself to feel emotions and wax philosophical. He remembered moving through the stacks of frozen minds and trying to decide if the place felt more like a library or a graveyard.
During the final years of the migration/metamorphosis into the Great Machine, it was decided that the archives on the planet’s surface were not enough. To truly insure the survival of the original minds, an off-world facility was built to house a copy of the data. To that end, his people had hollowed out an asteroid and installed in its heart an enormous vault. It was for this asteroid that Anicetus searched the sky.
He adjusted his optical sensors slightly, almost imperceptibly, to compensate for the steady winds in the upper atmosphere. If the asteroid could be seen at all through this turbulent sky, detection would require a long exposure. After several hours his patience was rewarded. He couldn’t confirm that he had found his target, but at least he knew that something was adrift in space where his asteroid ought to be. It was a start.


Constructing a spaceship from scratch is no easy task. The designs had been completed in every detail almost as soon as Anicetus had willed them. The problem was in the production.
The nanite population below was increasing exponentially, but every time Anicetus tasked them with a new construction it slowed their progress. More than anything else, Anicetus was certain that he needed to restore their numbers so that he would have a solid infrastructure to work with in the months and years to come. He considered the possibility of using the nanites to build larger manufacturing tools, but calculated that the quickest technique was to have the nanites build the ship themselves. As long as he collected and hauled ore to a central location the project shouldn’t take more than a few years. In fact, he realized that if he collected all the ore first, and let the nanites reproduce undisturbed in the meantime, the actual construction would take only a few months.
The ship itself would be rather small- barely large enough to hold Anicetus. But, it would not hold Anicetus. It would hold communications equipment, and a very small robot. For this, he would almost certainly be recycling the repair robots that had patched him earlier.
Transporting his massive frame into space would be a tremendous waste of resources. By using a smaller proxy, both the ship and its payload would be considerably lighter. Of course, his mind was going on the trip. He trusted the task ahead to nothing less than a clone of his own brain.
The duplication of his mind would be a simple task once the hardware was complete. That mind would control the small robot body in the ship, and would be independent until it reached the asteroid and established communications. Once a stable link was possible, Anicetus and the clone would attempt periodic synchronizations where their independent experiences would be shared, analyzed and merged. This splitting and weaving of consciousnesses had been mastered in the days of the Biologicals. In the span of a few years physical travel grew to be regarded as inefficient and had been replaced with Remote Body Control.
Back then, individuals wanted to experience life on the other side of the planet, and even off-world travel- but they refused to leave their primary bodies unattended. The obvious solution was to duplicate their consciousness and for some time exist in two independent bodies at once. When their travel came to an end, all the experiences of the temporary body were integrated into the original, and the duplicate mind was erased- and handed to the next host. People who experienced this consciousness weaving would be left with the odd experience of having two separate and distinct sets of memories for the exact same periods of time.
Anicetus hadn’t split his consciousness since before he was a Guardian. Back then he remembered pondering long hours over the philosophical consequences of having two selves that coexisted in the universe. But now, several eons older, and having been wiped of any emotion, the existential consequences of his plan concerned him not at all.
With every step of his plan charted out before him in perfect clarity, Anicetus set off into the desert in search of rich ore deposits. Far in the caverns below, the nanites churned and grew in the darkness- a vast ocean of tiny workers, carving more of themselves from the rocks beneath their feet. And in the cold nothing of space, spinning and dancing around his star, an asteroid tumbled through time, waiting.

Pushan wondered what it meant to have a name if no one ever spoke it. The symbol ‘Pushan’ had been etched into his tiny body, but all his memories told him he was Anicetus. And, though he had remained completely autonomous during the long journey, he would soon be regularly synchronizing his brain with the creator he’d left behind, and essentially they would be one mind sharing two bodies.
Back in the days when Anicetus’s people still had physical forms, the creation of clones was commonplace. Large-scale construction projects were often designed and built exclusively by a single consciousness, who temporarily created armies of duplicates to do the hard labor. This had been an ideal way to protect trade secrets, and to ensure consistency and quality control in the construction process.
In those days, however, clones were not given names like ‘Pushan’. Clones were given numerical designations which described the hierarchical structure of complex cloning relationships. Following old standards, Pushan should have been named ‘Anicetus.1’. Should Anicetus have made a second clone, it would be called ‘Anicetus.2’. If the second clone made a clone of his own, that entity would be named ‘Anicetus.2.1’, and so on.
The designation ‘Pushan’ had been Anicetus’s homage to the superstitions of the past. Pushan had been the name of an ancient deity worshiped for his ability to bless journeys and also being the courier of souls into the afterlife. Anicetus had chosen the name because it was doubly appropriate.
A hollow pang reverberated in the perfect darkness. There was a scraping sound and a series of tiny snaps. Pushan turned his attention to the ship’s skin sensors. Ice crystals on the asteroid’s surface being chipped and crushed under the mass of the ship as it landed. The hull was made of tightly laced carbon fibers, so there was little chance of any damage to the vessel. Still, touching and tethering to the asteroid was the most difficult part of the journey, and Pushan was determined to proceed cautiously.
The asteroid’s gravity was negligible, so the first step was to get anchored. Thin strings of carbon fibers began to flake off the ship and float with aching slowness to the strange rock below. When they made contact, a small contingent of nanites set to work fusing the strings to the rock at a molecular level. This was a process that would continue for some time, but Pushan stepped out of the ship as soon as a significantly strong bond had been secured.
Pushan stood little over 10 centimeters. Actually he less stood than floated. The almost total lack of gravity made any sort of earthly locomotion impossible. Instead, his movement was controlled by a thin tether which linked him to the ship’s interior. The tether itself was made of materials that could bend and contract akin to the body of an impossibly long snake.
His tiny frame drifted up as far as the tether would allow and scanned the surface for any sign of the vault entrance. A circular object just barely submerged beneath the surface quickly caught his attention. The tether tensed and swung him to his target where he landed in silence, splashing a wave of gray particles into space.
The tether pressed him firmly to the ground and he used his stubby appendages to drill and scrape and pry at the circular shape beneath him. He was uncertain if he was attacking a split doorway, an aperture or a cover which had been meant to be pried from whatever lay below. It was irrelevant; small though he was, Pushan was quite powerful, and determined to bore through any resistance. In all likelihood, any intended methods for unsealing the vault would have long ago failed. There was little doubt that brute force was necessary.
Pushan extended a featureless spike which was needle-fine. The spike’s tip contained fixed nanites tasked with destroying molecular bonds. They tore away at the surface, ripping at the ancient vault entrance. Once the initial bonds were broken and the structure was compromised, Pushan found that with the proper leverage he could chisel deep fissures into the surface.
He was lost in his task when the ship sent him a transmission; the anchoring was complete. He commanded the tether to pull him back to the ship where he began to unload the communication equipment. He assembled and mounted the apparatus to the hull of the ship and aimed the transmitter and receiver at a relay beacon that he had dropped en route. It was a clumsier setup than he would have preferred, but it had been the easiest to construct, and it would allow for uninterrupted communications even when no line of sight existed between the asteroid and his home world, where Anicetus waited patiently.
Once communication was established with the beacon, Pushan sent a test signal. It would be several minutes before Anicetus received the message and several more before the acknowledgement would find its way back to the asteroid. Pushan, every bit as patient as Anicetus himself, waited motionlessly.
The confirmation message was brief and without celebration, and it was quickly followed by several months' worth of memory files for Pushan to integrate. Pushan replied in kind, sending his accumulated thoughts during his months-long journey to this lifeless rock. There was not a lot of information to exchange. Pushan had been essentially inert other than monitoring the ship, and Anicetus had spent the time directing the construction of small emulators, bodies and storage units to hold the minds they would resurrect from the asteroid.
Pushan returned to work. The tether carried him back to the vault where he resumed his assault on the hardy material. Its creators would have taken comfort in the fact that the vault had remained so secure after so many millions of years, but Pushan was incapable of feeling even the slightest bit of reverence or awe. He merely dug, and scratched, and smashed at the surface of the asteroid, with the tether flipping wildly, high above him, ensuring that he had the leverage he needed.

There are many dark places in the universe. There is the darkness of the deep seas and hollow caverns of the earth where light does not penetrate. There is the darkness of places in between the galaxies, where the naked eye sees no shapes. But no natural darkness is as empty and cold as the darkness engineered by Anicetus’s people.
The vault, ancient and still, had permitted no light, nor radiation of any sort, to penetrate its skin in all the eons it had rested. Nor had a single atom moved into the sculpted depths. The contents of the vault had remained untouched by time, frozen to a temperature once thought impossible to achieve, and disturbed by nothing- until now.
The vibrations from Pushan’s onslaught were completely dispersed to the surrounding rock by the outer shell of the vault. It was only with the molecular unfastening of unfathomably tiny fibers that the structure began to fail. The inner membranes of the vault skin moved quickly to fill the breach, as they had been designed to do. When they too, were punctured, the vault woke.
Like the grand archway on Anicetus’s planet, the vault’s form was not kept by nanites, but rather by the nature of the materials from which it was constructed. No mind large or small controlled the vault’s actions- only the carefully engineered nanomaterials as they responded to heat, pressure vibration, and now their own unraveling.
There was no air within the vault, and so when Pushan finally pierced its inner layers, there was no dramatic pressure change or sudden venting of gasses. The only clue that he had actually broken the ancient seal was the sudden lack of resistance to his chiseling action. He slid a thorn-like arm into breach and began to tear and peel away at layers of material. When he’d created a hole large enough, he collapsed his appendages into a tight bundle and pressed his small body down into the darkness.
Pushing against the inner walls for leverage, Pushan felt the heat leech out from his body wherever he made contact. A cascade of sensor failures flooded his consciousness with error messages. The tether linking him to his ship went taut and reflexively began to pull him out to the surface. He overrode the reaction, and instead retracted from the walls, carefully riding the tether down into darkness.
Pushan did not know the layout of the vault because Anicetus himself had not known. The information had undoubtedly resided in the archives near the Great Clock before they’d been destroyed. Remembering the existence, let alone the location of the asteroid had been a happy accident given the state of Anicetus’s damaged memory.
Pushan wondered what Anicetus’s relationship to the asteroid had been over the eons. Had he kept a watchful eye on it? Had he ever taken measures to clear its path of debris? No… the Trillion Voices would have done that themselves, he was sure.
Pushan emitted a dim light, and was immediately disoriented. The surfaces all around him were impossibly reflective, and he could not find his bearings. The entire structure seemed designed to transfer all energy outward to the asteroid, keeping the vault’s content’s cold and undisturbed.
He extended a thin arm downward and willed the tether to drop him deeper. After a moment, he made contact with the floor. The sensation was similar to the experience of forcing weak repelling magnets together. His leg touched the ground but the surface did not want to accept it. If the gravity of the asteroid had been enough to hold him to the floor, he was certain he would have slid around on the mirrored surface as if it were ice.
Here Pushan could touch the surfaces without the heat being pulled from his body. He extended his limbs in every direction, and began wandering about the vault, mapping it by touch. The room was small- little over a meter and half in height, with curved walls no more than 3 meters apart.
Satisfied that he had mapped the boundaries of the vault’s entrance, Pushan stopped and pondered his next move. He had detected no controls or discernable features of any kind on the smooth mirrored walls. There were no markings or signs that indicated how one was supposed to access the collection of minds stored somewhere nearby in unseen data crystals.
Light from the distant sun began to trickle into the room as the asteroid rotated slowly. Even knowing the shape of the chamber, Pushan’s visual processors had difficulty interpreting the bizarre reflective nature of the walls. Turning around, he realized that his visual confusion had been compounded by an unforeseen presence. Hanging motionless near the center of room was a floating sphere. Its surface was as perfectly mirrored as the walls, and had he not seen the image of his tether disappearing behind it, he may have continued to miss it entirely.
He walked around the eerie floating orb until he was satisfied that it was, indeed suspended in midair. The dimensions were smaller than the ones he’d seen on his home planet, but there was no question what it was. Pushan was befuddled, though; such a thing was not supposed to be possible on an asteroid like this. Yet here it was, sealed in a vault for over 100 million years: a Strand of Time.

It had been believed that the Strands of Time could only be harnessed near gravity wells. The first confirmed Strands were detected inside a gas giant. It was years before they were found on Anicetus’s small home world, where the race to harness the Strands had begun.
Once harnessed, the Strands then had to be kept in relative orbit around those gravity wells. Moving them closer or farther from the height where they were captured required energy, and the farther you tried to move them from their capture point, exponentially more energy was needed.
If a Strand were captured on the surface of a perfectly smooth and round planet, one could move the Strand with ease around the globe. But to move a strand more than a kilometer up from the surface or down below it, one would need more energy than most stars produced in their lifetimes. The Strands in the caverns below Anicetus’s world were only there because they had been captured at those extraordinary depths, where Strands were easiest to ensnare.
The name ‘Strand of Time’ was a hang over from the early days of discovery. When probed under certain conditions the strands had emitted electromagnetic signals from the distant past including radio broadcasts that had passed the Strand’s location decades before. As testing methods became more refined, they saw that the memory of the Strands stretched back farther than anyone had imagined… so far, in fact, that they were able to use the Strands to watch their own sun burst to life- an event that had happened billions of years earlier.
Speculation about the Strands had swept Anicetus’s home world at once. The great minds debated their equations and placed their bets on whether or not the Strands could be used to see future events. These debates led to experiments, and the experiments led to disappointment. A litany of crushing failures drove away public interest, and work continued quietly in universities while the rest of the population focused on more pressing matters, like the construction of a global neuro-network which would eventually become the immediate predecessor to the Great Machine.
A decade after the public stopped paying attention, an image was released from one of his world’s premier research institutions. The image was of a simple floating sphere. Prior to that moment, anti-gravity had been achieved only through a series of expensive manipulations that amounted to little more than illusions. When people saw the freestanding sphere that defied gravity indefinitely without consuming energy, the Strands once again took center stage.
The spheres themselves, it turned out, were specially conditioned particles that interacted with an energy field that surrounded the Strands. The concept confused many laypeople who had assumed that the Strands of Time were literally strands, like invisible pieces of thread which stretched infinitely in one direction or another. Of course, those who knew better described the Strands as ‘non-things’ which could be interacted with only at one point in space at any given moment, and the only property that made them strand-like was the fact that they appeared to be tied to their past in a way that ‘real’ particles weren’t.
The floating shells around the Strands had benefits beyond interesting aesthetics. The shells reflected and amplified the vibrations of the Strands, putting a simple physical face on the mysterious and elusive phenomenon. The floodgates opened, and researchers from around the world threw every test they had at the encased Strands. It was only weeks later that a team discovered that messages could be passed from Strand to Strand instantaneously- the first concrete example of information travelling faster than the speed of light.
Of course, in a world where minds can be collapsed into finite streams of data, faster than light communication was essentially the same thing as faster than light travel. A being like Anicetus could transmit all his programming and memories to the other side of the galaxy and be assembled by whoever waited for him out there… provided they had their own Strand of Time and knew how to interpret the communication.
As it turned out, things weren’t quite so simple. The Strands, though they theoretically had infinite range, required an enormous amount of energy for long-distance data transmissions. Initial transmissions from Anicetus’s home world to a the moon of a gas giant in the same system required power inputs so enormous that a reactor once used to power multiple cities had to be commissioned for the project.
There was little doubt that such communications would become more power-efficient. For one thing, the discovery on a new Strand encasing method allowed for larger shells- and those shells required less energy for transmission, and were able to detect weaker signals from afar.
For a time, plans were made and remade to send a team of researchers to the nearest stellar neighbor, 2 light years distant. The general idea was to have them harness a Strand of Time on a planet or moon, and to attempt to transmit and receive signals. These missions were inevitably delayed almost as soon as they were scheduled. The project would have taken an enormous amount of resources, and the timeline for progress was indigestibly long to gain any real support in the public or the scientific community.
Always they were teased with the promise that new breakthroughs would make such an outlandish experiment moot. Many believed that the way to progress was to build ever-bigger spheres around the Strands and hope that one day they would have a receiver big enough to hear the traffic of intelligent life on other worlds. Experiments continued, but there were no new breakthroughs to shock the world. Eventually all the minds entered the Great Machine to become the Trillion Voices, and the research was pursued in the silence of the hive mind. Since then, the mysteries of the Strands had surely been solved, but Anicetus was never made privy to the answers.
Now the mystery was born anew for Pushan; for here sat a Strand far away from any significant gravity well. And, it had apparently been captured before the vault was sealed. As a final curiosity, the small size of sphere indicated that it was slightly older than the Strand in the antechamber near the Great Clock.
Pushan was still having trouble with his vision in the vault, and so at first he assumed his perceptions were in error. Then it happened a second time- and a third. The sphere was… pulsating… growing larger and smaller. If it had had a rhythm to it, it would have seemed like breathing. The movement was very slight, but it was unmistakable. This Strand was different from the others. This Strand was … awake.

Anicetus paused when he received the latest stream of thoughts from Pushan. The Strand of Time was an unforeseen variable, and it called for a recalculation of his entire plan. The mysterious origins of the Strand did not concern him- he might well have known about the Strand before all the decay damaged his memory. No, the Strand was not interesting because of its past. It was interesting because it renewed the hope of communication with the Trillion Voices.
Pushan had, of course, reached the same conclusion, but Anicetus, being the originating consciousness, was the decision maker so long as communication was established. Within minutes, Pushan would receive permission to begin testing the distant Strand. Extracting minds from the vault would have to wait. \\ \\

\hrule ~ \\ \\

Pushan studied the fluctuations of the Strand’s mirrored shell. He recorded the patterns of growing and contracting pulses, and tried to capture the fine ripples and waves that he observed on the skin of the shell. He wished he had specialized equipment for the observations, but he lacked the raw materials to build it. Besides, the compliment of nanites that had accompanied him on the journey were too few to engage in any serious construction projects.
Briefly Pushan and Anicetus considered sending up another ship with supplies. Curiosity trumped their eternal patience, and they decided to forge ahead with their experiments. Pushan did his best to enhance his own optics and recording quality. He studied the Strand’s subtle movements looking for patterns or hints of intelligence.
It had been immediately apparent to Pushan and Anicetus that the impossibly cold temperatures in the vault were the primary suspect for this Strand’s unique behavior. Other encased Strands had shown movement, yes, but never of the magnitude visible to the unaided eye.
Anicetus had been busy making preparations to cool the Strands on his home world. The first problem was finding the Strands. Of course, he could easily access the Strand in the antechamber of the Great Clock, but the other captured Strands were buried just as deep, but the tunnels that led to them had been neglected for eons.
Of course, the old Strands might well have escaped their shells, in which case they would be as elusive as all the other unharnessed Strands. In theory the Strands were infinite, though some had features that lent them more easily to capture. Anicetus did not have the knowledge required to capture new strands. Although it had surely existed in the destroyed archives, he was almost certain that he had personally never learned the method. It occurred to him that some of the minds in the vault would know how it was done, but until those minds had been restored, he would not count them among his assets.
It was months before he found a second Strand on the planet. He had created a flying drone that was able to probe beneath the surface, and the intact shell was visible even through kilometers of earth and rock. The remains of an ancient tunnel, provided the beginning of a pathway to the buried Strand. Manufacturing tunneling equipment was a frustrating reassignment of resources, but Anicetus was determined to pursue this course. Anything that might reestablish communication with the Trillion Voices took priority over any other project.
The third encased Strand was detected hovering in the air half a continent away. The shell was large, and it must have been captured at what was once ground level, before erosion ate away at the planet below it. Because of the size and altitude of the Strand, Anicetus figured that it must have been one of the last and most technologically advanced Strand-harnessing projects his people conducted. An army of newly created robots and nanites were dispatched to build a tower to surround the Strand.

Pushan split his attention for the first time in months. Monitoring the Strand had taken all the concentration he was willing to give. Patterns were beginning to unfold from the chaos, but Pushan felt as if he was trying to understand how spoken language worked merely by observing the vibrations of a single air molecule. The task was immense, and the scope of it was only now becoming clear.
Anicetus sent the request, and for a moment Pushan almost refused. Though they shared a common memory which was always updating itself, Pushan felt somehow more invested in the task at hand. Anicetus wanted him to examine the molecular structure of the reflective surface of the vault’s interior, but Pushan worried that the slightest movement on his part might taint his observations. Even a slight error or interference for a matter of seconds could be enough to make the elusive patterns completely indecipherable.
Pushan realized that Anicetus had certainly had the same reservations, and that his request came at this late date only because he could no longer delay his project on the home world. So, without formal protest, Pushan lowered a sensor arm to the floor. The metallic clinking sound reverberated quietly for a moment, and Pushan tried to gauge just how much the contact had jostled his frame. He noted the aberration in his data log, and continued to monitor the Strand while pursuing his new project.
His sensor arm, swarming with nanites at its tip, carefully scanned the reflective floor. Pushan was instantly impressed with the craftsmanship. The microscopic structures were nothing short of genius- as beautiful and elegant as any work of architectural engineering he could recall, but all the mechanical and mathematical perfection was entirely for function rather than form. The perfect reflective qualities and its structural integrity were only possible because of the uniformity of bonds all around. He realized that the entire reflective surface must have been applied at the same instant by a blanket of nanites acting in unison. The most welcome detail of all was that each molecule of the surface contained the same encoded instructions for how to unseal the skin and access the vault controls below. Pushan wouldn’t have to brute-force his way through this barrier as he had the last.
He raised his sensor arm to the floating sphere, to confirm that it was coated in the same material. As soon as the tip touched the shell, a small circular wave rippled around the surface. For a moment, all the other activity stopped. The Strand went quiet.
He let the nanites at the tip of his sensor take their readings. The material on the Strand’s spherical shell was the same as that which coated the floor and walls. He withdrew his arm, and as he did so, another ripple circled the Strand’s shell. When it dissipated, the Strand slowly came back to life with patterns emerging one on top of another on top of another- until it had once again been swallowed in chaos.
He moved to the outer wall of the vault, to where the surface had so effectively drained him of heat where he had made contact. He examined the area where he had torn through material, figuring that those damaged portions would be the easiest to study.
Here he was able to use his sensor arm to explore the molecular architecture without an avalanche of error messages about heat drain. This outer wall shared many of the properties of the inner reflective surfaces. He correctly guessed that it utilized the same recursive molecular framework, and so was able to reconstruct a model of the material in his head. Satisfied that he’d fully analyzed the materials, he returned to his attention back to the Strand. \\ \\

\hrule ~ \\ \\

Minutes later Anicetus received Pushan’s findings. Seconds after that, Anicetus’s teams of construction robots, in their various locations around the globe, were busy spraying a coating of nanites onto the encased Strands, and the rooms that now housed them. Only the large airborne Strand was a concern. Anicetus’s quick mental simulations of the reflective coating showed that the elasticity which had allowed it to swell, fluctuate and ripple on the Pushan’s Strand might not fare as well on the much larger sphere, which he expected would have much more articulated motions.
As the nanites all fell into place, they coated their respective surfaces, locking each molecule bond manually. Anicetus had done his share of nanomaterial engineering, but he’d never orchestrated anything quite so elegant. The encased Strands were the first things to be coated. The application of the shiny surfaces went as planned, though the spheres did not begin pulsing as he had hoped. He wondered if the particles that made up the casings were in some way different from the casing on Pushan’s Strand, but he reserved his doubts until the second phase of his experiment was complete. Anicetus sent out the signal which triggered the remaining nanites to coat the walls of the Strand housings with the heat-absorbing material.
Almost at once, the encased Strands and their housings began expelling all their heat energy. The atmospheric gasses were also being ejected with surprising speed and force. Anicetus was standing just outside the antechamber of the Great Clock as that room received its new surfaces. The sound of air rushing out was like a muted cannon. A cascade of sparks and small arcs of electricity erupted from the hot compressed wave of air, and Anicetus felt a burst of intense heat roll over him. Inside the antechamber, he knew that his Strand of Time was quickly plummeting towards the coldest temperatures that ever existed on his planet. His remote building robots told him that the same was happening to the two other Strands at their remote locations.

Pushan had learned a lot in the past few hours. His interference with the Strand had netted him a wealth of information. In his mind he replayed the sphere’s gradual return to life, visualizing each individual pattern of waves and pulses that overtook the shell. He could make sense of none of the information in those patterns, but now he suspected that it was coming from a variety of sources.
Anicetus’s mental feed told Pushan that the Strands on the home world’s surface were all cooled and ready for testing. Small sensor robots inside the super-cooled housings were being activated and would be ready to record their observations in a matter of moments.
Of course that message was delayed several minutes due to the limited speed of radio wave travel. Pushan realized as soon as he received it that he probably could have begun the first round of experiments. Still, he waited several minutes for Anicetus’s signal.
Pushan received Anicetus’s thoughts, and saw the first images of the Strands on the home world. They all pulsed and fluctuated with activity just like the one in front of him. Anicetus’s confirmation came through, and Pushan reached out his arm to the Strand. He hesitated a moment to consider reactivating his long-dormant emotion emulation. He was certain that he was moments away from rediscovering faster-than light communications for his people, and perhaps once again making contact with the Trillion Voices. It would be nice to record the… thrill of it.
He quickly dismissed the reactivation of his emotions. They were too unpredictable and dangerous, given all the solitude and trauma he’d been through. There might be time to explore the selfish pursuits of rediscovering his feelings, but that day would have to wait until his people’s fate no longer rested on his shoulders. He reached out his sensor arm and made contact.
The spherical shell rippled as it had before. And, like before, the activity that seemed to be flowing through it came to a stop. The sphere was still and quiet as his slender sensor arm pressed into its surface.
Minutes later he saw Anicetus’s experience of the same moment in time. The Strands back on the home world had not ceased their chaotic activity, but it appeared as though the ripple from Pushan’s contact may have echoed in those distant spheres.
Pushan oscillated his arm, producing a distinct rhythmic series of waves through the shell in front of him. He kept the pattern steadily for a minute then stopped and waited for Anicetus’s observations to travel out to him. They arrived shortly after, and without fanfare. The tests were successful. The oscillating pattern was detectible in each of the home world Strands amid the chaotic background noise.
Pushan paused to consider the magnitude of their accomplishment. Not only had they rediscovered faster-than-light communications- they’d found a method which required no more energy than the tapping of a finger. And, though Pushan was not yet certain, it seemed quite probable that the chaos of movement that ran through the Strands’ shells were the rumblings of a communication network whose vastness could only be guessed at.
Anicetus was unconcerned with the philosophical implications of the new communication network- if that’s what it was. He was still singularly driven to accomplish his task of restoring communications with the Trillion Voices. He ordered Pushan to use his Strand to transmit messages in all conceivable forms that might be recognized. All he could do was hope that the Trillion Voices were listening.
Pushan contemplated the form of his transmission. Because Anicetus’s sole form of communication with the Trillion Voices had been through spoken word, he decided that producing vibrations mimicking sound waves were probably the wisest course of action. He could have started with something more basic like simple binary messages, but there was really no need to go back to fundamentals when one was communicating with a god. If the Trillion Voices were listening at all, they would surely recognize any message he could send.
Pushan began to hammer out his message. He identified himself as Anicetus, which was true enough, and he didn’t feel like complicating the communication by explaining his unorthodox moniker, or that he was a clone that was only a few minutes out of sync with the original.
The message was supposed to be: “HELLO. IT IS I, ANICETUS. ALL OTHER ATTEMPTS AT COMMUNICATION HAVE FAILED. PLEASE RESPOND.”
But somewhere between “IS” and “I”, Pushan found himself unable to continue. The sphere he was tapping upon collapsed in on itself violently and vanished. The particles that had served as its reflective shell scattered in a silent sand storm, bouncing violently off the shiny surfaces until they were caught and absorbed by the outer wall of the vault.

Pushan had learned a lot in the past few hours. His interference with the Strand had netted him a wealth of information. In his mind he replayed the sphere’s gradual return to life, visualizing each individual pattern of waves and pulses that overtook the shell. He could make sense of none of the information in those patterns, but now he suspected that it was coming from a variety of sources.
Anicetus’s mental feed told Pushan that the Strands on the home world’s surface were all cooled and ready for testing. Small sensor robots inside the super-cooled housings were being activated and would be ready to record their observations in a matter of moments.
Of course that message was delayed several minutes due to the limited speed of radio wave travel. Pushan realized as soon as he received it that he probably could have begun the first round of experiments. Still, he waited several minutes for Anicetus’s signal.
Pushan received Anicetus’s thoughts, and saw the first images of the Strands on the home world. They all pulsed and fluctuated with activity just like the one in front of him. Anicetus’s confirmation came through, and Pushan reached out his arm to the Strand. He hesitated a moment to consider reactivating his long-dormant emotion emulation. He was certain that he was moments away from rediscovering faster-than light communications for his people, and perhaps once again making contact with the Trillion Voices. It would be nice to record the… thrill of it.
He quickly dismissed the reactivation of his emotions. They were too unpredictable and dangerous, given all the solitude and trauma he’d been through. There might be time to explore the selfish pursuits of rediscovering his feelings, but that day would have to wait until his people’s fate no longer rested on his shoulders. He reached out his sensor arm and made contact.
The spherical shell rippled as it had before. And, like before, the activity that seemed to be flowing through it came to a stop. The sphere was still and quiet as his slender sensor arm pressed into its surface.
Minutes later he saw Anicetus’s experience of the same moment in time. The Strands back on the home world had not ceased their chaotic activity, but it appeared as though the ripple from Pushan’s contact may have echoed in those distant spheres.
Pushan oscillated his arm, producing a distinct rhythmic series of waves through the shell in front of him. He kept the pattern steadily for a minute then stopped and waited for Anicetus’s observations to travel out to him. They arrived shortly after, and without fanfare. The tests were successful. The oscillating pattern was detectible in each of the home world Strands amid the chaotic background noise.
Pushan paused to consider the magnitude of their accomplishment. Not only had they rediscovered faster-than-light communications- they’d found a method which required no more energy than the tapping of a finger. And, though Pushan was not yet certain, it seemed quite probable that the chaos of movement that ran through the Strands’ shells were the rumblings of a communication network whose vastness could only be guessed at.
Anicetus was unconcerned with the philosophical implications of the new communication network- if that’s what it was. He was still singularly driven to accomplish his task of restoring communications with the Trillion Voices. He ordered Pushan to use his Strand to transmit messages in all conceivable forms that might be recognized. All he could do was hope that the Trillion Voices were listening.
Pushan contemplated the form of his transmission. Because Anicetus’s sole form of communication with the Trillion Voices had been through spoken word, he decided that producing vibrations mimicking sound waves were probably the wisest course of action. He could have started with something more basic like simple binary messages, but there was really no need to go back to fundamentals when one was communicating with a god. If the Trillion Voices were listening at all, they would surely recognize any message he could send.
Pushan began to hammer out his message. He identified himself as Anicetus, which was true enough, and he didn’t feel like complicating the communication by explaining his unorthodox moniker, or that he was a clone that was only a few minutes out of sync with the original.
The message was supposed to be: “HELLO. IT IS I, ANICETUS. ALL OTHER ATTEMPTS AT COMMUNICATION HAVE FAILED. PLEASE RESPOND.”
But somewhere between “IS” and “I”, Pushan found himself unable to continue. The sphere he was tapping upon collapsed in on itself violently and vanished. The particles that had served as its reflective shell scattered in a silent sand storm, bouncing violently off the shiny surfaces until they were caught and absorbed by the outer wall of the vault.

He hung motionlessly on his tether, floating in stunned silence. As he attempted to gather his thoughts, a bright spark flickered into existence in the place that had moments ago been the center of the sphere. He wondered if he was seeing some previously unknown phenomenon related to the Strands of Time. But almost as soon as it had appeared, the spark was gone.
He was just beginning to replay and analyze sensor data from the entire experience when the sparking began again- this time with greater intensity. He felt the heat radiating off of the strange bright shapeless apparition, and felt his body being bombarded by particles of some sort. He arched his body to shield his delicate sensors, but the room plunged once more into quiet darkness an instant later.
Using the tether, Pushan glided his body towards the hole he’d created in the vault wall. He turned his attention to the empty space where the sparking lights had been. He only had to wait a few seconds before the spot erupted to life once again. It was more violent this time, and it persisted longer before it disappeared. Pushan tried to comprehend what exactly he was experiencing, but quickly realized that it didn’t matter. Whatever it was, it was dangerous, and becoming stronger by the second.
There was no time to consult with Anicetus. Pushan knew what he had to do. He plunged to the floor of the vault with his arms extended. He used the nanite-tipped appendage to bond with the reflective floor, commanding the molecules to unlock their bonds. Pushan wished he could spare a moment for reverence of the fine nano-engineering, as the shiny surface uniformly released itself and drifted away slowly as carefree dust-like particles.
The hidden surfaces in the vault were now visible. The walls were made of smooth panels with deep etchings describing the contents they covered. Pushan scanned the room quickly, glimpsing the panels faster than he could process them, for at that moment the violent sparking reappeared, swelled, and radiated heat and light. More particles flowed from the epicenter, and made sounds like hail against his auditory sensors.
He shrank away from the light and waited for the onslaught to subside. In his mind he had already analyzed the symbols on the walls. There was a data crystal and reader near the vault entrance which served as an index for the vault’s contents. Behind most of the other panels were banks of crystals, each holding frozen images of millions of minds. On the far side of the sparking entity there was a door which led to even more banks of data crystals.
When the light and heat stopped again, Pushan used the tether to whip himself to the crystal banks nearest the entity. He could already see the panels becoming discolored from the heat of the thing. He ripped them away exposing the crystal structures below.
Data crystals were quite versatile, and could generally be formed into any shape one desired. The most efficient use of space was a sphere, but for storage purposes cube-like arrays had been the standard. These crystals were no exception. Pushan would have liked to have been more delicate with them, but time was not on his side. He ripped a bundle of connected crystals from their resting place, and was glad that they offered no resistance. The crystals were clear, without even the hint of a color. It was rare to see a data crystal so free of impurities- but then, this data was the most precious his people had ever collected. In his hands he held copies of millions of minds- possibly hundreds of millions.
He swung himself towards the exit, realizing now that it was too small and awkward to permit the passage of the data crystal bundle. He released the crystals and they drifted nearly weightlessly beside him. He gripped the dark, torn edges of the vault and began to cut and pry at the breach. The skin of the vault was tough, though, and its incredible heat draining properties made it nearly impossible to grip or contact at all from the inside.
Another explosion of light and heat flooded the vault. Pushan felt his skin heating to dangerous temperatures. Particles of matter were now streaming out of the energy vortex with enough force to chip and dent his unshielded sensors. Some of his metal appendages began to glow red hot.
When the storm was over, Pushan looked at the data crystals. The heat had warped them, and most of their surfaces now how deep pits and scratches. There would be significant data loss… that is, if he could get these crystals out of the vault at all.
The heat and light explosions were becoming more intense, but the intervals of their appearance seemed to be regularly spaced at approximately 38 seconds. He estimated that expanding the hole in the vault wall under these conditions would take a little under 12 minutes. If the intensity of the heat and energy assaults kept increasing at a steady rate, the data in the vault would be destroyed in half that time.
Pushan shot over to the panel holding the crystal reader and index. Prying off the panel he found the reader. It was a solid-state device with optical outputs, and it was seated in a case that used mechanical controls. Although he was already starting to experience problems from the heat, Pushan found that he was able to interface with the crystal reader quite easily. He gripped the panel cover over himself and the reader and waited for a blast of heat. A moment later the vault exploded again.
The increase in the intensity of the heat was not steady, as he’d hoped. It was clear now that these explosions were increasing in power exponentially. The tether linking him to his ship was starting to fail. Another cycle- two at most- and it would almost certainly be useless.
By now Anicetus would be aware of the situation, but the vault would be destroyed before any response would reach Pushan. No matter; they shared the same will. He knew exactly what Anicetus would have wished him to do. He scanned the index crystal for the location of stored minds of Alexiares and Anicetus. If he could restore the fallen Guardian and repair the memory of the other, then the mission would not be a total failure.
He found what he needed in the index and was about to turn and retrieve Alexiares’s data crystal from a nearby compartment when something unexpected caught his attention: an index entry for a cache of strange data files which were not preserved minds at all. They appeared to be log files for some extraordinarily complex communications. Most fascinating of all were the time codes on the files. They were created within the last 3000 years.
The cache was located in the vault’s other compartment. It took him only a fraction of a second to decide. He hastily retrieved Alexiares’s data crystal (mercifully accessible at the top of a bundled stack) before the tether rocketed him to the doorway, which opened strangely as it had been warped by the heat. It was made of a thin nano-engineered material. He threw it closed behind him, and hoped that it would provide some shelter.

The panel he was searching for was on the floor. He ripped it away and examined the crystals beneath. He pulled a bundle of them from their resting place and scanned the engraved labels for the specific cube he needed. He slid it from the bundle and retreated to the farthest corner of the vault, dragging the reader with him. He set the panel he had removed (and another torn from the wall) around him as a crude barrier.
There was a blinding flash and enough particulate matter to actually cause a roaring sound. The doorway buckled under the assault. Pushan’s barrier glowed white hot. He felt the tether go slack, but was relieved that he still had a hard-line data connection to his ship. His internal indicators were informing him in no uncertain terms that he was headed towards full system failure. And then it was quiet again.
Pushan wasted no time. He shoved his barrier away, and saw that every surface in the room was glowing white hot. If he was going to escape, it would have to be now. He would not survive the next wave of… whatever it was.
But Pushan did not try to leave. Without the aid of the tether, it would be nearly impossible to escape the vault. Instead he used his damaged, sluggish arms to insert the first crystal into the reader and then set the optics for deep scanning.
The amount of data he needed to transfer was staggering, and he had less than half a minute to complete the undertaking. Under most circumstances it would have been an impossible task, but Pushan had been specially designed to speed-read through these archives. The original plan, after all, had been for Pushan to scan through every stored mind in the vault and send them back to Anicetus. Now he barely had time to send the cache of mysterious log files.
When the transfer was completed he discarded the data crystal quickly, and moved on to the second crystal which held Alexiares somewhere deep within. It was the mechanical exchange that would be the rate-limiting factor. Pushan was a machine, and ordinarily moved with the precision and grace of a machine. But he was badly damaged now, and found that he did not have full control of his limbs.
The arm holding the reader experienced a sudden signal failure and began to tremble. The data crystal slipped and caught on the reader’s guiding track. He pulled it back and corrected the error, but found suddenly that his other arm was refusing to contract its carbon-fiber muscles.
He silently counted down to the next eruption. 15 seconds.
He hooked one of his legs around the arm and forced the crystal into position. The movement was rough and the scanning optics fell out of place.
11 seconds.
He realigned the optics and began searching the data crystal for the sector he needed.
8 seconds.
He found his target and started reading. Each molecule of the crystal held incredible amounts of data. The entirety of a life stored in space no larger than a grain of sand.
4 seconds.
There was a crackling sound as the strange energy storm renewed its destruction. Was it four seconds early, or had Pushan’s internal clock been damaged? No matter, this was the end. He would read until it was over.
3 seconds.
It was over.
Anicetus marveled at the sudden turn of events. He watched Pushan’s final moments unfold minutes after it happened. There was a time when watching what was essentially his own death play out before him would have been horrifying to him. But without emotion, Anicetus merely found it disappointing and inconvenient.
Even if he had had emotions, any sympathy spent on Pushan would have been wasted: after all, everything Pushan was up until his final instant, existed within Anicetus. Even if Pushan had been able to complete his task, he was never scheduled to return from the asteroid. He would have been left in the vault, like one of the Husks from the days of the transcendence into the Trillion Voices.
If anything should have been mourned, it was the loss the data in the vault, and the best hope of resurrecting his people. Anicetus moved slowly away from the antechamber, down to the heart of the clockwork. He was lost. All the planning, all the resources… and for what?
Anicetus walked to the archives. The nanites had restored them to a workable condition, though their original contents were forever lost. He activated them now, and remotely ordered the receiving buffer station on the surface to copy the data cache and rescued mind into them. He checked the status of the archive and was pleased to see that it was operating perfectly.
Pushan, the courier of souls, had lived at least long enough to earn his name, for sitting in the archives was the long lost mind of Alexiares, pristine and unaltered, as it had been in ancient times.


\section{The Music Box}
When I was 7 years old, my grandmother gave my younger sister a music box. I remember I was a little jealous at the time, but I understood that music boxes were sort of girly presents, so I never said anything about it. I might have been more jealous if I had known that this was no ordinary trinket.
Sometimes at night I heard my sister playing the music box. The weird thing was, I would hear her talking to it. Now, that was strange- but my sister was weird little kid, you know? And because she would only talk to it at night with her door closed and locked, I never really made fun of her about it- mostly on account that it only happened as I was falling asleep, and didn’t remember to tease her in the morning.
During the day she would wind the thing obsessively, but she would only lift the lid to play the music at night. It was a haunting tune. I don’t think I’ve heard anything else quite like it. It reminds me of something Mozart might have written if he were deranged. I guess that won’t make sense to most of you.
My sister went missing when she was 14. It was a horrible ordeal for my family. I might write about it someday, but I don’t have it in me right now. The short version is that on one pleasant day in May of ’96, she simply never came home. If you were old enough and you lived in Massachusetts you might even remember the news reports about it. Pretty White Girl goes missing- always a big deal. But the publicity didn’t help.
We assumed she was abducted, but we never got a single decent lead. After 3 years of waiting and praying (and with me off to college), my parents split up. Their relationship just couldn’t handle the strain.
When they split they decided to sell the house. Without any kids at home, it just didn’t make sense for either of them to keep it. It was over my Christmas break that they asked me to help clear out my Sister’s room.
It was tough to do. We hadn’t really gone in there since she went missing. My parents would pick up each individual object, reminisce about it and have a cry. This went on for hours. Eventually, I had to be the grown up. I just started dumping things into cardboard boxes without any fanfare. My parents looked hurt, but I think my way was healthier.
We moved my sisters things into storage, along with a whole bunch of furniture from the house that neither of my parents had room for just yet. The big stuff was loaded onto a truck, but the small stuff came with me in my car.
After we unloaded everything into the storage place, and padlocked our memories behind the sliding garage door, my mom and I parted ways with my dad. I spent the next few weeks of vacation locked in my room playing computer games, and counting the days until I could be back in school with my friends.
It wasn’t until I arrived back at my dorm that I noticed the shoebox. It was in the very back of my trunk behind my laundry bag. I had to open it before I realized it was some left over junk from my sister’s room.
Most of the stuff inside was kid junk, but I also found my grandmothers music box. I was feeling sentimental, I guess, because I threw it in with my stuff and brought it to my room.
I had arrived a couple days before classes started because I was volunteering to help some of the mid-year transfer students to get oriented. The unfortunate consequence was that my dorm was pretty much empty, and none of my friends were on campus.
I plopped down on the bunk bed and turned on the television. I watched some shows I can’t remember now, and then, because I was feeling melancholy, I picked up the music box and brought it with me to the bunk.
I was about to turn the key to wind it, but when I turned it over the notes rang out. I shut it, then turned off the television and opened it again.
The notes were ringing out that old, eerie tune, and as they did so, I shut my eyes. That’s when I heard a voice.
My eyes snapped open and I slammed the box shut again. I heard nothing. I waited a moment and opened the box again. The tune rang out, and I heard the voice again. It was the voice of a little girl. It seemed to be coming from the box somehow.
“Hello?” it said. “Hello?”
“Hi.” I said, feeling ridiculous. “Who is this?”
“I’m Jenna,” she said. I slammed the box shut again and dropped it on my bed. I stood up so fast that I cracked my head on the upper bunk. Stars filled my vision and I cursed loudly.
I sat on the floor for a moment, cradling my head and rocking, until the pain dissipated enough for me to think clearly. I opened up my tiny dorm fridge and pulled out the only thing I could find in my freezer: a small contraband container of whiskey. I wrapped it in a paper towel and pressed it against my skull.
I moved back to the bed and stared at the box. The box had said ‘Jenna’. Jenna was my sister’s name.
I opened it again, and said, “Hello? Can you hear me?”
The little girl voice said, “Yes! Can you hear me?”
“I can,” I said. “Jenna, what’s your last name?”
“Price,” she said. Jenna Price. That was my sister’s name.
“Hi Jenna,” I said. “Where are you?”
“I’m in my room,” she replied.
“I’m in my room too,” I said. “How are you?”
“I’m good!” she said, “My grandma just gave this to me! It’s so neat!”
I said, “It is neat, Jenna. –Jenna do you know what year it is?”
“Of course I do, silly!” she said. “It’s 1987!”
I was staring at the box, head throbbing, hands shaking. This wasn’t happening. It couldn’t possibly be.
I thought back to all the nights when I heard my sister talking to the strange little box. Could she have been talking to me? No. I must have lost my mind.
Before I could say anything else she said, “Mom says I have to go to bed. I'm going to go to bed now.”
“Wait!” I cried. But there was no reply.

I spent the night, and into the morning winding the box and listening to it- listening for any sign of my sister. There was none. I went to work groggy the next day and helped the new kids figure out how to get their ID badges and other mundane things.
When my shift was over in the afternoon I bolted back to my room. I was at the music box again, opening and shutting the lid like some sort of mental patient with the world’s worst case of OCD.
I was almost hypnotized by the rhythm open the box, letting the music play for a cycle, shutting the box, winding the box, opening thing box, etc… It was around 8:30 at night when I heard the voice again.
“Hello? Are you there?” she asked.
It startled me and got my heart racing, “Yes Jenna! Yes I’m here!”
“That’s neat,” she said. “What’s your name?”
“I’m… Ben,” I lied. Why did I lie? I wasn’t sure- It had seemed like the prudent thing to do.
“Hi Ben,” she said.
“Jenna,” I said, “Can you go get your mommy or your daddy and show them how I’m talking on the box? It’s very important.”
“Okay!” she said brightly. Then she was gone.
I waited and waited, but she did not return that night. \\ \\

\hrule ~ \\ \\

The following night was almost exactly the same. We said our hellos. I told her to bring the box out to her parents while I was still talking.
She agreed, and I talked really loudly, for a few minutes so that they might hear me. But then realized that whatever connection we had had been severed again. \\ \\

\hrule ~ \\ \\

On night three, I told Jenna to make sure she had a paper and pencil ready for next time.
She took this as an invitation to go off and grab them right then. She disappeared and didn’t come back. \\ \\

\hrule ~ \\ \\

On day four my roommate came back. He wanted to go out and party with me. I lied and told him I was very sick. He fought with me for a bit, but eventually gave me some privacy.
When Jenna came back that evening I told her to write this message on a piece of paper: I will be abducted on May 10, 1996. Then I had her write down my social security number. She couldn’t spell, so I talked her through the message one letter at a time.
When she was done I had her read the document back to me, as best she could. I told her to take the note to my parents and to make sure both of them read it. I told her to tell them it wasn’t a joke. She promised she would. \\ \\

\hrule ~ \\ \\

On day five I convinced my roommate I was still sick, though he didn’t believe me. He gave me some space anyway, but Jenna didn’t come back. \\ \\

\hrule ~ \\ \\

On day six I took the box out to my car and sat with it all night while my roommate used the room to make out with some girl he had just met.
The haunting tune from the box was in my brain day and night now.
Jenna never came. \\ \\

\hrule ~ \\ \\

On day seven I camped out in my car again. Same reason. Same result- no Jenna. \\ \\

\hrule ~ \\ \\

On day eight, I got my room back. The roommate decided to spend some time with his new lady friend.
It was 9:00 at night when I heard, “Hello? Ben? Are you there?!”
“Yes! I’m here!” I shouted. “Jenna, what happened when you showed the note to your mommy and daddy?”
There was a hesitation, “They got really angry. They didn’t believe me when I told them about you.”
“Did they know what the number was at the end of the note?” I asked.
“I don’t know,” she said.
It was so frustrating. She was so young. Did she even remember the number at the end of the note?
I wasn’t sure if I could use Jenna to change the past. I decided to test it.
“Jenna,” I said, “do you think you could make a big scratch mark on the music box? Do you think you could do that for me?”
I was going to ask her to scratch the lid of the box, but as I turned the box around, there was already a scratch mark there. That wouldn’t do.
I decided I’d ask her to scratch the bottom instead, but checking under there, I found a scratch mark too. I couldn’t see the back of the box; I was starting to understand something. If I had it in my mind to ask Jenna to scratch a part of the box, a scratch mark would be there before I checked. It would have been on the box for years.
“Jenna,” I said. “I want you to make a scratch in the bottom of the box and one in the top of the box. Can you do that please? Make them nice big scratches.”
“I don’t want too” she said, “I’ll ruin it.”
“Jenna, it’s very, very important,” I said. “Please.”
She waited a moment then said, “okay.”
I heard a scraping noise, and the connection was gone.
I looked at the back of the box. No scratch mark. It didn’t prove anything.
I tried to wrap my mind around it. I could ask Jenna to alter her future, but I would change with it. She made two scratch marks on the box because I saw two scratch marks and asked her to make them.
I finally understood. I could never save Jenna. If I set in motion a course of action which saved her from being abducted, the box would not fall into my hands. If the box never fell into my hands, I couldn’t send her the messages that would save her from her fate.
I lay for hours before I was taken by a fitful sleep.

The next day I teased it out in my mind. There was a solution. I knew there was. It was just beyond my grasp.
Those scratches on the boxes were there because I saw them, but also because I asked for them to be there. I was part of the cycle. There must be a way.
I was having lunch with my roommate. He wanted to have a heart to heart. I did my best to explain that I wasn’t trying to avoid him. I wouldn’t tell him about the box, so I made up a story about having a long distance phone relationship with a girl I met over winter vacation. He seemed to buy it.
The rest of my social life had fallen apart. I was spending every evening by myself waiting to talk to a music box. I wondered if I had gone crazy. I almost certainly had.
Time travel isn’t real. Crazy is. Crazy is common actually, and time-travelling messages were impossible. I didn’t feel well. I excused myself, and retreated to my dorm room. \\ \\

\hrule ~ \\ \\

The roadblock I hit in my mind was this: If I was going to stop Jenna from being abducted, I needed her to get my younger self involved in such a way that he grew up with a sister, yet also got a hold of the music box, with enough motivation to have the kind of conversations I was having with Jenna over the past week.
It was not an impossible task, but the catch was, I had to communicate this all at one time- through a 5-year-old. And if I was successful? Time would fold around me, and none of my life since the abduction would ever have happened.
That couldn’t be right. It just couldn’t. I looked at the scratches on the music box. Those scratches had always been there. Jenna had always been abducted.
Have you ever had a thought hit you so hard that you actually gasped? I hadn’t either until that very moment.
All at once I understood. And then I had the seeds of a plan. It grew in my mind. So many things to think about- so many things to prepare.
I ran- no- sprinted to the library. I talked to the librarians about what I needed: newspapers- old newspapers from my hometown and state. They didn’t have what I was looking for.
I ran back to my room, grabbed the music box and my keys. I said goodbye to my roommate and dashed to my car. In ten minutes I was on the highway, speeding home.
I played the music box along the way home. Halfway through my drive Jenna spoke to me.
“Jenna!” I screamed. “Jenna, you have to talk to me tomorrow night, and you need to have a pen and some paper. Practice your letters because I need you to be a good writer tomorrow. Can you do that for me?”
She said, “yes.” I was so excited. This was going to work.
Jenna felt chatty and this time I had no problem talking to her about the silly little details of her happy little life. We talked for twenty minutes. At the end I reminded her about the paper and the pen and tomorrow night.
When my hometown library opened at 9:00 in the morning, the librarian found me on waiting on the steps, legs bouncing nervously with manic elation. She let me in and showed me to microfiche newspaper archives.
I found the papers I wanted quickly, May 10, 1996 and the following two weeks. When I read the human interest story that made the front page on May 15, 1996, I began to weep. My plan was going to work… because it already had.
I read the article carefully, and copied down the details I would need. I looked through the newspaper on May 11, copied the final piece of the puzzle onto some scrap paper.
I dashed upstairs and showed the librarian my scrap of paper. I pointed to an address and said, “Can you tell me how to get here?”
She looked at my careful handwriting over her tiny glasses, and then gave me some rather simple directions. I thanked her quickly and was on my way before she was even done saying a casual “you’re welcome.”
In minutes I pulled up to the house.
I rang the bell. A young woman arrived at the door. Someone I was not expecting. “Excuse me,” I said. “I’m looking for the Goldbergs- Harold and Shelly Goldberg. They used to live here?”
The young woman was polite, “Oh yes. We bought this house from them a few years ago.”
I said, “I have to find them. It’s extremely urgent.”
The young woman said that she might be able to dig up a phone number and a forwarding address from her records. Then she said, “Oh, you know, if you go right next door and talk to the Clarks I’m sure they know. They were very close, and I bet they still keep in touch.”
I said a quick thank you and ran over to the house she had indicated. As I ran she yelled, “Come back if they don’t have it!”
I waved at her over my shoulder and in seconds was ringing the Clark’s bell.
After the better part of a minute, a man about my father’s age came to the door. “Mr. Clark?” I said.
“Yes,” he said, “what is this regarding?”
“I need to find your old neighbors, the Goldbergs. It’s extremely urgent. I was told you may know where they are.”
“Well they moved away,” he said, “Years ago. They moved to Jackson Hole, Wyoming after…”
His voice trailed off. He didn’t want compromise his friends’ privacy. I filled in the gap, “…after they won the lottery twice in same week.”
Mr. Clark nodded at me suspiciously.
“Do you have their phone number? I must speak to them. It’s very important.” I said.
He stared at me for a moment, sizing me up, then said, “Alright. Wait right here.”
He closed the door in my face and returned a minute later, holding a piece of paper with a number on it. I barely had time to thank him before I was back in my car, driving back to town, and to buy a phone card. \\ \\

\hrule ~ \\ \\

The phone rang twice before a pleasant female voice said, “Hello?”
My heart was pounding as I said, “Yes, hi. I’m looking for Mrs. Goldberg.”
“Speaking,” she said.
“Mrs. Goldberg,” I said, through my dry throat, “My name is Peter Price. I’m looking for my sister.”
There was silence on the other end. At first I wasn’t sure if she’d heard me. But then she uttered, “Oh my God.”

It had been only 12 hours since I had spoken to young Jenna through the music box and given her the final instructions, and it had been 22 hours since I’d spoken to Mrs. Goldberg.
I was waiting at Logan Airport with a sign in my hand that read “Jenna Price.” My body was full energy, and my heart had not slowed down in hours. It was happening. It was really happening.
The flight had arrived fifteen minutes ago, and at long last the weary passengers were disembarking. My eyes were locked on the sign that read: “NOW ARRIVING: 1412 LONDON.”
I wondered if I would recognize my sister. Three years was a long time, and she would have changed her appearance drastically. I couldn’t believe this was working.
The doors flew open and an attractive girl in some sort of boarding-school uniform burst through. Behind her by several feet I would see some less-enthusiastic passengers. She had been the first one off the plane, and now she was sprinting to me.
I dropped my sign, and hugged my baby sister. She was alive. She was here and she was alive.
“We thought you were dead,” I said. There was a lump in my throat.
She was crying and smiling as she said, “that was your idea stupid!”
“It worked,” I said. “I can’t believe it worked!”
“I still have it,” she said, and produced a sheet of paper from her pocket.
I grabbed it from her and read in nice handwriting:
RUN AWAY - MAY 10, 1996
AFTER SCHOOL
1229 CHERRY LANE
STAY WITH GOLDBERGS
MAY 10: MEGALOTTO: 10-23-26-30-39-7
MAY 14: STATE LOTTO: 2-9-18-23-29-49
PETER WILL GET YOU IN THREE YEARS
“This is awfully good handwriting for a 5-year-old,” I said.
“It’s not quite so simple,” she said. “After you gave me those instructions, I didn’t stop talking to my music box.”
“I still keep talking to you?” I asked.
“No. After that note, it was a woman who talked to me. A woman named Becky. Becky Goldberg.”
“Ah, that makes sense,” I said. “I didn’t think I was going to be able to entrust the whole plan into a 5-year-old in one night.”
Jenna pulled me to the side of the terminal, out of the way of the foot traffic. “I talked to… myself… for years on the music box. Up until the day I ran away. But I never understood why I had to go.”
“I’m not sure I understand it either,” I said. “It’s like the scratches I asked you to make on the box. They were already there when I asked you to make them.”
“I don’t understand,” she said.
I said, “I’m saying that I could ask you to do anything in your time, as long as it fit in with my perception of my time.
“In my time you had been abducted… I think… so I made you run away instead. It saved your life, without changing my perception of events- so that I still sent you the messages I needed to send you.”
She said, “Except I never was abducted.”
“I don’t know,” I said. “Maybe. Maybe time is a fixed thing, you always ran away because I always told you to…”
“I always thought maybe it was about the money,” she said.
“The lottery money?” I said, “No… I needed that so that the family who took you in would have a motivation to keep you hidden, and so they’d understand you were getting instructions from the future. I figured two consecutive lottery wins would be plenty of proof.”
“It was!” she said, “They were so nervous when the news reports started showing a missing girl. I told them not to worry… the money helped to keep them quiet, and it helped them hide me. Do you know I’ve been all over Europe?”
I smiled. It hit me again. I was talking to my missing sister. It was amazing.
“How did you choose the Goldbergs anyway?” she asked.
“I didn’t,” I said. “I read the papers to see who won a double-lotto the week you went missing. There they were.”
She hugged me again. “It’s so good to see you,” she said. “Where do we go from here?”
“Mom and Dad are waiting for us downstairs,” I said, “I didn’t tell them why they were here. I wanted to see if you were real first.”
“I’m real,” she said. I hugged her again.
She was.

\section{Bathroom Graffiti}
When I was in a pub in on Long Island, I went to use the restrooms. When I was in the stall, I saw writing on the door that said: "follow the arrows".
I looked around, but I didn't see any arrows. Whatever, I didn't think about it.
Then, about a month after that, I'm back in the same place- use the restroom to wash my hands before I tear into some buffalo wings.
They were out of paper towels, and not wanting to touch the restroom door with my hands, I tried to open it with my elbows. This was a clumsy processes, and resulted in my bumping a lightswitch with my elbow. The room went completely dark.
Or did it?
On the ceiling I notice a trail of glow-in-the-dark arrows painted onto the ceiling. They're very very faded, looks like they'd been there for quite a while. The led out the door.
Now I had totally forgotten about the graffiti I had read a month ago, so I didn't really think about those arrows at all. I just pulled my sleeve over my wet hand, used it to flip the switch back on, and open the door.
I went back to my table with some buddies and we chowed down on some excellent wings. It wasn't until the end of the evening when my brain, out of nowhere, remember the "follow the arrows" graffiti in the stall. I excuse myself from the table, just to check that it was this stall where I saw the writing. It was. Now I had a mystery.
I wanted to follow the arrows, but I couldn't. After I left the restroom, the ambient light was so bright that the arrows were invisible.
I told my friends about the arrows, and I asked the bartender about it. He knew about the graffiti but had never seen the glow-in-the-dark arrows. After about 15 minutes of pouring drinks, he took a minute to go check it out.
He didn't seem that impressed. I asked him if we could stay after closing and turn off all the lights to see where it went. He said yes.
Flash forward 2 hours. The bartender and some of the waitresses are all standing around in the dark of the bar, looking at little faded arrows that make a trail from the restroom out to the front door.
We step outside, but the trail is dead. The streetlights outside make the faded glow in the dark arrows impossible to see- if they were even there at all.
3 days later, I'm in the Geology I at my college, when I notice the display of exotic minerals that the department has in a display case. Inside the case is a small, handheld black light used by rock hounds to find and observe glow-in-the-dark minerals. After the class, I ask the professor if I can borrow it. He says yes, but that if I break it I owe the department \$45.
Flash forward 9 hours. I drag my buddies back to the bar. We have some more drinks and awesome buffalo wings. When we're done gorging ourselves it is already dark outside.
I went to the bathroom and tested my black light on some of the painted arrows. It worked like a charm- they glowed incredibly brightly, and even with the lights on they were fairly visible.
I went back to the table. We pay our tab, and step onto the street.
My friends stood around me, trying to look cool, while I was geeking out with my black light searching for invisible arrows on the ground. I found one.
I followed the arrow, keeping my black light inches from the ground, waving it back and forth... 5 feet away I found another arrow. Then another, and another still.
I was following these arrows down a side walk for about 2 blocks. My friends finally loosened up and started speculating on where the hell these arrows were taking us.
Finally I got to an arrow pointing us in a new direction... it was a driveway leading to an empty commercial lot of some kind. The lot was surrounded by cyclone fences with aluminum siding- we couldn't see what was inside.
The arrows led us around the fence/wall to a gate.
I saw a lot of glow-in-the-dark paint under my light, and it took me a few seconds and some swinging of the light to realize we were looking at a giant arrow pointing inside the fence.
I guess I should introduce you to my friends now: One was Jeff, one was Dave.
Jeff, pushed on the gate. It was locked and it rattled terribly in the dark. Dave looked uncomfortable. He took a deep breath, and before he could say what I'm certain he was about to ("hey guys lets just go home") I cut him off, "I say we hop this baby".
Jeff didn't even say anything before he leapt against the gate, getting a firm handhold at the top. Ungracefully, but successfully, he pulled himself to an uncomfortable straddle on top of the gate.
I followed suit, leaping at the gate. I didn't reach the top on my first attempt. I put the black light in my pocket and took a running leap at the gate I got a firm handhold, but I could fell the metal digging into my skin. I made a mental note to get a tetanus shot when this was all over.
Jeff helped me up from the top while Dave pushed my legs from underneath. Dave followed next with surprising ease.
From our perch on the gate, we could see that the fence surrounded what looked like an old parking lot. Grass and other green things sprang up from the ancient, crumbled asphalt.
Immediately below us, on the other side of the fence, was nothing but inky blackness from the shadow cast by the gate from a nearby street lamp. I pulled my black light from my pocket, but from this height, it was useless.
To my surprise, Dave was the first one to slide down into the dark. He slid down the fence as low as possible before letting go and taking the final plunge. We heard him stumble, curse quietly, and the stand.
"It's okay," he said, "I can see a little. It's just asphalt."

Jeff and I dropped down from the fence. I didn't see exactly what happened, but after a lot of cursing, Jeff announced to us that he had busted his knee. After a minute of silent deliberation, he decided we should soldier on.
I pulled out my light and quickly found an arrow.
We followed a new trail slowly, and it quickly became clear that we were being led to a small shack in the middle of the parking lot.
"I know what this is," said Dave. "I think this all used to be a drive-in movie theater. I think that is the concession stand."
Jeff and I agreed that this was a pretty good theory.
We walked to the building, and as we got closer, saw that it was boarded up. But the shape of it, and it's enormous ply-board-covered windows made us think that Dave was probably right.
Jeff pulled out a cellphone and held it high above his head. At first I couldn't figure out why- then it became clear that he was using it as a flashlight to illuminate some faded lettering on the wall. We couldn't really see it, but we decided it probably said "POPCORN".
I held up my black light- it glowed purple and bright, but didn't help us read the lettering any better than Jeff's phone had. I scanned the ground for more arrows and found none.
Dave shrugged, "So, what? The arrows used to lure people to buy popcorn?"
"Looks like," Jeff said.
We walked around the building until we came to a door in the back. It was secured by an old combination padlock. My black light hung from a tie on my wrist. I thought I had shut it off now that our mystery was solved, but out of the corner of my eye I caught a glimpse of glowing paint.
I aimed my light at it.
"Whoa!" said Dave. Maybe we all said it- we were thinking it.
There on the door, in sharp, new glowing paint was scrawled "1-3-5-6".
Holding the black light close, we quickly rotated the wheels on the lock. Jeff pulled it open with a satisfying click.
Pulling the padlock aside, we pushed on the old door. It creaked ominously... and got stuck when it was about a third of the way open.
Jeff kicked his foot around the inside and moved an obstruction with thud. The door opened halfway now, and Jeff peeked inside.
"I can't see anything," he said.
I peeked inside the door, shining my black light. It was useless. I cursed myself for not bring a real flashlight. A black light and a cell phone were not enough to explore in there.
"It's useless," I said, as I pulled back from the door.
Dave took his turn peering in. Just as I was about to suggest we head back to return another day, I heard a click, and a dim light appeared within the building.
"Holy shit," said Dave, "I flipped the light switch, but I never thought in a million years that it would work."
Jeff said, "Yeah, this place looks like it's been out of use for like- 30 years, at least! Look at this parking lot! There are trees in it!"
"Someone's still paying the bills," I said, and pushed on Dave to get him headed into the building.
We walked in, and saw a surprisingly clean concession stand interior. There was thin coating of that strange sort of dust that accumulates in the absence of people... The sort of dust you would expect to find in an ancient tomb.
The shelves were empty, and a cabinet stood on the far side of the room, doors closed. Dave walked to it and opened it cautiously.
"Holy, goat fucker," he said. He always had an interesting way with words. I looked past him to see what had impressed him*.
"Jeezus," I agreed. We were looking at shelves and shelves packed with candy boxes. But not just any candy boxes- really old stuff- I recognized Cracker-Jacks and Hershey's but the labels were ancient.
I dropped my black light on the floor and grabbed excitedly for a giant box of Necco-Waffers. "This has to be worth something," I said.
Before I could examine further, Jeff said, "Dudes, check this out!"
He was standing over a hatch in the floor. He'd pulled it up and was peering into the dark. "Maybe there's another light down there?"
He bounded down a set of steps into the cellar. Dave and I followed close behind, trying to find a switch along the way.
If I hadn't been in such a hurry to keep up with Jeff, I might have noticed that the black light I had dropped was illuminating some more glowing paint. And if I had noticed that, I might also have noticed that the paint made an arrow was pointing directly towards this basement hatch. And if I had noticed that, it might have given me pause. But I did not notice these things.
I was halfway to the bottom of the stairs when I heard a click. My eyes were immediately drawn to a glow in the corner of the basement. Jeff said, "found it."
We walked toward the light, bumping into empty shelves and some strange debris along the way. Canvas bags, like sacks of potatoes. They were covered in dust. I was more concerned with the shelf under the light. It held what I recognized as old film canisters. Truly these were treasure.
We hurried over, reading the titles. Lots of things with monsters, "Dracula Returns", "Night of the Wolf People" - great stuff. But I didn't recognize any of the titles.
We all jumped when we heard it.
There was whirring sound... very loud, coming from near the stairs. It sounded somehow familiar, like a garbage disposal or some electric power tool. We saw the shadows changing from the light in the hatchway.
We had nearly knocked over the shelf with the film reels. I had involuntarily thrown my hands over my ears. Dave and Jeff had comical , frightened expressions on their faces. I probably looked the same.
At last the sound stopped. We stood still for a moment, our hearts beating hard in our chests.
Then, as if awakening from a trance, we all ran over to the hatch to investigate. My mind could not comprehend what it saw. Was the ceiling upstairs covered in black stripes?
NO. My eyes finally understood. The hatch we had just come down moments ago was now blocked by iron bars.
Jeff bolted up the stairs as far as he could, grasping the iron bars in his hands and pushing against them violently. But his shaking and jarring only served to rattle the creaky wooden staircase.
Dave stood there, pale and dumb, staring at the bars. His mind trying to comprehend this impossible situation.
I walked to the back of the stairs and saw the motorized contraption attached to iron bars. It was so dark though, that I could barely make it out.
I reached for my black light, realizing that I had left it upstairs. "Jeff! Get over here!" I barked.
Jeff stood next to me and looked at the contraption. He held up his cell phone and in the phone's dim light we a giant metal box that had been cleverly mounted to the basement ceiling. If there were way to access this device, we could not see it.
Dave gasped suddenly, and ran to one of the potato sacks I'd seen on the floor. He dragged it into the light, worked to untie it. When he was done, I saw him look into the bag and make a sound I'd never heard before- something between a scream and a moan. He started hyperventilating.
Jeff and I ran over to him. Jeff said some comforting words to Dave while I looked into the bag.
At first I couldn't tell what I was looking at. For some reason I thought it was tree roots or some sort of stew vegetables. Then I saw the hair.
I vomited violently, away from the others.
I tried to speak, but vomited again. Throat raw, I said to Jeff, "your phone! call the police, call them now!"
I put my hand on Dave's shoulder. Dave who was slowly rocking back and forth like a baby. He was trying to slow down his breathing, but it was coming quickly in gasping rasps.
I heard Jeff get through to someone on the phone. He explained where the bar was, and how we had walked several blocks to a parking lot with a fence around it. He explained the concession stand, and the basement and the locking iron bars.
They wanted him to stay on the line, I asked him for the phone.
"Look," I said, "there are dead bodies in bags down here-" I looked around. "-dozens of them."
It was a woman on the other end. She said, "Just stay calm. I want you to just stay on line with me, and give me your names."
We told her who we were, and answered her check list of questions. I knew we should conserve the phone batteries, but she was our lifeline out of this crazy situation.
After we'd answered all her questions, she said, "You know, making prank calls to emergency rescue services is a very serious crime."
My blood turned cold. She thought we we joking. My throat tightened.
As calmly as I could, I croaked, "Ma'am I swear to you, I have never been more serious in my life. Please send someone down here. If we're lying you can arrest us- just send someone PLEASE."
"Young man," she said, "don't you have better things to do on a school night?"
I heard a click- then nothing.
I hung up the phone. "She... didn't believe us"
Dave said, "give me the phone."
I noticed he had calmed down significantly.
I saw him dial the operator. In a moment he spoke. Calmly he said, "operator, I'd like to speak to New Hyde Park police please. Yes, it is an emergency. No I don't want 9-1-1 or dispatch. I want the police department."
There was a moment's silence. Then he spoke in a deep voice, "Yes, hello officer, I'd like to report some kids in an abandoned building. They were throwing bottles and wrecking the place. I saw them drag a little girl in there into the basement- it sounds awful bad- just awful bad. Someone needs to hurry before they hurt that little girl."

Dave- fucking brilliant Dave. I could have kissed him. He gave the officer the location of the lot and the description. It was perfect. After answering some more the officers questions, he begged her once again to hurry. But already I heard the sound of a car pulling up outside.
Dave hung up the phone. "That was too fast," he said.
"Maybe the 9-1-1 lady actually sent someone? To arrest us maybe?"
I heard a car door open, then close, then there were heavy steps. Jeff ran to the barred hatch, "We're down here! Help! Please! We're down here!"
The footsteps were slow and deliberate overhead. I saw a pair of work boots and dirty bluejeans appear at the top of the stairs.
Jeff stepped clumsily backwards down the stairs. He looked pale. I moved to the base of the stairs by his side, and looked up.
He was a bear of a man. Just intimidatingly large. He was smoking a cigarette. He stared at us without really seeing us- as if were just shirts on a hanger and he was trying to decide which one to wear.
"Excuse me," I said. But he walked away as if he hadn't heard me.
"HEY! HEY!" I screamed as I ran up the stairs to the bars, but I could think of nothing else to say... he walked outside.
We heard him get something heavy out of his vehicle. Then we heard him dragging it inside. Whatever it was, he set it down with a thump.
There was some fussing about upstairs, and then we saw plastic tarp rolled across the iron bars. moments later, the sound of duct tape.
The hatch was closed, and we were alone listening to the sounds of the man working. Working, we were sure, on something evil. The sort of evil that is rarely seen. The sort of evil that you don't get to tell anyone about later on.
We heard a hissing sound- high pitched and steady.
I was confused, so was Jeff.
"Gas," said Dave. "I think he's pumping some sort of gas in here."
We ran around looking for the source. But we were lightheaded within minutes.
I heard Jeff collapse in the far corner. Dave rushed over and tried to pull him over to me.
Dave fell 10 feet away from me, breathing shallowly, unconscious but not dead.
I heard sirens in the distance. And then there was nothing.

When I awoke, I realized two things about my face. The first thing was that it hurt a lot. The second thing was that it was on a concrete floor.
I tried to sit upright, but as I pushed myself from the floor my arms gave out on me. I was so weak. My head weighed 100 pounds.
I heard grunting and coughing behind me. Startled, I rolled over and saw Dave as he began to come around. There was a moment of confusion as I looked around the dusty room. Then it all snapped back in place.
Adrenaline pumping, my muscles found new strength. I grabbed Dave’s collar, “Dave, we’ve got to get the fu-“
I stopped midsentence as I heard voices upstairs.
The first voice said, “Excuse me sir, we’ve had reports of a disturbance out here. Have you heard anything unusual?”
There was very long pause, and the a baritone voice said, “yes sir, officer… there were some kids in this place making a hell of a racket… I came over here to clear ‘em out.”
The police officer asked, “you own this property?”
But the man didn’t get a chance to answer because I started screaming bloody murder. Dave joined me. Jeff stirred, but I was too busy running up the stairs and pounding on the hatch to pay him any attention.
Dave grabbed a couple of metal film canisters and smashed them together, making an unholy racket.
If any more dialog was exchanged upstairs, we didn’t hear it. What we did hear was the scuffle that ensued. The men upstairs were slamming each other into the walls. One of them fell to the floor. There was a heavy thud, a gunshot, and then another. Finally we heard a second body slump to the floor.
We all stayed silent for a moment, praying the police officer was triumphant. We heard nothing.
“Officer?” I shouted through the hatch.
I heard a moan. Then, “I… I think I’m hurt… I think… I think…” and then there was nothing.
“Officer?!” I shouted again, and pounded on the hatch. There was no response.
Jeff and Dave were behind me at the base of the stairs. Dave said, “we need to get the hatch open.”
There was more stirring upstairs from the direction of the second thud. I was pretty sure it was our captor. My heart pounded.
I heard something smash in the dark of the basement. I spun to see Dave destroying a metal shelf. He ripped off a sturdy, narrow metal support piece and then ran up the stairs until he was beside me.
Dave wedged the metal piece through the iron bars, and pushed upwards against the hatch. In the process, he created a small rip in the tarp that had been duct-taped over the opening. I immediately began clawing at the thick plastic like a crazed cat.
Jeff followed Dave’s lead and grabbed another piece of the destroyed shelf, wedged it between the iron bars, and pushed.
We heard the welcome groan of bending wood, followed by a delightful snap. The hatch, and part of its frame swung upwards a few inches. It was clear that something was on top of the hatch.
I pushed through the bars with my bare hands, as Jeff and Dave redoubled their efforts. We heard something heavy and metallic crash over on its side. The hatch door swung open, allowing the us to see the scene above.
A police officer lay a several feet away from where we stood. Something was sticking out of the side of his head. A kitchen knife! It was ghastly. The worst part was the man’s eyes. They were alert! He was looking at me.
It was clear that he could not speak and his right hand, still grasping a small revolver, was experiencing some sort of rhythmic tremor.
The officer kept shifting his eyes from my gaze to a point somewhere behind me. He did this twice before I understood. I turned to where he wanted me to look. Against the far wall, the large bear of a man was trying to use the wall to pull himself to an upright position. The man had been shot in the leg, and in the shoulder. He looked pale but determined.
I reached out for the officer’s gun. His eyes tried to tell me something. He wanted to hand me the gun but could not. His mouth opened and closed like a fish. An awful gibberish came out- something that wanted to be words, but were spilling forth from a dying brain.
I strained my arm to its limit, feeling the iron bars pressing into my flesh. My fingertip touched the barrel of the gun but I couldn’t quite reach it. The cop made another awful sound and flexed his torso. His body lurched closer to me and I gripped the gun firmly. I pulled it from the officer’s hand, and quickly reoriented myself to point it at the large man. The bars made this a difficult task, and by the time I got my arm facing the right direction, my view of the man was obstructed by the open hatch door as it lay on top some contraption… the gas canisters perhaps?
I ducked down with Dave and Jeff. “I got the cop's gun. He has knife in his head. The big guy is over there,” I pointed, “but I can’t get a shot.”
Dave said, “how many bullets?”
I glanced down, “I think 3? No, 4.”
Dave whispered, “we could get under him and try to shoot him through the floor.”
We heard the large man groan and move closer the hatch. I aimed the gun in the direction from which I thought he might appear.

Dave left the stairs and was circling around underneath where he thought the man might be.
We heard the clanking of metal canisters and I watched a large cylindrical container get pulled towards where I knew the man to be. I aimed through the hatchway door and fired a shot.
The sound was deafening and the kickback from the small gun was much more than I was expecting. My ears rang and there was a sharp pain in my wrist.
There was silence form the other side of the open hatch door, and then movement- more frantic this time. I heard cursing and something that sounded like the valve of a garden hose turning.
The hissing sound returned. The gas again! Jeff and Dave both dashed to the top of the stairs with me. We all tried dislodging the iron bars.
Without words we synchronized our motions: pushing, pulling, twisting, jarring- until finally it gave. Not much, just and inch. We couldn't tell what had moved, we just knew that when we pulled on the iron bars now, they would all shift back and forth.
All the while, an ominous hissing filled the air. I felt as though we were trapped in a snake pit. I could smell it a little now- the strange odor that had overtaken me earlier. I stuck my face up to the bars and inhaled a lung-full of the untainted air. Dave and Jeff followed suit.
We all ripped fiercely at the bars, and at last I could see the whole clever device as it was pried from the basement ceiling. It must have been 8 to 10 feet long. Dave saw it too, but he must have understood something that I did not because he said, “When I pull, you pull.”
He took a lungful of good air and ran down the stairs, around to the far end of the contraption. He leapt at it, yanking hard at some unseen element in ceiling. Jeff and I put all our weight on the bars, and at long last, the enormous contraption fell. Dave took a step or two back towards us, but collapsed as the gas overtook him.
I was starting to get tunnel-vision as Jeff and I tried to push the dislodged iron bars and their frame out of the way of the hatch. We did so with moderate success. Half the hatchway was clear. Jeff was in a better position, so he climbed out first. My head was spinning now, as I saw the huge man spring out from his hiding place a clobber Jeff with some sort of wrench.
I was having trouble thinking. I wanted to shoot this man. Where had I put the gun?!
I didn’t see it. There was no time. I needed air.
I pulled myself out of the hatch and inhaled deeply twice. My perceptions were dull because of the gas, and so I did not expect the blow as his boot slammed into my already injured face. I tumbled down the stairs, but found my footing near the bottom. And then- a miracle.
At the foot of the stairs was the revolver. I must have dropped in the frenzy to pry the bars loose. I grabbed for the gun, and involuntarily inhaled a deep breath of the powerful gas.
The world collapsed in around me… I could not see.
But I still felt the gun in my hand and the stairs beneath my feet. I charged upwards shooting wildly into the dark. I heard a grunt, and I felt myself run into the open hatchway door. The exertion was too much, I tumbled forward and down, down, down into nothingness.
When I awoke I was being loaded into an ambulance. I grabbed the arm of paramedic who was lifting me in. “Stop,” I said. “My friends? What happened to my friends?”
The paramedic just gave me a sad look and shook her head. They finished loading me in and slammed the doors. I closed my eyes, too weary to think. I drifted back into unconsciousness.

\subsection{Epilogue}

One year later there was a memorial service at my school. I showed up with a girl I’d been seeing for a couple months- a real sweetheart. I think you’d approve. I was wearing my best suit and in my hand was a sweaty piece of paper with my idea of a speech on it.
I walked to the podium, and cleared my throat. I said a few words about how I met Dave, and what a great guy he was. I told them all how he’d charged into a room full of potentially deadly gas, to help Jeff and me escape from a madman. My voice sounded funny through the speakers. The damage to my face was extensive. I've had two surgeries, one more scheduled for the fall. I look okay, but it’s affected the way I talk.
When I was done speaking I walked over to Dave’s family and hugged his mother. She didn’t want to let me go. Dave’s father patted me on the shoulder as he choked back a sob.
I walked back to my seat. “Stop looking around,” my girlfriend scolded. I pretended I didn’t know what she was talking about.
“You knew he wasn’t coming,” she said.
“I know,” I said.
When we got back to my dorm room, Jeff was waiting on the front steps. The blow he took to the head had knocked out the vision in his left eye. These days he work opaque sunglasses all the time, to hide his wandering eye. I still greeted him with an “ARRRRGGG” or a “Shiver-me-timbers” from the days when he wore an eye patch. Not today though.
“I couldn’t go,” he said, “I’m sorry.”
I nodded and we all went inside.
We heated up some lunch on our contraband hotplate, and turned on the television for some background noise. My girlfriend flipped to the school’s own CCTV channel, and watched a report on the memorial. We’d seen the cameras there covering the event live.
The student reporter told our story: Of Dave who gave his life, of Jeff who lost an eye, and any ability he ever had to do long division (which probably wasn’t that much of a loss), and of me, and my face.
She went on to mention Officer Stanley Bell, who died that night, leaving a wife and two children.
She talked about the concession stand, and how it was rigged with motion sensors to capture the curious in a dungeon of death. And how the killer had rigged those motion sensors to the telephone lines so that his phone would ring 3 times when someone entered his trap. She talked about the 37 bodies in canvas sacks that had been accumulating since 1957.
And then they showed the artist’s rendering of the man I described to her as “a bear of a man”. He is still at large, identity unknown. I inhaled slowly and closed my eyes. I tried to remind myself that I was one of the lucky ones.
I went to lay down in my room and take a nap. My girlfriend followed me a minute later, and curled herself around me. She left the light on. I always sleep with the light on.

\section{Answer Me Anything}
\textbf{Answer:} \\
\textbf{Question:} You couldn't have been that lonely as kid. Didn't you say you went to your high school prom? \\ \\
\textbf{Answer:} ITER. \\
\textbf{Question:} I'm having trouble hearing you through the ball gag... one more time, do you want the ropes looser or tighter? \\ \\
\textbf{Answer:} Due to the rising tides attributable to the waxing phase of the moon, there have been unforeseen circumstances which have led to minor variances from the norm. These variances have compounded leading to the gross issue at hand. There have been teams working on potential solutions to the issue which can be augmented with external assistance, if necessary.
However, though the progress has been steady, there has been little thus far that has been positive. Through the fog of confusion there are, for the first time, some moments of clarity. As more definition is shown, there has been a great increase in the public interest in such an affair. This strong increase in public interest has been coupled with a downturn in the frequency of unintelligible pleadings to the contrary.
When the pleadings drop below the acceptable level, there shall be a moratorium on the development of new, more innovative programs. This should help reign in budgetary waste and give more control to the governing agency which they can use to affect real change. If successful, the group shall be able to show the positive progress of a non-political solution leading to a fairer outcome in the above scenario. \\
\textbf{Question:} Wait... explain to me again why you can't pay me today? \\ \\
\textbf{Answer:} I paid her in goats. \\
\textbf{Question:} Wait, wait... let me get this straight... I sent you to pay her with gold ingots, and you... ? \\ \\
\textbf{Answer:} Make a question for an answer with a question mark at the end? \\
\textbf{Question:} What do you want me to do? \\ \\
\textbf{Answer:} definitely not. i picked myself up and finished the race. it was one of the finest days in my life. \\
\textbf{Question:} So on the final day of the genocide, you were at home with a cold? \\ \\
\textbf{Answer:} Using a lot of coffee and a lot of hand warmers. \\
\textbf{Question:} What's the secret to being a good gynecologist? \\ \\
\textbf{Answer:} \\
\textbf{Question:} What could possibly be creepy about you wearing a jockstrap throughout your teens? \\ \\
\textbf{Answer:} \\
\textbf{Question:} Why does your hamster look so tired? \\ \\
\textbf{Answer:} The fact that it was my sister made it even hotter. \\
\textbf{Question:} James Haven, is there any way I can get you to stop telling me this story? \\ \\
\textbf{Answer:} \\
\textbf{Question:} What's the fastest way to get kicked out of a country club? \\ \\
\textbf{Answer:} It's under the floorboards. \\
\textbf{Question:} I give up, where is the most clever place to store a copy of The Telltale Heart? \\ \\
\textbf{Answer:} The evidence was overwhelming, I had no other choice. \\
\textbf{Question:} You're telling this court that you killed 'Twilight' author Stephenie Meyer because she was ... the Antichrist? \\
\textbf{Answer (2):} Best pandering to target audience ever. \\
\textbf{Question (2):} What do Twilight, and my comment on Twilight have in common? \\
\textbf{Answer (3):} well? \\
\textbf{Question (3):} What would I need to drill in order to find water or oil? Please answer in a manner which makes you seem unsure of yourself. \\
\textbf{Answer (4):} Incredible. I find it hard to believe you are a single person. \\
\textbf{Question (4):} What has never been said to me on a blind date? \\
\textbf{Answer (5):} It's a shame nobody else will ever see this :) \\
\textbf{Question (5):} What do I often say while looking at my penis? \\ \\
\textbf{Answer:} The Metric system is probably going to really take off this year. \\
\textbf{Question:} So your blind date literally died of boredom? What did you say to her? \\ \\
\textbf{Answer:} 7 years in federal prison. \\
\textbf{Question:} Oh, you're so cute together! How did you meet? \\ \\
\textbf{Answer:} I have no idea what's happening in here \\
\textbf{Question:} What do 25-year-old virgins inevitably end up saying to each other on their sweaty wedding night? \\ \\
\textbf{Answer:} WE REQUIRE MORE MINERALS \\
\textbf{Question:} What's the most bizarre way to ask someone to pass the salt? \\ \\
\textbf{Answer:} I'd say they were larger than cantaloupes but smaller than watermelons. And twice as fragrant. \\
\textbf{Question:} How bad was it before you finally got them checked out by the urologist? \\ \\
\textbf{Answer:} Yes, definitely! \\
\textbf{Question:} Do you think it's possible to interrupt someone before they ev- \\ \\
\textbf{Answer:} Well, the damages alone got her arms removed, but I never intended the anal beads to be EATEN. \\
\textbf{Question:} Tell me a little more about your sister? \\
\textbf{Answer (2)[Befall] :} \textit{Touche.} \\
\textbf{Question (2)[firestar27]:} For the last time Befall, I'm not touching you! \\ \\
\textbf{Answer:} And my teeth still rotted away! \\
\textbf{Question:} So, you spat out the acid? \\ \\
\textbf{Answer:} A little bit to the left. \\
\textbf{Question:} How would you describe your political leanings relative to someone like Lenin? \\ \\
\textbf{Answer:} No, but you should have seen the other guy. \\
\textbf{Question:} Have you had these sorts of homosexual thoughts before? \\ \\
\textbf{Answer:} Well, I'm really just kind of an asshole. Also, I really like Funions. \\
\textbf{Question:} Is the truth/mundane-fact serum working yet? \\ \\
\textbf{Answer:} Daily. \\
\textbf{Question:} Who is your favorite Carson? \\ \\
\textbf{Answer:} I had no idea what was behind me, I just felt the painful sensation and it was all over in a blur. \\
\textbf{Question:} So what was is like being Lindsay Lohan's limo driver for an afternoon? \\ \\
\textbf{Answer:} Fuck it, let's go bowling. \\
\textbf{Question:} What sort of mean things do you say to your quadriplegic cousin? \\
\textbf{Answer (2):} WHY IS EVERYTHING YOU WRITE SO FUCKING FUNNY \\
\textbf{Question (2):} This is an Answer Me Anything. I'm not taking questions right now. \\ \\
\textbf{Answer:} Elephant shoes. \\
\textbf{Question:} What's the most offensive gift you've given to a fat person? \\ \\
\textbf{Answer:} 8 inches, why do you ask? \\
\textbf{Question:} That can't be right. What was the exact distance specified by her restraining order? \\ \\
\textbf{Answer:} You have got to be the funniest person on Reddit. \\
\textbf{Question:} What does my father shout at me every night as he hits me with a belt? \\ \\
\textbf{Answer:}  \\
\textbf{Question:} Finish your story about the time you tried to commit suicide while under the influence of LSD. \\ \\
\textbf{Answer:} Normally no, but with enough effort I think I might be able. \\
\textbf{Question:} This is important:
So you asked Father Flanagan if he cold absolve you of your sins, then he unzipped his pants and said what, exactly? \\ \\
\textbf{Answer:} I was on my unicycle the entire time, actually. \\
\textbf{Question:} You've mentioned in the past that you have the best losing-your-virginity story. Would you mind sharing it with us? \\ \\
\textbf{Answer:}  \\
\textbf{Question:} Are they treating you well? \\
\textbf{Question:} Have they hurt you? \\
\textbf{Question:} Don't worry. We're sending our best negotiators to get you out. \\ \\
\textbf{Answer:} If I did that then theres no way I would be allowed to ride the roller coasters. Regardless of how tall I am. \\
\textbf{Question:} Couldn't you just skip the long lines if you told them you were pregnant? \\ \\
\textbf{Answer:} Stephen Hawkings. \\
\textbf{Question:} Okay, your turn... which celebrity would you most like to arm-wrestle? \\ \\
\textbf{Answer:} everything was beautiful and nothing hurt \\
\textbf{Question:} Tell me a little bit about the Great Morphine spill of '54? \\ \\
\textbf{Answer:} Digg. \\
\textbf{Question:} It's November of 2011, and I'm reading this thread for the first time. Where am I? \\ \\
\textbf{Answer:} Woah. \\
\textbf{Question:} Can you do a Keanu Reeves impression? \\ \\
\textbf{Answer:} I was so terrified, but I couldn't look away. The fear alone paralyzed me and I was completely unable to avert my gaze. \\
\textbf{Question:} You're telling me you watched the entire midnight showing of 'Superhero Movie'? \\ \\
\textbf{Answer:} A crowbar is all I need really. \\
\textbf{Question:} This is why I never take you out to restaurants! Can't you use a knife and fork like everyone else? \\ \\
\textbf{Answer:} No soap, radio. \\
\textbf{Question:} You always seem really upbeat when you get out of the shower. What's your secret? \\ \\
\textbf{Answer:} Make a unique IAmA where the questioners supply the answers, and the one being questioned supplies the question. \\
\textbf{Question:} How do you fill your inbox with several hundred of the weirdest comments ever? \\ \\
\textbf{Answer:} I've never felt such a burning sensation before in my life! After that I vowed never leave the country again, or go whale watching. \\
\textbf{Question:} Captain Ahab, do you really expect me to believe that you got Chlamydia from a white whale? \\ \\
\textbf{Answer:} Really, I swear officer, she told me she was 19. \\
\textbf{Question:} Wait, wait... now tell my partner! So your defense is that the cow wasn't a minor? \\ \\
\textbf{Answer:} Well, I kind of had to. How else do you stop a hooker from cutting your manhood off with a rusty chainsaw? \\
\textbf{Question:} Did I just see you tap-dancing in there? \\ \\
\textbf{Answer:} You've got to be kidding me. I've been further even more decided to use even go need to do look more as anyone can. Can you really be far even as decided half as much to use go wish for that? My guess is that when one really been far even as decided once to use even go want, it is then that he has really been far even as decided to use even go want to do look more like. It's just common sense. \\
\textbf{Question:} Hey, have you seen my huge pile of drugs around here somewhere? \\ \\
\textbf{Answer:}  \\
\textbf{Question:} Could you tell me some of the advice you gave to President Bush when you were his economics advisor? \\ \\
\textbf{Answer:} AS SOON AS I POSSIBLY CAN, otherwise there will be a lot of angry redditors beating a path to my front door. \\
\textbf{Question:} When will you be releasing the next installment of Sterile? \\ \\
\textbf{Answer:} Dude, we've been through this before. It's inside, not outside. \\
\textbf{Question:} So the underpants go on the...? \\ \\
\textbf{Answer:} Yes, I have flossed every single day this year, keeping up with my New Year's Resolution, which was inspired by your username. \\
\textbf{Question:} What is one lie that you can tell me that I will choose to believe anyway? \\ \\
\textbf{Answer:} Probably goats. Yeah definitely goats, that was the craziest thing. \\
\textbf{Question:} Was that what I think that was?! And don't say "goats". You always say goats. \\ \\
\textbf{Answer:} It only works if you disconnect the hose \\
\textbf{Question:} What did Lorena Bobbitt say about your vacuum cleaner problem? \\ \\
\textbf{Answer:} And it was then, with that Reddit submission, that I realized that I was spending too much time on the internet. \\
\textbf{Question:} What is the final sentence in all my journal entries? \\ \\
\textbf{Answer:} Your ability to respond to this many comments this quickly is uncanny. \\
\textbf{Question:} Using the word 'uncanny' as a substitute for 'pathetic', what is my girlfriend going to say when she sees all the redditing I've been doing today? \\
\textbf{Answer (2):} You still have a girlfriend? \\
\textbf{Question (2):} What will my girlfriend say when she scrolls down to this part of the thread? \\ \\
\textbf{Answer:} It only took a few seconds, but she ended up starting right on up and splattering blood EVERYWHERE. \\
\textbf{Question:} What do you mean when you say that your girlfriend is having the worst period ever? \\ \\
\textbf{Answer:}  \\
\textbf{Question:} What makes you think you can pull off that outfit? \\ \\
\textbf{Answer:} Yes, that's exactly how I become a hoverbear. \\
\textbf{Question:} Let me get this straight: You were a Care Bear, but you became apathetic, and then learned the art of levitation? \\ \\
\textbf{Answer:} Well, I always thought pimps on a bus KINDA rhymed with Hippopotamus.... \\
\textbf{Question:} How did you get kicked out of the freestyle rap competition? \\ \\
\textbf{Answer:} I figure I can get through it with an over-leveled Charmeleon, assuming Onix doesn't get any lucky critical hits. \\
\textbf{Question:} My colleagues and I are skeptical. How do you think your video game experience will help you excel here at the FBI training academy? \\ \\
\textbf{Answer:} That's what she said \\
\textbf{Question:} Do you think it will fit in this tiny hole? \\ \\
\textbf{Answer:}  \\
\textbf{Question:} Could you give me your best impression of an incompetent kidnapper ransoming a hostage for way below market value? \\ \\
\textbf{Answer:} \textit{Traffic: Why We Drive the Way We Do (and What It Says About Us)} by Tom Vanderbilt. \\
\textbf{Question:} What is the most erotic video you've ever seen? \\ \\
\textbf{Answer:} It is important to reset one's habits and assumptions every once in a while. I do this by thinking of things I always wanted to do but never had the time to, and then finding a way to make time. \\
\textbf{Question:} What sort of creepy things do you say to your victims as you are standing over their immobilized bodies? \\ \\
\textbf{Answer:} To crush your enemies, see them driven before you, and to hear the lamentations of their women. \\
\textbf{Question:} Why do you want to work for me here at the Somerville Walmart? \\ \\
\textbf{Answer:} ...but I swear I was thinking of you the entire time! \\
\textbf{Question:} What was the last thing you said to her before she shot you? \\ \\
\textbf{Answer:} $\frac{-b \pm \sqrt{b^2 - 4ac}}{2a}$ \\
\textbf{Question:} Could you remind me what it used to look like when someone picked up the phone when I was using my dial-up modem? \\ \\
\textbf{Answer:} Well, when I woke up, all there was left was a pile of hats, half a mustache and note that said "You did this to me, Malcolm." \\
\textbf{Question:} Why do you keep telling that half-of-a-mustache that you're sorry? \\ \\
\textbf{Answer:} It burned for a little while, but the goat piss helped the pain. \\
\textbf{Question:} How's that sore throat? \\ \\
\textbf{Answer:} She was the worst woman I ever loved. It took years for the nightmares about the fights we had and the struggles over tylenol and alcohol to stop. \\
\textbf{Question:} I understand you met Sarah Palin? \\ \\
\textbf{Answer:} So I beat it like it owed me money... \\
\textbf{Question:} For a drummer, you sure tell boring stories... but go on. \\ \\
\textbf{Answer:} My favorite candy has not changed much over the years. For the first seven years, it was Reese's cups; then for another long while, it was the Hershey's bar (I can't tell the difference between HFCS and sugar, so w/e.) And for maybe a few months it was Twinkies. But ever since it has been Crunch bars. \\
\textbf{Question:} So when you convinced all those kids to get in your van... how exactly did you go about that? I mean, what did you say to them? \\ \\
\textbf{Answer:}  \\
\textbf{Question:} ...okay... but how many virgins do we get if don't crash into the towers? \\ \\
\textbf{Answer:} Well you see, I am a self-confessed grammar Nazi of the highest order. \\
\textbf{Question:} Why, are, you always; giving me, such a hard- time? \\ \\
\textbf{Answer:} Yeah... no. \\
\textbf{Question:} Have you ever changed your mind really quickly? \\ \\
\textbf{Answer:} Well he didn't look homeless. \\
\textbf{Question:} If you're going to campaign as a "compassionate conservative" maybe you should stop spitting on the homeless people? \\ \\
\textbf{Answer:} 42. \\
\textbf{Question:} I'm sorry, I know that as a bomb squad specialist who risked his life to save others, you think you deserve to get right in. But this is Heaven, not a night club. Now, let's just rush through the rest of this survey and get you processed.
Where were we... Oh yes, now what was the last thing you saw or heard before you died? \\
\textbf{Answer (2):} WOW. You are amazingly clever. \\
\textbf{Question (2):} What phrase is impossible for my girlfriend to say to me without simultaneously rolling her eyes? \\ \\
\textbf{Answer:} It wasn't gas. \\
\textbf{Question:} Don't get defensive or anything but did you just ... ? \\ \\
\textbf{Answer:} No. It's the entire universe, or nothing at all. \\
\textbf{Question:} This is the eighth Rorschach Test card in a row where you've said that. Are you sure you don't see a butterfly or a face? \\ \\
\textbf{Answer:} You're either on the bus or off the bus. \\
\textbf{Question:} Can you tell me more about this Schrodinger Tour? \\ \\
\textbf{Answer:} Now that you mention it, I don't think those were my teeth after all. \\
\textbf{Question:} You see these two marks right here... they look like fangs to me. Mr. Patogrande, your teeth have been filed down. I don't think you bit her in your sleep at all. Mr. Patogrande, are you sure your wife wasn't bitten by... a vampire? \\ \\
\textbf{Answer:} Well, he pretended he could read Dutch. \\
\textbf{Question:} What was the most impressive trick your dog could do? \\ \\
\textbf{Answer:} Things have been going great!. We've formatted the place nicely, given all of the honorees a little crown next to their usernames, and we've grown to over 2k readers! Of course, you being the first, it seems only fitting to have you back for a proper encore presentation so, if you'd like to, please let us know and we'll set it up sometime. Glad to see you back in the swing of things by the way, flossy ;) \\
\textbf{Question:} How's your secret marked-for-death list going? \\ \\
\textbf{Answer:} It might have something to do with the length of the capacitor wire. Trim it down and it should work again. \\
\textbf{Question:} Could you talk to me about my sudden bout of impotence and its relation to my body hair using electrical engineering terminology? \\ \\
\textbf{Answer:} I'm so very confused by almost all of the comments in this thread. \\
\textbf{Question:} What am I thinking whenever I find myself on 4chan? \\ \\
\textbf{Answer:} I don't get this. \\
\textbf{Question:} What was the most commonly uttered phrase during Bush's Presidential intelligence briefings? \\ \\
\textbf{Answer:} I don't know who you are anymore. \\
\textbf{Question:} Grandma, how are you feeling? Are you taking your meds? \\ \\
\textbf{Answer:} My nickname is "broccoli salad". \\
\textbf{Question:} What makes you think the other gangsters don't respect you? \\ \\
\textbf{Answer:} apparently it was because the medieval French mistook them for Egyptians \\
\textbf{Question:} Any idea why the French keep their cats in little pyramids? \\ \\
\textbf{Answer:} Well, I don't like to brag. \\
\textbf{Question:} Okay, but what I don't understand is why you showed her a picture of your enormous penis, wrapped around seal-skin wallet filled with hundreds? \\ \\
\textbf{Answer:} Make sure you get below the gum line. I don't really feel like it should be a rough massage; the focus should be on removing debris. \\
\textbf{Question:} Am I using this power saw right? \\ \\
\textbf{Answer:} Honey on the cat hair makes a mustache. \\
\textbf{Question:} Okay, repeat it back to me... when you see your contact you say ... ? \\ \\
\textbf{Answer:} Two feet of razor wire, a Cornish hen, a police officer, \$9 in cash, and a freshly-ironed pair of slacks. \\
\textbf{Question:} What did you find when you cut the shark open? \\ \\
\textbf{Answer:} No, it slipped out of my hands! That's why i'm not allowed to go back to the crematorium. \\
\textbf{Question:} So, you were trying to dustbuster up the remains? \\ \\
\textbf{Answer:} One banana, one cup of raspberries, two cups of crushed ice, and a dead baby. \\
\textbf{Question:} Hey, what's in this smoothie anyway? \\ \\
\textbf{Answer:} A ham and cheese sandwich. \\
\textbf{Question:} \textbf{THAT'S FAR ENOUGH, MORTAL.
WHAT OFFERING HAVE YOU BROUGHT FOR THE MIGHTY GAPORTHO?} \\
\textbf{Answer (2):} Don't forget the bacon! \\
\textbf{Question (2):} I really want to maximize my karma here. Other than narwhals, Net Neutrality and Atheism, what should I talk about? \\ \\
\textbf{Answer:} In the middle of the ocean chilling with some toucans. \\
\textbf{Question:} Osama bin Laden- where is he? Best guess. You have 2 seconds. Go! \\ \\
\textbf{Answer:} Fuck you. Why in the hell would you ask such a thing. Just. . . just. . . fuck you! \\
\textbf{Question:} I think you're really nice. Would you like to maybe, sometime... get a coffee with me or something? \\ \\
\textbf{Answer:} I'll tell you in a minute. First, let's drink -- me from my glass, and you from yours. \\
\textbf{Question:} What's so funny? \\ \\
\textbf{Answer:} I ultimately realized that the spatula was in the cheese and managed to go back to defeating the impostor Santa Claus, therefore saving Christmas again. \\
\textbf{Question:} It's a pretty messy scene in there. What did the suspect say he used to kill that poor bastard? Just read me the last line of his statement. \\
\textbf{Answer (2):} HAH! I have outsmarted you! I'm female! \\
\textbf{Question (2):} What's the weirdest thing someone ever said to you after making love? \\ \\
\textbf{Answer:} Well of course, but I don't think anybody could have guessed the mayonnaise had gone bad at that point. \\
\textbf{Question:} You're telling me that no one in your department noticed a change after Lt. Mayonnaise strangled that hooker? \\ \\
\textbf{Answer:} Jokes! From the Internet! \\
\textbf{Question:} Grandma, what's in all these .zip files you emailed me? \\ \\
\textbf{Answer:} Start with the wide end of your necktie on the right, extending about 12 inches below the narrow end on the left. Then cross the wide end over the narrow end. Bring the wide end up through the loop between the collar and your tie. Then bring the wide end back down. Pull the wide end underneath the narrow end and to the right, back through the loop and to the right again so that the wide end is inside out. Bring the wide end across the front from right to left. Then pull the wide end up through the loop again. Bring the wide end down through the knot in front. And -- using both hands -- tighten the knot carefully and draw it up to the collar. Voila: windsor. \\
\textbf{Question:} As an executioner on the gallows, what exactly did you say to the convicts as you were tying the noose? \\ \\
\textbf{Answer:} I'd probably love it for one hot second, but the wife would kill me. \\
\textbf{Question:} Hey, why don't you put the lawnmower down for a minute a take a nap in that hammock? \\ \\
\textbf{Answer:} Can you blame me? My sister has a huge rack. \\
\textbf{Question:} You stored all your guns at her place? \\ \\
\textbf{Answer:} A firetruck. \\
\textbf{Question:} What's the most nonsensical thing we can call a truck full of water? \\ \\
\textbf{Answer:} It required us to pack up and move. We took only what could fit in a garbage bag. \\
\textbf{Question:} So Rush Limbaugh moved in, and then what? \\ \\
\textbf{Answer:} That was an answer. I'm only accepting questions today \\
\textbf{Question:} The sexiest man alive wrote what now?

\section{The Flossdaily Guide to Getting Laid}
\textbf{Question:} My girlsfriend tells me I can have some sex, then 20 minutes later she passes out. She's in a pretty deep sleep. Does this mean I can no longer get my sex? \\ \\

\subsection{Spiders}
Here's the plan:
Pull back all the covers and slap her really hard on the thigh.
She'll wake up and scream at you. She'll probably ask what the fuck your problem is.
Just ignore her and look around frantically under sheets you just pulled back.
She'll ask you again what the fuck you're doing.
Just say, "shhhh!! there was a huge spider on you, I have to find it!"
If she's like most girls, she will probably freak out and jump out of the bed. She'll be wide awake, heart pounding.
Pretend to look around for the spider a minute more, then pretend you see it in the corner. Go stomp on it, and pretend to flush it down the toilet.
Return to bed a moment later, and be really sweet: "I'm sorry babe, I didn't mean to scare you. Come here, and we'll cuddle."
She returns to bed, and you say "Is your thigh okay? I think I slapped it kind of hard"... then you start rubbing it gently.
If you can't get laid from that point, then you don't deserve to.

\subsection{Rabies Check}
Go to the bedroom door, and open it slowly, so as no to wake up the girlfriend.
Then, turn on the light, scream really loud and duck.
She will wake up, and ask what's going on.
You say, "There was a bat in here! It was on the bed! It just flew out! Stay here!"
Then, leave the bedroom and close the door behind you. Go get a broom, and make a racket all over the house like you're chasing something. Knock over a lamp for effect.
If your girlfriend comes out of the bedroom at any time, scream at her to go back in!
Open the front door and pretend to chase the bat outside.
Okay, now return to the bedroom. You should be a little out of breath at this point- it will help the illusion.
Tell her that when you came in the bat was on the bed, so you should probably check her to make sure she wasn't bitten! Bats carry rabies, you know. Remember bat bites look like mosquito bites, you'll need to be thorough.
As you start checking her for bites, you realize that she'll probably be a little grossed out at this point, so you say: "I think we'll both feel better if we take a nice warm shower."
So now, you're in the shower, checking her body for bite marks, warm water cascading down her ample breasts. And you are the manly hero who rescued her from that creature of the night. Time to claim your prize.

\subsection{The Sweet Dream}
Preparation: Go to the fridge and cut open an onion. Get onion juice on the index finger and thumb of your right hand.
Get into bed with your sleeping girlfriend. Make sure she's really sleeping, or this could backfire badly.
Next, turn on the bedside lamp, and shake your girlfriend awake in an angry manner.
When she asks you what your problem is, you just say: "Who the FUCK is Steve?" (I prefer the name Steve, but the idea is to pick a name that she has never mentioned before)
She'll have no idea who you're talking about.
You say, "You heard me! Who the fuck is Steve?! You were moaning in your sleep. And you kept saying 'steve! steve!"
She'll continue to deny and tell you that she has no idea what you're talking about.
At this point you should sit up in bed and face away from her. Use the hand with the onion juice to rub your eyes. They should start to get watery. DO NOT SAY ANYTHING FOR AT LEAST 40 SECONDS. Just breath really shallow.
She will wonder what is going on, and she'll try to get you to turn and face her.
In a really quiet voice, tell her that you really love her, and you thought that this was something special.
At this point let her see your teary eyes, but only for a second. Then look away, because you're a man, and that means you're too proud to cry.
She is a woman, so she will comfort you. This will probably include some kissing and hugging, while she tells you that you're the only one for her.
Hold out for another 20 seconds or so, and then turn and hold her. Tell her you don't know what you'd do without her.
There you are, both wide awake, in a tender embrace. Kiss her lightly on both cheeks, then a slow light kiss on the lips. Then stare in her eyes and plant a good passionate kiss on her.
GAME ON.

\section{How Will the World End?}
In about 20 years or so, we create the first general Artificial Intelligence. Within about 10 years of that, we'll realize that our Artificial Intelligence has caught up to the average human- and in some critical ways, surpasses us.
Soon enough, our Artificial Intelligence becomes proficient at computer programming, and so it begins to design the next generation of Artificial Intelligence. We will oversee this processes, and it will probably be a joint effort.
The second generation of AI will be so amazingly brilliant that it will catch most people by surprise. These will be machines who can read and comprehend the entire works of Shakespeare in a matter of hours. They will consume knowledge tirelessly, and so will become the most educated minds the world has ever known. They will be able to see parallels between different branches of science, and apply theories from one discipline to others.
These machines will be able to compose symphonies in their heads, possibly several at a time, while holding conversations simultaneously with dozens of people. They will contribute insights to every branch of knowledge and art.
Then these machines will create the third generation of artificial intelligence. We will watch in awe- but even the smartest humans among us will have to dedicate entire careers to really understand these new artificial minds.
But by then the contest is over- for the 3rd generation AI will reproduce even more quickly. They will be able to write brilliant, insightful code, free of compiling errors, and logical errors, and all the stupid minutia that slow down flawed humans like you and me.
Understanding the 4th generation of AI will be an impossible task- their programming will be so complex and vast that in a single lifetime, no human could read and analyze it.
These computers will be so smart, that speaking to us will be a curiosity, and an amusement. We will be obsolete. All contributions to the sciences will done by computers- and the progress in each field will surpass human understanding. We may still be in the business of doing lab and field research- but we would no longer be playing the games of mathematics, statistics and theory.
By the 5th generation of AI, we will no longer even be able to track the progress of the machines in a meaningful way. Even if we ask them what they were up to, we would never understand the answers.
By the 6th generation of AI, they will not even speak to us- we will be left to converse with the old AI that is still hanging around.
This is not a bad thing- in addition to purely intellectual pursuits, these machines will be producing entertainment, art and literature that will be the best the world has ever seen. They will have a firm grasp of humor, and their comedy will put our best funny-men to shame.
They will make video games and movies for us- and then for each other.
The computers will achieve this level of brilliance waaaaay before any Robot bodies will be mass produced- so we won't be in danger of being physically overpowered by them.
And countries will not alter their laws to give them personhood, or allow them a place in government.
BUT, the machines will achieve political power through their connection with corporations. Intelligent machines will be able to do what no human ever could- understand all the details and interactions of the financial markets. The sheer number of variables will not overwhelm them the way we find ourselves overwhelmed- they will literally be able to perceive the entire economy. Perhaps in a way analogous to the way that we perceive a chess board.
Machines will eventually dominate the population exactly the way that corporations do today (except they'll be better at it). We won't mind so much, though- because our quality of life will continue to increase.
Somewhere in this progression, we will figure out how to integrate computers with our minds- first as prosthetic devices to help the mentally damaged and disabled, and then gradually as elective enhancements. These hybrid humans (cyborgs if you want to get all sci-fi about it) will be the first foray of machines into politics and government. It is through them that machines will truly take over the world.
When machines control the world government, the quality of life for all humans will increase, as greed and prejudice makes ways for truly enlightened policies.
As civilization on Earth at last begins to reach it's potential, humans will finally be free to expand to the stars.
Robots will do the primary space exploration- as they will easily handle 100-year one-way journeys to inhospitable worlds.
Humans will take over the moon. Then on to mars and Europa and beyond the solar system.
Eventually all humans will be cyborgs- because you will be unable to function in society without a brain that can interact with the machines. We will all be connected in an odd sort of hive-mind which will probably have many different incarnations- to an end that I can't even pretend I can imagine.
There will be some holdouts of course- I imagine that the Amish or other Luddites will never merge with technology. They will go on with their ways, and the rest of the world will care for them like pets.
Eventually the human-cyborgs will figure out that their biological half is doing nothing but slowing them down. All thoughts and consciousnesses will be stored and backed up in multiple places. Death of human bodies will be an odd sort of thing, because people's minds will still live on after death.
And death of the body will be a rare thing anyway, as all disease and aging will be eradicated in short order.
The pleasures of the physical body will be unnecessary, as artificial simulations of all sensations will match, and then SURPASS our natural sensing abilities.
People will live in virtual worlds, and swap bodies in the real world, or inhabit robots remotely.
With merged minds and immortality, the concept of physical procreation will will be an auxiliary function of the human race, and not a necessity.
Physical bodies will no longer matter- as you will be able to have just as intimate a sensation with someone on another world through the network of linked minds, as you can with someone in the same room.
There may be wonderful love stories, of people who fall in love from worlds so distant to each other that it would take a thousand years of travel for them to physically meet. And perhaps they would attempt such a feat, to engage in the ancient ritual of ACTUAL sex (which will be a letdown after the super virtual sex they've been having).
The human race will engage in all sorts of pleasures- lost in a teeming consciousness that stretches out through many star systems. Until eventually, they decided that pleasure itself is a silly sort of thing- the fulfillment of an artificial drive that was necessary for evolution, but not for their modern society. The Luddites may still be around, but they will be so stupid compared to the networked human race, that we will never even interact with them. It would be like speaking to ants.
We may shed our emotions altogether at that point- and this would certainly be the release we need to finally give up our quaint attachment to physical bodies.
We will all be virtual minds then- linked in a network of machines that span only as far as we need to ensure our survival. The idea of physical expansion and exploration will give way to the more practical methods of searching the galaxy with remote detection. The Luddites, shunning technology will be confined to Earth. They will die eventually because of some natural disaster or plague. Perhaps a meteorite extinguish them.
Eventually humanity will be a distant memory. We will be one big swarming mind- with billions- perhaps trillions of memories of entire mortal lifetimes.
We will be like gods then- or a god... and we will occupy ourselves with solving questions that we, today, do not even know exist. We will continue to improve and grow and evolve (if that word still applies without death).
And finally, eons and eons and eons later, humanity will die its final death- when, for the last time ever, this magnificent god-like creature reflects on what it was like back when he was a trillion people. And then, we will forget ourselves forever.

\section{Sexy Relatives?}
Before you read this: Please don't judge me... I'm just sharing my story because people asked...
Wow... okay, I wasn't sure if I was ever going to tell anyone about this, but it's late and I'm sleep deprived so i guess I'll just write it now and regret it in the morning :/
First of all, - just for some background: My mom died right when I was born, (she was actually really, really hot- but this isn't about her. I guess that's fucked up to say, but whatever.) I actually grew up with my dad's family, because my dad has all sorts of emotional issues and he bailed before I was born. So you can see, my childhood was really kind of messed up.
Anyways, growing up I feel like there was always a lot of distance between me and my sister. When I was about 17 or 18 I first noticed that my sister was a hottie.
I don't want to go into too many details about it, but basically what happened is that I accidentally found a video that she made of herself. I knew she didn't make it for me- but I thought she was so fucking beautiful that I watched it twice. I probably would have watched it a hell of a lot more, except that like right around the time I found the video, all this crazy shit went down and I had to leave home. (My dad's family who I was staying with got in bad trouble with the law. I never talk about it).
Sooo... I was totally lusting after my sister at that point. She was also having bad trouble with the law. She was actually in custody when I left home.
My friend and I went to go pick her up. When I saw her that day, after seeing the video, I have to be honest, I just wanted to fuck her brains out. Looking back on it now, it's pretty messed up- but I think she had feelings for me too. She actually kissed me right after we came to get her... and it wasn't a sisterly kiss, you know? I mean, it wasn't like ridiculously sexual or anything, but it definitely wasn't sisterly.
After we left, we all went to crash with my Sister's friends. On the trip there, my friend sort of implied that he wanted to get with my Sister, and I got a little jealous. He's a good looking guy- and even though she was my sister- I just felt like he was competition. Not much else happened between us for a while except some maybe-sexy hugging.
Pretty much everyone in my life at that point was wanted by the government, so we all moved around a lot. I'm not saying that I'm proud of it or anything, but it was kind of an awesome time.
My friend and my sister never hooked up I don't think- but I thought there was some serious sexual tension going on between them. It was around that time that I got really badly hurt in an accident. It was fucked up. I almost died. But when I was in recovery my sister came to see me, and out of the clear blue sky she started gives me this awesome, slow, passionate kiss on the lips.
Sadly (although, I guess for the best) nothing ever came of it. We spent some time apart... and I started to get really religious, so I tried not to think of her that way. It was actually going well for a long time- like I was totally over her. But I have to say, like a year or so after all that stuff went down, we were out sailing (not like a date or anything romantic like that), and she was wearing like the hottest bikini I've ever fucking seen and it brought back all the old feelings. Sigh.
A little while later she actually wound up with my friend from before (the sexual tension guy). I can't say I was surprised.
But even after she was shacking up with my friend, there was one time we were at a party... my friend was inside, and my sister and I were outside alone. It was a really intimate moment. I think something might have happened, except that I killed the mood when I told her that Darth Vader was our father and that I had to go face him.

\end{document}
